### 2017-06-10 report/paper.tex
report skeleton

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% University Assignment Title Page 
% LaTeX Template
% Version 1.0 (27/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% WikiBooks (http://en.wikibooks.org/wiki/LaTeX/Title_Creation)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
% Instructions for using this template:
% This title page is capable of being compiled as is. This is not useful for 
% including it in another document. To do this, you have two options: 
%
% 1) Copy/paste everything between \begin{document} and \end{document} 
% starting at \begin{titlepage} and paste this into another LaTeX file where you 
% want your title page.
% OR
% 2) Remove everything outside the \begin{titlepage} and \end{titlepage} and 
% move this file to the same directory as the LaTeX file you wish to add it to. 
% Then add \input{./title_page_1.tex} to your LaTeX file where you want your
% title page.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title{Title page with logo}
%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\begin{document}

\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\center % Center everything on the page

%----------------------------------------------------------------------------------------
% HEADING SECTIONS
%----------------------------------------------------------------------------------------

\textsc{\LARGE EURECOM}\\[1.5cm] % Name of your university/college
%\textsc{\Large Major Heading}\\[0.5cm] % Major heading such as course name
%\textsc{\large Minor Heading}\\[0.5cm] % Minor heading such as course title

%----------------------------------------------------------------------------------------
% TITLE SECTION
%----------------------------------------------------------------------------------------

\HRule \\[0.4cm]
{ \huge \bfseries Music Recommendation when Exploring a City}\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

%----------------------------------------------------------------------------------------
% AUTHOR SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Authors:}\\
Lorenzo \textsc{Canale} % Your name
\newline
Fabio \textsc{Ellena} % Your name
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
Pasquale \textsc{Lisena} % Supervisor's Name
\end{flushright}
\end{minipage}\\[2cm]

% If you don't want a supervisor, uncomment the two lines below and remove the section above
%\Large \emph{Author:}\\
%John \textsc{Smith}\\[3cm] % Your name

%----------------------------------------------------------------------------------------
% DATE SECTION
%----------------------------------------------------------------------------------------

%{\large \today}\\[2cm] % Date, change the \today to a set date if you want to be precise

%----------------------------------------------------------------------------------------
% LOGO SECTION
%----------------------------------------------------------------------------------------

%\includegraphics{logo.png}\\[1cm] % Include a department/university logo - this will require the graphicx package

%----------------------------------------------------------------------------------------

\vfill % Fill the rest of the page with whitespace

\end{titlepage}
\tableofcontents
\newpage
\begin{abstract}
Common music recommender systems do not take into account the position of the customer. This piece discusses how it is possible to link a song with a POI using the semantic web.
\end{abstract}

\section{Introduction}
Linkng POIs and songs is a big challenge, in fact they are part of two completely separated concepts that cannot be easily linked also by a person it would be difficult to state some criteria that can link a song with a place. We present an approach that attempts to leverage this problem by using the semantic relations exposed by DBpedia.
\subsection{Motivation and context}

\subsection{Research problems}

\subsection{Contributions}

\subsection{Report structure}
The report is divided into four sections, one for each part of the project. The first two parts are about linking external datasets to Dbpedia, this is also known as enrichment and it consists of linking in the correct way two entities of different datasets
\section{Interlinking and enriching POIs}

\subsection{Problem description}
Finding relations inside DBpedia is a known problem which has been resolved in the past. So we could simply look for POIs and Artists in Dbpedia and then link them using known algorithms.
Unfortunately DBpedia is not perfect: it is true that it contains POIs and Artists, but these entities are not cleanly defined, they usually contains dirty data that can tremendously affect our performances.
POIs and Artists can be found in highly specialized datasets, but unfortunately they do not contain links to eachother, and even worse they are not linked to DBpedia. This means that by using these databases alone we cannot find relations.
What is done in this cases is to link highly specialized datasets to DBpedia, in this way we can exploit the advantages of both worlds: highly specialized datasets give us confidence and trust in our main entities (POIs and Artists), while DBpedia allow us to find relations between them thanks to its generality.
The following two sections will explain in a detailed way the whole process of connecting these highly specialized datasets to DBpedia.

\subsection{Datasets: 3cixty, DBpedia, Wikidata}
\subsubsection{3cixty}
3cixty is a semantic dataset that contains aggregated informations of POIs and events. The dataset is the result of an aggregation process that join the POI informations from different datasets e.g. Facebook, Foursquare, Yelp \dots
In this project 3cixty is used as a trusted source of POIs for Nice.
POIs have many informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint selecting the Nice city.
\subsubsection{DBpedia}
DBpedia is a project that aims at connecting the semantic world. We used it to get the POIs in Nice.
In order to get the POIs from DBpedia, it is necessary to perform SPARQL queries against the SPARQL endpoint. POIs are retrieved using two different sparql queries that target different kind of resources:
\begin{enumerate}
\item We perform a query that looks for all Geoentities that are in the area of nice. An entity is in the area of Nice if its coordinates are in a custom box that contains all the area of Nice.
Unfortunately there are many POIs that are without coordinates,so they are not selected with this query.
\item We perform some queries that get in a recursive way all entities that have as a parent the category of nice or nice and that are related to a place. The relation to a place is a list of classes that is done by hand and could be subjected to refinements.
\end{enumerate}
\subsubsection{Wikidata}
Wikidata is a project that aims at connecting the semantic world. We used it to get the POIs in Nice. Respect to DBpedia, Wikidata has a well defined ontology that is strictly enforced. This means that it is easier to select what we want. Moreover, most of POIs in wikidata have coordinates, so we can get them with a single query. Since wikidata supports complex geo-based queries, we made a query that looked for all POIs in a range of 25 Kilometers from the center of Nice.
\subsection{Entity Linking process}
Now that we have locally all our entities, we can link them. Having the entities locally is crucial, in fact it allows us to make way more complex operations respect to those that can be done with SPARQL queries.
\subsubsection{Properties}
The first phase is to actually get the interesting properties of the entities. Regarding those that come from DBpedia, we take use only the labels. We do not use coordinates because not all entities have them and we do not want to bias our algorithm using DBpedia coordinates, which is known that are not very accurate. Regarding the labels, we take all labels from all entities, in this way we are going to do a multilingual match because we know that sometimes this can make the difference.
Respect to Dbpedia, 3cixty entities have very accurate coordinates, and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.
\subsubsection{Transformations}
At this point of the pipeline, we have labels that are encoded in unicode utf-8. Common similarity metrics accepts only plain ASCII strings as input, so we need to convert them into ASCII. Since utf-8 can represent way more characters than ASCII, we need to strip non ASCII characters from our labels. This is done in an intelligent way using the python library 'unidecode', that is able to convert from unicode to ASCII deleting only few characters. For example, an accented letter like 'è' can't be represented in ASCII. Most of the libraries delete all incompatible characters, while 'unidecode', when possible, converts it to the nearest ASCII character, in this case 'è' is converted to 'e'. In this way we can retain most of the original information after this conversion process.
The second step is probably the most important, and is the normalization of names. Some similarity metrics are extremely sensitive to noise. For example, when we use simple levenstein distance between ('aeroport','aeroport nice') is 5, while the distance ('aeroport','port') is 4. This is enough to raise some concerns: the simple addition of the city name can turn a perfect match into a mediocre one. In order to fix this problem we add the city name to all the labels where this is not present.
The third step is to strip all not alphabetical characters and to convert to lowercase all strings, this offcourse gives us cleaner strings to compare.

\subsubsection{Similarity measures and matching algorithm}
Now that strings are clean, we can proceed to the matching. A first problem rises: we want to match a 3cixty poi to a dbpedia poi, or we want to match a dbpedia poi to a 3cixty poi? In the first case we are sure that each 3cixty poi will be matched to a single dbpedia poi, but there is the risk that multiple 3cixty poi are matched to the same DBpedia poi. Alternatively, we match are sure that each DBpedia poi is matched to at most a 3cixty poi, but there is the risk that two DBpedia poi are matched to the same 3cixty poi.
Regarding DBpedia, we are sure that POIs are univoque, while we know that for the same POI, in 3cixty there are multiple ones.
Since at the end we will be using 3cixty coordinates, we opt for the first choice: if a DBpedia poi will be matched to multiple 3cixty pois, than we will follow an heuristic to choose the best match.
Regarding similarity metrics among strings, there are multiple ones, but most of them are based on levenstein distance.
Since each distance has its privileges and defects, we use multiple similarity measures, taken from the 'fuzzy wuzzy' python library.
For each 3cixty poi get the label and calculate the different similarity metric against all labels of all DBpedia POIs.

\subsubsection{Aggregations}
The aggregation algorithm can be described as follow:
\begin{enumerate}
\item For each similarity metric, take the three best matches and for them average the score of all similarity measures
\item The final match is the POI corresponding with the string with the highest score
\end{enumerate}
Why we don't simply take the average, or the minimum, or the maximum?
The reasoning behind this is that by taking the average we are flattening all the scores, and there is the risk that the string with the highest similarity is a string that is mediocre in all the different metrics. If a string is mediocre in all comparisons, then we do not trust it. Instead, with our methodology we are keeping only those matches that excel in some similarity metric, and then we take the one that performs better on average. We think that in this way we can filter out all those matches with average strings that matches almost anything.

\subsubsection{Filtering}
Now that the matching is done, we need to filter our results.
The first filter to do is to eliminate all those matches that match with Nice, but that have a label different from Nice. This usually happens because we added Nice to all strings. That addition was helpful, and it also created a safe default that now can be easily filtered.
Most of these match are acronym that match with Nice e.g. 'ATP Nice' matches with Nice because half of the string is Nice and is artificial, because we added it.

At this point we filter out all matches with a score below a given threshold.

Then, we have probably multiple 3cixty POIs connected to a single DBpedia POI.
In order to choose the most representative 3cixty POI, from whom we will take the coordinates, we have few possibilities:
\begin{enumerate}
\item K-medoids: We can actually cluster our points and look at the rapresentant of the biggest cluster 
\item Pick the POI which is nearest to the center
\item Pick the POI which is nearest to the DBpedia POI, if coordinates are available
\item Pick the POI which is nearest to the position found on OpenStreetMap
\item Link our data to GeoNames, a dataset of POIs
\end{enumerate}
The first method might be the best one, but it requires several precautions.
The second method is baiased towords pois in the center.
The third method can work only with POIs with coordinates, and gives good results if DBpedia coordinates are good, but we already know that this is not true.
The fourth method might be the best one, but we need to exit from the semantic world and hope that the API gives a good result, here the problem is that we have no control over the API.
The fourth method can work, but we would need to design another linking process.

For simplicity and reliability, we decided to use both OpenStreetMap API and Google Map API, in this way we have a much bigger confidence.

We make a request with the DBpedia label to the API, and we keep the POI which is nearest to one of them, in this case the minimum distance wins. If the distance is greater than a chosen threshold (500 meters), then the match is filtered out.

\subsection{Evaluation (Google Map / OpenStreetMap)}
The evaluation part is done using both the Google Map and OpenStreetMap. We calculated the Medium Square Error of the POIS to the positions recovered with the APIs, the error distance is the haversine distance.
\section{Interlinking and enriching Artists}
\subsection{Problem description}
\subsection{Datasets: DOREMUS, DBpedia, Wikidata}
\subsection{Entity Linking process (+ ElasticSearch)}
\subsubsection{Properties}
\subsubsection{Transformations}
\subsubsection{Similarity measures}
\subsubsection{Aggregations}
\subsubsection{Filtering}
\subsection{Evaluation}
\section{Path finder}
\subsection{Problem description}
\subsection{Related work (relfinder)}
\subsection{Proposed approach and best path selection algorithm}
\section{REST API}
The paths between a POI and the linked artists are exposed by a REST API that runs on Flask. Their extensible framework allows to develop several components requiring minimum boilerplate.
The main endpoint is the one that exposes the tracks and the paths related to a specific geoposition.
The whole process can be summarized in:
\begin{enumerate}
\item Take user position
\item Calculate nearest POIs and assign weights, from these create a univoque playlist name.
\item Select the tracks for each artist linked with the poi.
\item Select for each artist a compatible number of tracks to put in the playlist.
\item Create a playlist if it does not exist and add previously selected tracks.
\item Attach to each track the path between the poi and the track's artist.
\item Return the playlist ID and the track-path mappings as a JSON.
\end{enumerate}
\subsection{Spotify API usage}
Spotify provides a public API that allows to perform all the operations that can be done using the Spotify application. These comprend artist and tracks search, CRUD operations on user playlists and the listening of the tracks' preview.
\subsubsection{Authentication}
Since the end user listen to a spotify loaded dynamically by the application, there is no need for a client authentication. This is perfect because it allows to any user to use our application. Regarding the server, At startup it is performed a token based authentication, where the server get possess of a private token used to perform all CRUD operations on the playlist catalogue.
\subsubsection{Playlist}
A playlist can be dynamically created. At creation time, it is required to give a name to the playlist, and the whole playlist object, containing the univoque playlist ID is returned. Later it is possible to access to the playlist either using the playlist ID or using the playlist name. The playlist name is univoque inside the application by construction, while the playlist ID is univoque for all Spotify playlists.
\subsubsection{Artist}
An artist can be searched by name, this part is the most critical one because Spotify does not provide any automatic artist matching using the api. This means that specifying the full name of the artist is essential for the success of this operation.
This is done by using the Doremus person label property, which consists of name and surname of the artist. It is interesting to note that from this point of view DBpedia is not reliable because the person label can contains adjectives used for the disambiguation of this one, such as 'Composer'. If this adjectives are passed to the Spotify search endpoint, no artist is returned.
When a request is done, Spotify returns a list of matching artists. Each artist object contains different informations, among them the most useful are the genres and the popularity. 
In order to limit outliers, not only we select the most popular artist, but we check that it has at least 10 popular songs, where popular songs are special songs selected by spotify. The popularity metric algorithm is not public, but it is based on the playcounts and the recentness of the track.
Here we use the popularity as a criteria to select the correct artist, in fact we take always the most popular. The use of the genre specification would be interesting for an ulterior enhancement.
\subsubsection{Tracks}
Among all properties that caracterize a track, we only need the ID and the name.

\subsection{Playlist Endpoint}
\subsubsection{Nearest POIs selection algorithm}
In order to match a position with a list of POIs, the following algorithm is followed:
\begin{enumerate}
\item Calculate distance from the each POI to the user position. Since we are using coordinates, the distance is calculated using the haversine distance, which is very accurate and fast.
\item Add to the list the nearest POI, regardless of the distance.
\item Add the remaining two nearest POIs if their distance is inferior of 1 km.
\item For each element in the list, add 10 meters to the distance and then take the log2. By adding 10 meters we are adding a bias to all our distances, in this way positions too near to us are not over-weighted respect far distances. Then, the log2 squashes distances until 1 km to a restricted range of values.
\item Calculate repartition weights using the following equation:
$$w_i = \Bigg \lfloor 10 \dfrac{\dfrac{1}{\log_2 (d_i + 10)}}{\sum \dfrac{1}{\log_2 (d_i + 10)} } \Bigg \rceil$$
In this way we obtain normalized weights from 0 to 10 that are inversely proportional to the log base 2 of the distance. 
\end{enumerate}
At this point we have a direct mapping between POIs weights and a position
\subsection{Artist' tracks selection algorithm}
For each artist there is a direct mapping with its tracks.
The problem is: given a playlist name, find the correct tracks.
The playlist name encodes the weights of each poi, and each weight express exactly the number of tracks that must be chosen for the POI associated.
Since each POI is linked to different artists, we need a way to select songs from them in a balanced way.
What we do is to cycle between all the artists to take each time the most important song that is not already present in the playlist. In this way we obtain different songs from different artists, and since the artist and songs are static, the tracks in the playlist will be always the same. In the future we think to add randomicity to the whole selection process.

\subsection{Response generation}
\begin{enumerate}
\item Generate playlist name as described before
\item Select tracks as described before
\item Create a playlist if it does not exist and add previously selected tracks.
\item Attach to each track the path between the poi and the track's artist.
\item Return the playlist ID and the track-path mappings as a JSON.
\end{enumerate}

\section{Mobile Web Application}
\subsubsection{Music Player}
\subsection{Google Map API}
\subsubsection{POIs placement}
\subsubsection{Navigation}
stocazzo
\subsection{Relation visualization (and Path format)}
\section{Conclusion and Future Work}

Your introduction goes here! Some examples of commonly used commands and features are listed below, to help you get started.

If you have a question, please use the support box in the bottom right of the screen to get in touch.

\section{Some \LaTeX{} Examples}
\label{sec:examples}

\subsection{Sections}

Use section and subsection commands to organize your document. \LaTeX{} handles all the formatting and numbering automatically. Use ref and label commands for cross-references.

\subsection{Tables and Figures}

Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. You can upload a figure (JPEG, PNG or PDF) using the files menu. To include it in your document, use the includegraphics command as in the code for Figure~\ref{fig:frog} below.

% Commands to include a figure:
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{frog.jpg}
\caption{\label{fig:frog}This is a figure caption.}
\end{figure}

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{\label{tab:widgets}An example table.}
\end{table}

\subsection{Mathematics}

\LaTeX{} is great at typesetting mathematics. Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
$$S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i$$
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.

\subsection{Lists}

You can make lists with automatic numbering \dots

\begin{enumerate}
\item Like this,
\item and like this.
\end{enumerate}
\dots or bullet points \dots
\begin{itemize}
\item Like this,
\item and like this.
\end{itemize}

We hope you find write\LaTeX\ useful, and please let us know if you have any feedback using the help menu above.

\end{document}

### 2017-06-10 report/paper.tex
report update

@@
 Common music recommender systems do not take into account the position of the customer. This piece discusses how it is possible to link a song with a POI using the semantic web.
+
+Abstract: Place is a notion closely linked with the wealth of human experience, and invested
+by values, attitudes, and cultural influences. In particular, many places are strongly linked to
+music, which contributes to shaping the perception and the meaning of a place. In this project we
+propose a semantic based approach for finding musicians linked to a place of
+interest (POI).
+We show a semantic-based framework built upon the DBpedia ontology, 3cixty and Doremus.
+Furthermore we present a graph exploration algorithm  that is able to find deep connections in a triple store in an short time and discriminate between them
+graph-based algorithm that scores musicians with respect to their semantic relatedness to
+a POI and suggests the top scoring ones. We found that users appreciate and judge as valuable
+the musician suggestions generated by the proposed approach. Moreover, users perceived
+compositions of the suggested musicians as suited for the POIs
+
 \end{abstract}
@@
 \subsubsection{Music Player}
+The music player is implemented using the Spotify Play Button.
+This is a special iframe that loads a simplified Spotify player for a specified playlist.
+This solution is extremely convenient because it simply needs a plylist ID to run.
+Since the playlists are created server side and are recovered using the REST API, the whole process is very simple.
+Unfortunately it is not possible to manipulate programmatically the iframe and this limit the whole user experience. As an improvement, we could build a custom player that still uses the Spotify API.
 \subsection{Google Map API}
 \subsubsection{POIs placement}
+todo: Lorenzo
+
 \subsubsection{Navigation}
-stocazzo
+
 \subsection{Relation visualization (and Path format)}
+todo: Lorenzo
 \section{Conclusion and Future Work}

### 2017-06-10 report/paper.tex
report update

--- 2017-06-10 report/paper.tex
@@
 \begin{abstract}
-Common music recommender systems do not take into account the position of the customer. This piece discusses how it is possible to link a song with a POI using the semantic web.
+Abstract: In this project we show a new approach for finding artists linked to a place of interest (POI).
+We propose a semantic-based framework built upon the DBpedia, 3cixty, and Doremus.
+Furthermore we present a graph exploration algorithm that is able to find deep connections in an short time and discriminate between them by looking at those that can be the most interesting.
+Our project aims to making the user know about the existing connections that can link music to a Place, by stimulating the curiosity of the user proposing non common relations.
 \end{abstract}
@@
 \section{Introduction}
-Linkng POIs and songs is a big challenge, in fact they are part of two completely separated concepts that cannot be easily linked also by a person it would be difficult to state some criteria that can link a song with a place.
-We present an approach that attempts to leverage this problem by using the semantic relations exposed by DBpedia.
+todo: change
+Most of the available music recommenders suggest music without taking into consideration the user’s context, e.g., her mood, current location, activity. 
+Finding music that suits a POI can be viewed as a context-aware recommendation problem, the place being the context for consuming the recommendation.         
+The main challenge that one must face when addressing the above mentioned goal is related to the fact that POIs and music are two rather different domains, and there is no obvious way to match such heterogeneous items.
+However, with the advent of the Semantic Web, and specifically with its reference implementation in the Linked Data initiative, new opportunities arise to face the above difficulties.
+
 \subsection{Motivation and context}
+In the past, many tried to link POIs and music in many different way. xxx managed to link music and POIs by using a common set of tags that describe emotional properties both for music and POIs.
+This method is completely supervised, in fact it is necessary to define in a clean way emotions for songs and POIs. This operation was done by hand and is hardly scalable.
+Marius Kaminskas restrict the subspace of DBpedia by identifying classes belonging to the two domains of interest, and the relations existing between instances of such classes.
+In this way they managed to find relations in a set of constrained paths.
+Looking on the future works proposition, they proposed the idea to exploit arbitrary semantic relations between POIs and musicians, e.g.
+direct relations such as 'Gustav Mahler was the director of Vienna State Opera', and complex non-directed relations such as 'Ana Bel' (a famous Spanish singer) composed a song whose lyrics are about La Puerta de Alcala (a well-known POI in Madrid, Spain).
+In order to do this, they wanted to use Relfinder and set the connections' weights programatically.
+In fact one of the bad things was that connections weights were assigned by experts and were not provided in the paper.
+
+What we intend to do is to find relations in a completely unsupervised way: this means that we intend to define a pathfinder that finds paths and a path discriminator that selects the interesting algorithms.
+Our intention is to limit to zero the need of human intervention in the hope that this approach will be completely data driven and easily scalable
 
 \subsection{Research problems}
-
-\subsection{Contributions}
-
-\subsection{Report structure}
-The report is divided into four sections, one for each part of the project.
-The first two parts are about linking external datasets to Dbpedia, this is also known as enrichment and it consists of linking in the correct way two entities of different datasets
-\section{Interlinking and enriching POIs}
-
-\subsection{Problem description}
-Finding relations inside DBpedia is a known problem which has been resolved in the past. So we could simply look for POIs and Artists in Dbpedia and then link them using known algorithms.
+Finding relations inside DBpedia is a known problem which has been solved in the past. So we could simply look for POIs and Artists in Dbpedia and then link them using known algorithms.
 Unfortunately DBpedia is not perfect: it is true that it contains POIs and Artists, but these entities are not cleanly defined, they usually contains dirty data that can tremendously affect our performances.
@@
 The following two sections will explain in a detailed way the whole process of connecting these highly specialized datasets to DBpedia.
+
+\subsection{Contributions}
+
+\subsection{Report structure}
+The report is divided into five sections, one for each part of the project.
+The first two parts are about linking external datasets to Dbpedia, this is also known as entity linking and we perform it in the optic of enriching our data with the inter-concept links present in DBpedia.
+The third treats the pathfinder, a module of our system that is able to find deep connections between two entities in DBpedia.
+The fourth describes the whole implementation of the REST API that allows the application to work smoothly.
+The fifth part is about the mobile web application and the technologies involved in its functioning.
+
+\section{Interlinking and enriching POIs}
+\subsection{Problem description}
+Finding relations inside DBpedia is a known problem which has been solved in the past. So we could simply look for POIs and Artists in Dbpedia and then link them using known algorithms.
+Unfortunately DBpedia is not perfect: it is true that it contains POIs and Artists, but these entities are not cleanly defined, they usually contains dirty data that can tremendously affect our performances.
+We start our search of connecting POIs and Artists from the POIs.
+POIs can be found in highly specialized datasets that contains clean data that we can trust, one of these datasets is 3cixty.
+Now, it would be optimal to find a direct mapping between a 3cixty POI and a DBpedia POI, in this way we could actually enrich the 3cixty POI with the context informations that can be found on DBpedia.
+Unfortunately this link does not exist and we must create it on our own by using an heuristic.
 
@@
 \subsection{Datasets: DOREMUS, DBpedia, Wikidata}
+\subsubsection{DOREMUS}
+3cixty is a semantic dataset that contains aggregated informations of POIs and events.
+The dataset is the result of an aggregation process that join the POI informations from different datasets e.g.
+Facebook, Foursquare, Yelp \dots
+In this project 3cixty is used as a trusted source of POIs for Nice.
+POIs have many informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint selecting the Nice city.
+\subsubsection{DBpedia}
+DBpedia is a project that aims at connecting the semantic world. We used it to get the POIs in Nice.
+In order to get the POIs from DBpedia, it is necessary to perform SPARQL queries against the SPARQL endpoint.
+POIs are retrieved using two different sparql queries that target different kind of resources:
+\begin{enumerate}
+\item We perform a query that looks for all Geoentities that are in the area of nice. An entity is in the area of Nice if its coordinates are in a custom box that contains all the area of Nice.
+Unfortunately there are many POIs that are without coordinates,so they are not selected with this query.
+\item We perform some queries that get in a recursive way all entities that have as a parent the category of nice or nice and that are related to a place.
+The relation to a place is a list of classes that is done by hand and could be subjected to refinements.
+\end{enumerate}
+\subsubsection{Wikidata}
+Wikidata is a project that aims at connecting the semantic world.
+We used it to get the POIs in Nice.
+Respect to DBpedia, Wikidata has a well defined ontology that is strictly enforced.
+This means that it is easier to select what we want.
+Moreover, most of POIs in wikidata have coordinates, so we can get them with a single query.
+Since wikidata supports complex geo-based queries, we made a query that looked for all POIs in a range of 25 Kilometers from the center of Nice.
+
 \subsection{Entity Linking process (+ ElasticSearch)}
@@
 \subsection{Evaluation}
+todo: add source of isni
+The evaluation of the found links is done by comparing the found links with those provided by ISNI.
+ISNI is the ISO certified global standard number for identifying the millions of contributors to creative works.
+By achieving these goals the ISNI will act as a bridge identifier across multiple domains and become a critical component in Linked Data and Semantic Web applications.
+
+ISNI matches are made by humans, so we can consider them as a ground truth that can be trusted.
+By comparing our matches we want to see if our performances are acceptable and if we can discover new links between ISNI numbers and DBpedia.
+
+todo: table with cool statistics
+todo: graph image
+
+We can state that the proposed method based on combinations of labels, classes and dates is able to match almost perfectly the artists of the two datasets.
+Moreover, we are able to find 2000 artists that at the time of writing are not present in the ISNI register.
+
 \section{Path finder}
 \subsection{Problem description}
-\subsection{Related work (relfinder)}
-\subsection{Proposed approach and best path selection algorithm}
+todo: add citations
+Once we have a direct mapping between entities that comes from specialized datasets and DBpedia, we actually need to link POIs and Artists.
+The problem of finding relations between entities in DBpedia has already been approached and solved in the past, especially from Relfinder.
+The whole problem can be solved by writing a single query that finds a path of a given depth between two resources.
+This approach works well when datasets are relatively small and the two entities are two concepts that are semantically close.
+Instead, in our case we have concepts that are definetly far from each other, which implicates an high depth of an eventual path, and most importantly, we need to match hundreds of POIs with thousands of artists, This makes means that at the end the whole process will be repeated 100.000 times.
+\subsection{Related work (Relfinder)}
+The path finding problem has already been solved in the past with Relfinder: a tool that is able to find all paths with a specified depth between two entities. 
+In fact, when we think at linking two entities, we need to set the position of the middle node and the number of middle nodes.
+
+$$a-->b-->c-->d-->e=m$$
+$$a-->b-->c-->d=m<--e$$
+$$a-->b<--c=m-->d-->e$$
+
+These are all different paths that links two entities 'a' and 'e'.
+In the simpler case, the arrows goes in one direction.
+In the second case they change direction one time.In the third case they change two times.
+Relfinder manages to solve the problem by making different query that cover all possible combinations of the path specified above.
+As a constraint, in Relfinder the direction cannot change more than two times.
+There are still a huge amount of queries that explodes when the depth starts to be deep.
+Here we intend as a deep depth a depth greater than 4, in fact this is like a magic threshold. 
+Moreover, when we use Relfinder and set a greater depth we incur in two problems: 
+\begin{enumerate}
+\item The number of queries explodes because we need to consider all possible combinations
+\item The time required by a single query explodes too, most of the times we cannot even do a query between two entities in a short time.
+\end{enumerate}
+In order to succeed we need to solve those two problem and we need to create a fast implementation, because at the end we will need to do 100.000 queries. 
+\subsection{Proposed approach}
+The problem is that DBpedia is small world and its average degree is 4.3, this means that on average we can reach every entity in at most 4-5 hops.
+Unfortunately our problem does not make part of that average, and many times we need 5-6 hops to connect two entities.
+The problem is that when we make a query that looks for paths with depth 6 we are basically querying the whole DBpedia, which at the time of writing is composed of 8.8 billion triples.
+It is our belief that a query that tries to find a path between two entities, is converted by the SPARQL engine in what we can compare to a join for each hop.
+This, with the small world characteristic of DBpedia means that we are doing huge joins for each query.
+Another way to visualize the query is a Breath First Search that starts from the source entity, and it expands hop after hop until the specified depth is reached.
+In this way is even more easy to see why we and up by querying billions of triples.
+A common improvement of BFS is the two-way BFS, where the same algorithm is applied both at the source and the destination.
+In this way we can see that we can reach the same middle node by querying a way smaller portion of the graph.
+Then, looking by hand at paths, we have seen that usually one direction inversion cover most of the cases, by limiting this we are actually simplifying a lot our problem.
+The, we have seen that for artists and POIs, the connection is most of the times the result of a common node.
+This means that the direction must change at least one time.
+We reduced all the different cases to one.
+In fact what we do is to make two separate queries with depth  from the source and from the destination.
+These queries return the list of all half-paths.
+We make a set of the involved nodes and then we intersect the two sets, in order to find the common nodes.
+At this point we operate joins that create full paths.
+The whole matching of POIs and Artists,100.000 combinations, requires only some hours against the weeks that would take relfinder.
+\subsection{Selection Algorithm}
+Now that we have all our path, we need to find the best ones, those that shows interesting links between POIs and Artists.
+todo: lorenzo
 \section{REST API}

### 2017-06-12 report/paper.tex
report update

@@
 
-%\includegraphics{logo.png}\\[1cm] % Include a department/university logo - this will require the graphicx package
+\includegraphics[scale=0.8]{logo.jpg}\\ % Include a department/university logo - this will require the graphicx package
 
@@
 \end{titlepage}
+\begin{abstract}
+Abstract: 
+Our project aims at making the user discover the existing connections that link music to a Place, by stimulating his curiosity proposing non common relations.
+In this project we show a new approach for finding artists linked to a place of interest (POI).
+We propose an entity linking framework built upon DBpedia, 3cixty, and Doremus that is able to reach editorial accuracy in the interlinking process.
+Furthermore we present a graph exploration algorithm that is able to find deep connections in an short time and discriminate between them by looking at those that can be the most interesting.
+\end{abstract}
+\newpage
+
 \tableofcontents
 \newpage
-\begin{abstract}
-Abstract: In this project we show a new approach for finding artists linked to a place of interest (POI).
-We propose a semantic-based framework built upon the DBpedia, 3cixty, and Doremus.
-Furthermore we present a graph exploration algorithm that is able to find deep connections in an short time and discriminate between them by looking at those that can be the most interesting.
-Our project aims to making the user know about the existing connections that can link music to a Place, by stimulating the curiosity of the user proposing non common relations.
-\end{abstract}
 
@@
 The main challenge that one must face when addressing the above mentioned goal is related to the fact that POIs and music are two rather different domains, and there is no obvious way to match such heterogeneous items.
-However, with the advent of the Semantic Web, and specifically with its reference implementation in the Linked Data initiative, new opportunities arise to face the above difficulties.
+However, with the advent of the Semantic Web,  new opportunities arise to face the above difficulties.
 

### 2017-06-12 report/paper.tex
report update

@@
 In the past, many tried to link POIs and music in many different way. xxx managed to link music and POIs by using a common set of tags that describe emotional properties both for music and POIs.
-This method is completely supervised, in fact it is necessary to define in a clean way emotions for songs and POIs. This operation was done by hand and is hardly scalable.
-Marius Kaminskas restrict the subspace of DBpedia by identifying classes belonging to the two domains of interest, and the relations existing between instances of such classes.
-In this way they managed to find relations in a set of constrained paths.
+This method was completely supervised, in fact it required the definition of a set of emotions for songs and POIs. This operation has been done by hand and is hardly scalable.
+In another project, Marius Kaminskas restricted the subspace of DBpedia by identifying classes related to the domains of interest, and the relations existing between instances of such classes.
+In this way they managed to find relations in a set of paths constrained to pass belong to those classes.
 Looking on the future works proposition, they proposed the idea to exploit arbitrary semantic relations between POIs and musicians, e.g.
@@
 
-What we intend to do is to find relations in a completely unsupervised way: this means that we intend to define a pathfinder that finds paths and a path discriminator that selects the interesting algorithms.
-Our intention is to limit to zero the need of human intervention in the hope that this approach will be completely data driven and easily scalable
+Our intention is to build our approach on top of this paper and find relations in a completely unsupervised way: this means that we intend to define a pathfinder that finds paths and a path discriminator that selects the interesting relations.
+We aim at reducing the need of human intervention in defining classes and weights with the hope that this approach will be completely data driven and easily scalable to different cities.
+Moreover, we will use different datasets with the intention to exploit their implicit advantages and obtain overall a better recommender system.
 
@@
 Unfortunately DBpedia is not perfect: it is true that it contains POIs and Artists, but these entities are not cleanly defined, they usually contains dirty data that can tremendously affect our performances.
-POIs and Artists can be found in highly specialized datasets, but unfortunately they do not contain links to eachother, and even worse they are not linked to DBpedia.
+
+On the other side, POIs and Artists can be found in highly specialized datasets, but unfortunately they do not contain links to each other, and even worse they are not linked to DBpedia.
 This means that by using these databases alone we cannot find relations.
 What is done in this cases is to link highly specialized datasets to DBpedia, in this way we can exploit the advantages of both worlds: highly specialized datasets give us confidence and trust in our main entities (POIs and Artists), while DBpedia allow us to find relations between them thanks to its generality.
-The following two sections will explain in a detailed way the whole process of connecting these highly specialized datasets to DBpedia.
+
+Once we have our two sets, we need to find paths that link them. This problem has been solved in the past with Relfinder, a tool that is able to fin relations between entities.
+What we have seen is that POIs and Artists are generally far from each other, in fact usually we need 5 hops to link them, this is more that the average DBpedia degree and it is also more than what Relfinder can do, in fact Relfinder query times are too high once we set more that 4 hops.
+This lead us to create a pathfinder that can work in acceptable times with 100.000 pairs that are far from each other.
 
@@
 \subsection{Problem description}
-Finding relations inside DBpedia is a known problem which has been solved in the past. So we could simply look for POIs and Artists in Dbpedia and then link them using known algorithms.
-Unfortunately DBpedia is not perfect: it is true that it contains POIs and Artists, but these entities are not cleanly defined, they usually contains dirty data that can tremendously affect our performances.
-We start our search of connecting POIs and Artists from the POIs.
-POIs can be found in highly specialized datasets that contains clean data that we can trust, one of these datasets is 3cixty.
-Now, it would be optimal to find a direct mapping between a 3cixty POI and a DBpedia POI, in this way we could actually enrich the 3cixty POI with the context informations that can be found on DBpedia.
-Unfortunately this link does not exist and we must create it on our own by using an heuristic.
+Interlinking different datasets is not trivial, many approaches that aimed at a semi-supervised interlinking has been proposed, but this is still a topic of research.
+The worst part of this is actually the class definition, in fact specialized datasets tend to have a very strict ontology, while DBpedia does not enforce it.
+This means that not all music artists are composers, and that not all places in nice are linked to nice.
+Since Nice is a middle city, we cannot allow to loose some matchings and we need to carefully analyze the DBpedia ontology.
 
@@
 
-ISNI matches are made by humans, so we can consider them as a ground truth that can be trusted.
+ISNI matches are made by persons in the editorial world, so we can consider them as a ground truth that can be trusted.
 By comparing our matches we want to see if our performances are acceptable and if we can discover new links between ISNI numbers and DBpedia.
@@
 \section{Conclusion and Future Work}
+Regarding the fact that is difficult to evaluate the performances of a recommender system, in fact a user may seem appropriate the link but not like the song, we are convinced of our results.
+Regarding the first part: the interlinking, we can refer to the evaluation section of the two approaches.
+Regarding POIS, we see that we achieve a perfect POIs matching: matched POIS are 99\% correct, and their positioning is very accurate, comparable to Google Maps.
+
+Regarding the Artist matching, we obtained a perfect match, in fact we have checked that our linker fails when the ISNI matches are wrong.
+Moreover, we have found 3000 entities with high confidence that are not matched by ISNI.
+So we think that this linker can definetly considered a success.
+
+Pathfinding: we created a way that has never been publicated that is actually scalable.
+We think that having scalable solution for the relation finding is crucial for any project that aims to use heavily the huge knowledge graph that DBpedia is.
+
+Moreover, we find a good use of an equation proposed in another paper. todo. cite
+
+The high precision values (over 80% for top 5 results in
+
+Table 1) obtained by the evaluated recommendations let us
+
+claim that our approach is able to automatically identify
+
+musicians semantically related to a given place of interest
+
+(RQ1). The user studies also showed that, in our approach,
+
+musicians evaluated as relevant tend to have relative high
+
+numbers of paths in a POI’s semantic network for all the
+
+proposed types of relations (i.e., city, date and category),
+
+while these numbers are significantly lower for non-relevant
+
+musicians. This evidences that our approach, which is based
+
+on finding semantic paths between POIs and musicians, can
+
+be used effectively to define and evaluate the semantic relat-
+edness between such instances (RQ2). Moreover, we have
+
+shown that users perceive music composed/performed by the
+
+recommended musicians as well-suited for the POIs.
+
+We note that the presented framework fully relies on the
+
+data available in DBPedia repository – in order for a mu-
+sician to be recommended by our approach, its record has
+
+to be present in DBPedia. Admittedly, this is a limitation,
+
+since less known musicians may not have DBPedia entries.
+
+In the future, this could be addressed by using additional
+
+Linked Data repositories.
+
+An important next step in this research is adapting the
+
+proposed framework to incorporate user preferences into the
+
+recommendation process. As described in Section 3.1, this
+
+can be achieved using the weights of relations between classes
+
+and instances in the semantic network. We intend to ex-
+plore personalization approaches that translate user’s pref-
+erences into these weights. Furthermore, we intend to work
+
+on identifying and exploiting other arbitrary semantic rela-
+tions between POIs and musicians, e.g. direct relations such
+
+as ‘Gustav Mahler was the director of Vienna State Opera’,
+
+and complex non-directed relations such as ‘Ana Bel ́en (a fa-
+mous Spanish singer) composed a song whose lyrics are about
+
+La Puerta de Alcal ́a (a well-known POI in Madrid, Spain)’.
+
+We will search for these relations in different Linked Data
+
+repositories, and will use available tools such as RelFinder
+
+[7]. It is also important to better explore and evaluate strate-
+gies to initialize the importance weights of the relations and
+
+classes in the semantic network. In this context, we will ex-
+plore other approaches to define and measure the semantic
+
+relatedness between concepts [13], and will adapt or extend
+
+them for cases in which the concepts belong to different do-
+mains.
 

### 2017-06-15 server/util.py
poi nearness calculated with log

@@ -7,17 +7,22 @@ import spotipy_util
 def get_near_pois(source, original_pois):
     """given a position and the poi, get three nearest ones"""
 
+    def log2(x):
+        return np.log(x)/np.log(2)
+
     def add_distance_wrapper(src):
         def add_distance(point):
             point['distance'] = vincenty(src, (float(point['latitude']), float(point['longitude']))).meters
-            if point['distance'] < 5:
-                point['distance'] = 5
-            point['distance_sqrt'] = np.sqrt(point['distance'])
+            point['distance'] += 10
+            point['distance_sqrt'] = log2(point['distance'])
             return point
         return add_distance
 
-    MAX_RADIUS = 350
-    MAX_RADIUS_SQRT = np.sqrt(MAX_RADIUS)
+
+
+    MAX_RADIUS = 1000
+
+    MAX_RADIUS_LOG = log2(MAX_RADIUS)
 
     new_pois = copy.deepcopy(original_pois)
 
@@ -28,13 +33,13 @@ def get_near_pois(source, original_pois):
     near_pois = sorted(near_pois, key=lambda x: x['distance'])[:3]
 
     filtered_pois = [near_pois.pop(0)]
-    filtered_pois += filter(lambda x: x['distance_sqrt'] < MAX_RADIUS_SQRT, near_pois)[:2]
+    filtered_pois += filter(lambda x: x['distance_log'] < MAX_RADIUS_LOG, near_pois)[:2]
 
     # weight part
-    total_score = sum(1. / x['distance_sqrt'] for x in filtered_pois)
+    total_score = sum(1. / x['distance_log'] for x in filtered_pois)
     total_weight = 0
     for poi in filtered_pois:
-        poi['weight'] = 1. / (total_score * poi['distance_sqrt'])
+        poi['weight'] = 1. / (total_score * poi['distance_log'])
         total_weight += poi['weight']
     for poi in filtered_pois:
         poi['weight'] = int(round(poi['weight'] * 10. / total_weight))

### 2017-06-16 matching_DB_Doremus/get_csv.py
Artist_POI_paths

@@ -1,191 +1,0 @@
-import collections
-import csv
-import json
-import sys
-from os import listdir
-from os.path import isfile, join
-
-output_path =sys.argv[1]
-
-categories ={1:"low",2:"medium",3:"medium_high",5:"high"}
-
-print output_path
-
-if 'dbpedia' in output_path and 'artists' in output_path:
-    print 1
-    input_path = sys.argv[2]
-    data = json.load(open(input_path))
-    arr = []
-    for key in data:
-        uri_doremus = key.encode('utf-8')
-        rank = data[key]["rank"]
-        uri_dbpedia = data[key]["best"].encode('utf-8')
-        arr.append((uri_doremus,uri_dbpedia,rank))
-    arr.sort(key=lambda tup: -tup[2])
-    with open('RESULTS/'+output_path, 'w+') as f:
-        writer = csv.writer(f)
-        writer.writerow(('uri_doremus','uri_dbpedia','rank'))
-        for t in arr:
-            category = ""
-            writer.writerow(t)
-    dic = {}
-    for key in data:
-        rank = data[key]["rank"]
-        rank = round(rank, 1)
-        if rank in dic:
-            dic[rank] = dic[rank] + 1
-        else:
-            dic[rank] = 0
-    odic = collections.OrderedDict(sorted(dic.items()))
-    with open(output_path, 'w+') as f:
-        writer = csv.writer(f)
-        writer.writerow(("score","count","category"))
-        for k in odic:
-            category = ""
-            for c in categories:
-                if k < c:
-                    category = categories[c]
-                    break
-            t = (k,odic[k],category)
-            writer.writerow(t)
-
-
-elif 'dbpedia' in output_path and 'works' in output_path:
-    print 2
-    input_path = sys.argv[2]
-    data = json.load(open(input_path))
-    arr = []
-    for key in data:
-        uri_doremus = key.encode('utf-8')
-        rank = data[key]["rank"]
-        uri_dbpedia = data[key]["best"].encode('utf-8')
-        arr.append((uri_doremus,uri_dbpedia,rank))
-    arr.sort(key=lambda tup: -tup[2])
-    with open('RESULTS/'+output_path, 'w+') as f:
-        writer = csv.writer(f)
-        writer.writerow(('uri_doremus','uri_dbpedia','rank'))
-        for t in arr:
-            category = ""
-            writer.writerow(t)
-    dic = {}
-    for key in data:
-        rank = data[key]["rank"]
[…]

### 2017-06-16 matching_DB_Doremus/old_stuff/get_csv.py

@@ -1,0 +1,191 @@
+import collections
+import csv
+import json
+import sys
+from os import listdir
+from os.path import isfile, join
+
+output_path =sys.argv[1]
+
+categories ={1:"low",2:"medium",3:"medium_high",5:"high"}
+
+print output_path
+
+if 'dbpedia' in output_path and 'artists' in output_path:
+    print 1
+    input_path = sys.argv[2]
+    data = json.load(open(input_path))
+    arr = []
+    for key in data:
+        uri_doremus = key.encode('utf-8')
+        rank = data[key]["rank"]
+        uri_dbpedia = data[key]["best"].encode('utf-8')
+        arr.append((uri_doremus,uri_dbpedia,rank))
+    arr.sort(key=lambda tup: -tup[2])
+    with open('RESULTS/'+output_path, 'w+') as f:
+        writer = csv.writer(f)
+        writer.writerow(('uri_doremus','uri_dbpedia','rank'))
+        for t in arr:
+            category = ""
+            writer.writerow(t)
+    dic = {}
+    for key in data:
+        rank = data[key]["rank"]
+        rank = round(rank, 1)
+        if rank in dic:
+            dic[rank] = dic[rank] + 1
+        else:
+            dic[rank] = 0
+    odic = collections.OrderedDict(sorted(dic.items()))
+    with open(output_path, 'w+') as f:
+        writer = csv.writer(f)
+        writer.writerow(("score","count","category"))
+        for k in odic:
+            category = ""
+            for c in categories:
+                if k < c:
+                    category = categories[c]
+                    break
+            t = (k,odic[k],category)
+            writer.writerow(t)
+
+
+elif 'dbpedia' in output_path and 'works' in output_path:
+    print 2
+    input_path = sys.argv[2]
+    data = json.load(open(input_path))
+    arr = []
+    for key in data:
+        uri_doremus = key.encode('utf-8')
+        rank = data[key]["rank"]
+        uri_dbpedia = data[key]["best"].encode('utf-8')
+        arr.append((uri_doremus,uri_dbpedia,rank))
+    arr.sort(key=lambda tup: -tup[2])
+    with open('RESULTS/'+output_path, 'w+') as f:
+        writer = csv.writer(f)
+        writer.writerow(('uri_doremus','uri_dbpedia','rank'))
+        for t in arr:
+            category = ""
+            writer.writerow(t)
+    dic = {}
+    for key in data:
+        rank = data[key]["rank"]
[…]

### 2017-06-16 matching_DB_Doremus/old_stuff/useful_functions/useful_functions.py

@@ -1,0 +1,155 @@
+import urllib2
+import geocoder
+import re
+import os
+import os.path
+import json
+
+def computeProb(number,start,end):
+    if number < 20:
+        return float(number**2)/400
+    elif end - number < 6:
+        diff = end - number 
+        return 1.0 - 4/float(diff)
+    else:
+        return 1
+
+def StringMatching(str1,str2,op):
+    c1 = str1.upper()==str2.upper()
+    c1_cs = str1==str2
+    c2 = re.search(str1, str2, re.IGNORECASE)
+    c3 = re.search(str2, str1, re.IGNORECASE)
+    c2_cs = re.search(str1, str2)
+    c3_cs = re.search(str2, str1)
+    if op == 'equal':
+        return c1
+    elif op == 'equal_cs':
+        return c1_cs
+    elif op == 'contains':
+        return c1 or c2 or c3
+    elif op == 'contains_cs':
+        return c1_s or c2_s or c3_s
+
+def isInText(term,text):
+    if term in text:
+        return 1.0
+    else:
+        terms = term.split(' ')
+        n_terms = len(terms)
+        vote = 0.0
+        for t in terms:
+            if t in text:
+                vote += 1.0
+        penalty = 0.1 + 0.2/n_terms
+        if vote > 0.0:
+            return vote/n_terms - penalty
+        else:
+            return vote
+
+def YearDistance(year_1,year_2):
+    distance = float(abs(int(year_1) - int(year_2)))
+    if distance == 0.0:
+        return 1.0
+    else:
+        d = 1/distance
+        if d > 0.7:
+            return 0.7
+        else:
+            return 1/distance
+    
+
+
+def JSONtoDictionary(path):
+    json_data=open(path)
+    data = json.load(json_data)
+    final_dict = {}
+    if 'dbpedia' in path:
+        res = data["results"]["bindings"]
+        for r in res:
+            uri = r["s"]["value"].encode('utf-8') 
+            names_u = r["labels"]["value"].split('|||')
+            for name_u in names_u:
+                name = name_u.encode('utf-8')
+                final_dict[name] = uri
+    elif 'wikidata' in path:
+        for r in data:
+            uri = r["s"].encode('utf-8')
+            names_u = r["labels"]["value"].split('|||')
+            for name_u in names_u:
+                name = name_u.encode('utf-8')
+                final_dict[name] = uri
+    return final_dict        
+
+
[…]

### 2017-06-16 matching_DB_Doremus/useful_functions/useful_functions.py

@@ -1,155 +1,0 @@
-import urllib2
-import geocoder
-import re
-import os
-import os.path
-import json
-
-def computeProb(number,start,end):
-    if number < 20:
-        return float(number**2)/400
-    elif end - number < 6:
-        diff = end - number 
-        return 1.0 - 4/float(diff)
-    else:
-        return 1
-
-def StringMatching(str1,str2,op):
-    c1 = str1.upper()==str2.upper()
-    c1_cs = str1==str2
-    c2 = re.search(str1, str2, re.IGNORECASE)
-    c3 = re.search(str2, str1, re.IGNORECASE)
-    c2_cs = re.search(str1, str2)
-    c3_cs = re.search(str2, str1)
-    if op == 'equal':
-        return c1
-    elif op == 'equal_cs':
-        return c1_cs
-    elif op == 'contains':
-        return c1 or c2 or c3
-    elif op == 'contains_cs':
-        return c1_s or c2_s or c3_s
-
-def isInText(term,text):
-    if term in text:
-        return 1.0
-    else:
-        terms = term.split(' ')
-        n_terms = len(terms)
-        vote = 0.0
-        for t in terms:
-            if t in text:
-                vote += 1.0
-        penalty = 0.1 + 0.2/n_terms
-        if vote > 0.0:
-            return vote/n_terms - penalty
-        else:
-            return vote
-
-def YearDistance(year_1,year_2):
-    distance = float(abs(int(year_1) - int(year_2)))
-    if distance == 0.0:
-        return 1.0
-    else:
-        d = 1/distance
-        if d > 0.7:
-            return 0.7
-        else:
-            return 1/distance
-    
-
-
-def JSONtoDictionary(path):
-    json_data=open(path)
-    data = json.load(json_data)
-    final_dict = {}
-    if 'dbpedia' in path:
-        res = data["results"]["bindings"]
-        for r in res:
-            uri = r["s"]["value"].encode('utf-8') 
-            names_u = r["labels"]["value"].split('|||')
-            for name_u in names_u:
-                name = name_u.encode('utf-8')
-                final_dict[name] = uri
-    elif 'wikidata' in path:
-        for r in data:
-            uri = r["s"].encode('utf-8')
-            names_u = r["labels"]["value"].split('|||')
-            for name_u in names_u:
-                name = name_u.encode('utf-8')
-                final_dict[name] = uri
-    return final_dict        
-
-
[…]

### 2017-06-17 report/paper.tex
update report

@@
 %
-% Instructions for using this template:
-% This title page is capable of being compiled as is. This is not useful for 
-% including it in another document. To do this, you have two options: 
-%
-% 1) Copy/paste everything between \begin{document} and \end{document} 
-% starting at \begin{titlepage} and paste this into another LaTeX file where you 
-% want your title page.
-% OR
-% 2) Remove everything outside the \begin{titlepage} and \end{titlepage} and 
-% move this file to the same directory as the LaTeX file you wish to add it to. 
-% Then add \input{./title_page_1.tex} to your LaTeX file where you want your
-% title page.
-%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\includegraphics[scale=0.8]{logo.jpg}\\ % Include a department/university logo - this will require the graphicx package
+\includegraphics[scale=0.8]{images/logo.jpg}\\ % Include a department/university logo - this will require the graphicx package
 
@@
 \section{Introduction}
-todo: change
-Most of the available music recommenders suggest music without taking into consideration the user’s context, e.g., her mood, current location, activity. 
+Most of the available music recommender systems suggest music without taking into consideration the user’s context.
+This means that a generic recommender system will propose the same set of songs regardless of the user mood, location, activity.
 Finding music that suits a POI can be viewed as a context-aware recommendation problem, the place being the context for consuming the recommendation.         
@@
 However, with the advent of the Semantic Web, new opportunities arise to face the above difficulties.
+We will show that using generic semantic datasets we can recommend artists that are linked to the user location.
 
@@
 \subsection{Contributions}
+In this project we show a new approach for finding artists linked to a place of interest (POI).
+We propose an entity linking framework built upon DBpedia, 3cixty, and Doremus that is able to reach editorial accuracy in the interlinking process.
+Furthermore we present a graph exploration algorithm that is able to find deep connections in an short time and discriminate between them by looking at those that can be the most interesting.
 
@@
 \subsection{Problem description}
-Interlinking different datasets is not trivial, many approaches that aimed at a semi-supervised interlinking has been proposed, but this is still a topic of research.
-The worst part of this is actually the class definition, in fact specialized datasets tend to have a very strict ontology, while DBpedia does not enforce it.
-This means that not all music artists are composers, and that not all places in nice are linked to nice.
-Since Nice is a middle city, we cannot allow to loose some matchings and we need to carefully analyze the DBpedia ontology.
+Interlinking different datasets is not trivial, many approaches that aimed at a semi-supervised interlinking have been proposed, but this is still an active research topic.
+One of the main problems that must be faced in an interlinking process is the ontology definition, in fact specialized datasets tend to have a very strict ontology, while DBpedia does not enforce it.
+This means that in the case of POIs, not all places in nice are linked to nice, thus it is difficult to even correctly define a POI in Nice.
+Since we are dealing with a medium sized city such as Nice, we can't allow to loose some matchings and we need to carefully analyze the DBpedia ontology in order to leave out a minimum part of Nice POIs.
 
@@
 \item We perform a query that looks for all Geoentities that are in the area of nice. An entity is in the area of Nice if its coordinates are in a custom box that contains all the area of Nice.
-Unfortunately there are many POIs that are without coordinates,so they are not selected with this query.
-\item We perform some queries that get in a recursive way all entities that have as a parent the category of nice or nice and that are related to a place.
-The relation to a place is a list of classes that is done by hand and could be subjected to refinements.
+Unfortunately there are many POIs that are without coordinates,so they are not selected by this query.
+\item We take all resources that have as a parent either the Nice resource or the Category:Nice resource.
+Then we repeat this operation for each subcategory of Category:Nice in a recursive way.
+Among these resources, we keep those which type is in a set of classes defined by hand.
 \end{enumerate}
@@
 Moreover, most of POIs in wikidata have coordinates, so we can get them with a single query.
-Since wikidata supports complex geo-based queries, we made a query that looked for all POIs in a range of 25 Kilometers from the center of Nice.
+Since wikidata supports complex geo-based queries, we can make a query that looks for all POIs in a range of 25 Kilometers from the center of Nice.
 \subsection{Entity Linking process}
-Now that we have locally all our entities, we can link them.
+In order to link our two set, we copy them locally and then we perform the linking process.
 Having the entities locally is crucial, in fact it allows us to make way more complex operations respect to those that can be done with SPARQL queries.
@@
 The first phase is to actually get the interesting properties of the entities.
-Regarding those that come from DBpedia, we take use only the labels.
-We do not use coordinates because not all entities have them and we do not want to bias our algorithm using DBpedia coordinates, which is known that are not very accurate.
-Regarding the labels, we take all labels from all entities, in this way we are going to do a multilingual match because we know that sometimes this can make the difference.
-Respect to Dbpedia, 3cixty entities have very accurate coordinates, and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.
+Regarding those that come from DBpedia, we use only the labels.
+Regarding the labels, we take them in all the available languages.
+In this way we can do a multilingual match that improves our accuracy.
+Since this is not intuitive, here is an example.
+DBpedia labels:
+'Conservatory of Nice'
+'Conservatoire de Nice'
+3cixty label: 'Conservatoire de nice'
+In this case if we use the english label, we do not obtain a perfect match, while with the french label we obtain a perfect match.
+
+We do not use coordinates because not all entities have them. Moreover, we have seen experimentally that using the DBpedia coordinates we obtain worse results because they are inaccurate.
+
+Regarding 3cixty entities, they have very accurate coordinates, and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.
+
 \subsubsection{Transformations}
-At this point of the pipeline, we have labels that are encoded in unicode utf-8.
+At this point of the pipeline, we have labels that are encoded into unicode utf-8.
 Common similarity metrics accepts only plain ASCII strings as input, so we need to convert them into ASCII.
 Since utf-8 can represent way more characters than ASCII, we need to strip non ASCII characters from our labels.
-This is done in an intelligent way using the python library 'unidecode', that is able to convert from unicode to ASCII deleting only few characters.
-For example, an accented letter like 'è' can't be represented in ASCII.
-Most of the libraries delete all incompatible characters, while 'unidecode', when possible, converts it to the nearest ASCII character, in this case 'è' is converted to 'e'.
+This is done in an intelligent way using the python library 'unidecode', that is able to convert from unicode to ASCII by changing or deleting a minimum set of characters.
+For example, an accented letter like 'è' can't be represented in ASCII, and most of the libraries simply delete it, while 'unidecode' converts it to the nearest ASCII character: in this case 'è' is converted to 'e'.
 In this way we can retain most of the original information after this conversion process.
@@
 Some similarity metrics are extremely sensitive to noise.
-For example, when we use simple levenstein distance between ('aeroport','aeroport nice') is 5, while the distance ('aeroport','port') is 4.
+For example, when we use simple levenstein distance between ('airport','airport nice') is 5, while the distance ('airport','port') is 4.
 This is enough to raise some concerns: the simple addition of the city name can turn a perfect match into a mediocre one.
-In order to fix this problem we add the city name to all the labels where this is not present.
-The third step is to strip all not alphabetical characters and to convert to lowercase all strings, this offcourse gives us cleaner strings to compare.
+In order to fix this problem we add the city name to all the labels where it is not present.
+The third step is to strip all non alphabetical characters and to convert to lowercase all strings, this off course gives us cleaner strings to compare.
+
+The whole transformation pipeline aims at maximizing the similarity measure between correct matches.
+This is extremely important, because later we can set a threshold to separate matches that have a good confidence from matches with a low confidence.
+If we do not perform the transformation phase, we would obtain correct matches that have the same confidence of the incorrect ones because we have basically some noise in all the strings.
 
 \subsubsection{Similarity measures and matching algorithm}
-Now that strings are clean, we can proceed to the matching.
+Now that strings are clean, we can proceed to the actual matching.
 A first problem rises: we want to match a 3cixty poi to a dbpedia poi, or we want to match a dbpedia poi to a 3cixty poi?
 In the first case we are sure that each 3cixty poi will be matched to a single dbpedia poi, but there is the risk that multiple 3cixty poi are matched to the same DBpedia poi.
-Alternatively, we match are sure that each DBpedia poi is matched to at most a 3cixty poi, but there is the risk that two DBpedia poi are matched to the same 3cixty poi.
+Alternatively, we are sure that each DBpedia poi is matched to at most a 3cixty poi, but there is the risk that many DBpedia poi are matched to the same 3cixty poi.
 Regarding DBpedia, we are sure that POIs are univoque, while we know that for the same POI, in 3cixty there are multiple ones.
 Since at the end we will be using 3cixty coordinates, we opt for the first choice: if a DBpedia poi will be matched to multiple 3cixty pois, than we will follow an heuristic to choose the best match.
-Regarding similarity metrics among strings, there are multiple ones, but most of them are based on levenstein distance.
-Since each distance has its privileges and defects, we use multiple similarity measures, taken from the 'fuzzy wuzzy' python library.
-For each 3cixty poi get the label and calculate the different similarity metric against all labels of all DBpedia POIs.
+
+Regarding the similarity metric among strings, we use multiple similarity measures based on levenstein distance.
+We chose to use different metrics because we have seen experimentally that in this specific case, strings that represents POIs, a single similarity metric is not enough.
+From a technical point of view, we used a set of the similarity metrics provided by the 'fuzzywuzzy' python library.
 
 \subsubsection{Aggregations}
-The aggregation algorithm can be described as follow:
+Until now, we took one by one the 3cixty labels and we calculated the different similarity metrics against all DBpedia labels.
+
+The aggregation algorithm is run for each 3cixty POI and can be described as follow:
 \begin{enumerate}
-\item For each similarity metric, take the three best matches and for them average the score of all similarity measures
-\item The final match is the POI corresponding with the string with the highest score
+\item For each similarity metric, take the three best matching labels and for each of them, calculate the average of all the similarity metrics.
+\item The final match is the POI corresponding with the label with the highest score.
 \end{enumerate}
@@
 Now that the matching is done, we need to filter our results.
-The first filter to do is to eliminate all those matches that match with Nice, but that have a label different from Nice.
-This usually happens because we added Nice to all strings.
-That addition was helpful, and it also created a safe default that now can be easily filtered.
-Most of these match are acronym that match with Nice e.g. 'ATP Nice' matches with Nice because half of the string is Nice and is artificial, because we added it.
+The first operation to do is to eliminate all those POIs that match with Nice, but that have a label different from Nice.
+This happens because we added Nice to all the strings.
+That addition was helpful, and it also created a safe default that we can easily filter.
+Most of these POIs filtered in this way are acronyms that match with Nice e.g. 'ATP Nice' matches with Nice because half of the string is Nice and is artificial, because we added it.
 
-At this point we filter out all matches with a score below a given threshold.
+The second operation to perform is the filtering based on the average score.
+The average score can be interpreted as a confidence. Intuitively, high scores corresponds to correct matches, while low scores corresponds to bad matches.
+The importance of the selction, transformation, similarity metric and aggregation pipeline is extremely high, in fact we want a confidence which we can trust.
+An untrusted confidence gives us no additional informations about good matches and bad matches.
+At this point we filter all matches with a score below a given threshold.
 
-Then, we have probably multiple 3cixty POIs connected to a single DBpedia POI.
-In order to choose the most representative 3cixty POI, from whom we will take the coordinates, we have few possibilities:
+Now we are at the half of our work, for each 3cixty POI we have a link to a DBpedia POI, but we might have multiple 3cixty POIs linked to the same DBpedia POI.
+We aim to a 1 to 1 relation, so we need to choose among a group of 3cixty POIs linked to the same DBpedia POI, the most representative.
+We have few possibilities:
 \begin{enumerate}
-\item K-medoids: We can actually cluster our points and look at the rapresentant of the biggest cluster 
+\item Pick the POI that minimize the distance to all the other POIs, this is like applying the K-medoids clustering with K equal 1.
 \item Pick the POI which is nearest to the center
 \item Pick the POI which is nearest to the DBpedia POI, if coordinates are available
-\item Pick the POI which is nearest to the position found on OpenStreetMap
+\item Pick the POI which is nearest to the position found on Google Maps
 \item Link our data to GeoNames, a dataset of POIs
 \end{enumerate}
-The first method might be the best one, but it requires several precautions.
-The second method is baiased towords pois in the center.
-The third method can work only with POIs with coordinates, and gives good results if DBpedia coordinates are good, but we already know that this is not true.
-The fourth method might be the best one, but we need to exit from the semantic world and hope that the API gives a good result, here the problem is that we have no control over the API.
-The fourth method can work, but we would need to design another linking process.
+The first method might be the best one, but it works if most of the POIs are actually clustered. If they are very sparse it does not work.
+The second method is biased towards POIs near the center.
+The third method can work only with DBpedia POIs with coordinates, and gives good results if DBpedia coordinates are good, but we already know that this is not true.
+The fourth method might be the best one, but we need to look outside the semantic world and trust the Google Maps API.
+Here the problem is that we have no control over the API, but we  know that Google Maps is very good at matching a name with a place.
+The fourth method could be the best one, in fact we can exploit GeoNames coordinates that are trusted. The main problem is the fact that not all DBpedia POIs have a corresponding POI.
 
-For simplicity and reliability, we decided to use both OpenStreetMap API and Google Map API, in this way we have a much bigger confidence.
+For simplicity and reliability, we used the Google Maps API because we trust it.
+We use the API by sending the DBpedia label to the service, the response contains the coordinates of the POI associated to the DBpedia label.
+At this point we select the nearest 3cixty POI and we keep it if the distance is less than 2 kilometers.
+\subsection{Evaluation (Google Map / OpenStreetMap)}
+The evaluation part is done using the Google Maps API.
+As done before, we use the distance between the 3cixty POI coordinates and the POI coordinates provided by the API.
+Since we used the Google Maps API during our process, we expect that distances are low, in fact we know that each POI distance is less than 2 kilometers.
+What we want to check here is the distance distribution.
+\begin{figure}
+\centering
+\includegraphics[]{images/distance.png}\\
+%\caption{\label{fig:distance}This is a figure caption.}
+\end{figure}
+Looking at the distance distribution we note that most of the POIs are actually near to the Google Maps coordinates, while for few POIs this is not true.
+The main reason for this is the inherent unprecision that arise when wedefine a POI which occupies a big surface with coordinates that refer to a specific point.
+For example the surface of the airport of Nice is quite big and different services can locate it in different points of his surface.
+In the case of the airport, the distance is actually 500 meters.
+This means that if it is true that most of the POIs are under 500 meters, we can't use this as a threshold because we would leave out a large part of the correct POIs.
 
-We make a request with the DBpedia label to the API, and we keep the POI which is nearest to one of them, in this case the minimum distance wins.
-If the distance is greater than a chosen threshold (500 meters), then the match is filtered out.
+At the end of our POI linking process we have 58 POIs that will be matched with the artists.
 
-\subsection{Evaluation (Google Map / OpenStreetMap)}
-The evaluation part is done using both the Google Map and OpenStreetMap.
-We calculated the Medium Square Error of the POIS to the positions recovered with the APIs, the error distance is the haversine distance.
 \section{Interlinking and enriching Artists}
 \subsection{Problem description}
+DBpedia contains Artists and their works in a disorganized way.
+This consist a huge limit because we do not trust the data that we have in DBpedia.
+Even the simpler operations, such as finding all artists and all songs are extremely difficult due to the non-strict ontology of DBpedia.
+In order to have some order, we use DOREMUS, which contains trusted informations about artists and songs in a strict ontology.
+
 \subsection{Datasets: DOREMUS, DBpedia, Wikidata}
 \subsubsection{DOREMUS}
-3cixty is a semantic dataset that contains aggregated informations of POIs and events.
-The dataset is the result of an aggregation process that join the POI informations from different datasets e.g.
-Facebook, Foursquare, Yelp \dots
-In this project 3cixty is used as a trusted source of POIs for Nice.
-POIs have many informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint selecting the Nice city.
+DOREMUS is a semantic dataset that aims to a fine description of musical works in the fields of traditional and classical music: related musical or creation events, relations to authors, cultural background, interpretations, social functions, etc.
+With DOREMUS we can have absolute trust in the data regarding artists, and we can then found corresponding artists in DBpedia with a custom linking process.
+
+Retrieving all artists from DOREMUS is extremely easy, in fact we just need to ask for the Persons in the datasets. Then from these we filter persons that actually created at least a work.
+
 \subsubsection{DBpedia}
-DBpedia is a project that aims at connecting the semantic world. We used it to get the POIs in Nice.
-In order to get the POIs from DBpedia, it is necessary to perform SPARQL queries against the SPARQL endpoint.
-POIs are retrieved using two different sparql queries that target different kind of resources:
-\begin{enumerate}
-\item We perform a query that looks for all Geoentities that are in the area of nice. An entity is in the area of Nice if its coordinates are in a custom box that contains all the area of Nice.
-Unfortunately there are many POIs that are without coordinates,so they are not selected with this query.
-\item We perform some queries that get in a recursive way all entities that have as a parent the category of nice or nice and that are related to a place.
-The relation to a place is a list of classes that is done by hand and could be subjected to refinements.
-\end{enumerate}
+Unfortunately DBpedia does not have a strict definition of a musical Artist.
+This means that retrieving artists from DBpedia is not trivial.
+What we do it to get all Persons, which are quite a lot.
+Most of them are not artists, and we filter them later.
+
+todo: lorenzo
+
 \subsubsection{Wikidata}
-Wikidata is a project that aims at connecting the semantic world.
-We used it to get the POIs in Nice.
-Respect to DBpedia, Wikidata has a well defined ontology that is strictly enforced.
-This means that it is easier to select what we want.
-Moreover, most of POIs in wikidata have coordinates, so we can get them with a single query.
-Since wikidata supports complex geo-based queries, we made a query that looked for all POIs in a range of 25 Kilometers from the center of Nice.
+If Wikidata was extremely reliable for the POIs, it is not that strict about musical artists, in fact we need to get all persons and then filter them in some way, looking at classes that are related to music.
 
 \subsection{Entity Linking process (+ ElasticSearch)}
+Here we do the same thing that we did with POIs, we need to extract interesting properties from our entities and then use them to find the correct matches. 
+With POIs we had one hundred entities from DBpedia, and we could do all operations locally.
+Here we would like to do the same, but we are dealing with millions of persons, and retrieving them and doing all operations locally is not feasible.
+For each artist in DOREMUS, we would compare his label with the label of millions of persons, and in Doremus we have thousands of artists.
+
+In order to speedup operations, we use a dump of DBpedia indexed on ElasticSearch. This allow us to perform all the comparison in a fraction of time thanks to the use of indexes.
+
+todo: Lorenzo
+
 \subsubsection{Properties}
@@
 \subsection{Evaluation}
-todo: add source of isni
-The evaluation of the found links is done by comparing the found links with those provided by ISNI.
+The evaluation of the found links is done by comparing them with those provided by ISNI.
 ISNI is the ISO certified global standard number for identifying the millions of contributors to creative works.
@@
 
-todo: table with cool statistics
-todo: graph image
+\begin{figure}
+\centering
+\includegraphics[]{images/counts_artists.png}\\
+%\caption{\label{fig:distance}This is a figure caption.}
+\end{figure}
+
+Since the matching confidence vary with the threshold, we can plot all the important counts and metrics respect to the threshold used.
+
+In the figure above there are all the counts of the important sets that describe our matching.
+Trues indicates the number of doremus entities matched by ISNI, they are ~3500 and of course they are independent from the threshold.
+Predicted indicates the number of doremus entities matched by us, the number vary with the confidence, there are different drops that corresponds to crucial thresholds defined by our matching algorithm.
+The most important thing is that their number goes from ~3000 to ~6000, this indicates that we are matching way more entities than ISNI.
+Doremus intersection represents the number of entities that are matched from both ISNI and us.
+This shows us that there is a part of the doremus entities that ISNI matches and that we are not able to match.
+Now, the following sets are all calculated from the intersection set, in fact we cannot compare the matching performances using entities that are not present in both sets.
+Equal show the number of correct matches, we see that this basically overlap with the intersection set, meaning that ISNI and our algorithm match a doremus entity with the same DBpedia entity.
+Since ISNI matches have a professional validity, this means that we can have a great confidence in the matches produced by our algorithm.
+
+Since equal and doremus intersection are not exactly the same, it means that either our algorithm or ISNI are doing a wrong match.
+Looking more closely we saw that in some cases ISNI matches were wrong, especially in corner cases, where there were two persons with the same name.
+This corner cases can fool also a professionist, and this is the reason why in our algorithm we embedded the comparison of birthdate and deathdate in DBpedia with those present in Doremus.
+This allowed us to disambiguate between different persons with the same name.
+In other cases this was not enough, there are persons with the same name and birth/death dates, or whose dates are not available, that can be correctly classified looking at other fields, such as their profession.
+
+\begin{figure}
+\centering
+\includegraphics[]{images/metrics_artists.png}\\
+%\caption{\label{fig:distance}This is a figure caption.}
+\end{figure}
+Looking at the usual metrics, we see that they are extremely high for this kind of match. This means that we are doing an almost perfect match.
 
@@
 \subsection{Problem description}
-todo: add citations
 Once we have a direct mapping between entities that comes from specialized datasets and DBpedia, we actually need to link POIs and Artists.
@@
 The whole problem can be solved by writing a single query that finds a path of a given depth between two resources.
-This approach works well when datasets are relatively small and the two entities are two concepts that are semantically close.
-Instead, in our case we have concepts that are definetly far from each other, which implicates an high depth of an eventual path, and most importantly, we need to match hundreds of POIs with thousands of artists, This makes means that at the end the whole process will be repeated 100.000 times.
+This approach works well when datasets are relatively small or the two entities are two concepts that are semantically close.
+Instead, in our case we have concepts that are absolutely far from each other, which implicates an high depth of an eventual path, and most importantly, we need to match hundreds of POIs with thousands of artists, This makes means that at the end the whole process will be repeated 25.000 times.
 \subsection{Related work (Relfinder)}
@@
 plore personalization approaches that translate user’s pref-
-erences into these weights. Furthermore, we intend to work
-
-on identifying and exploiting other arbitrary semantic rela-
-tions between POIs and musicians, e.g. direct relations such
-
-as ‘Gustav Mahler was the director of Vienna State Opera’,
-
-and complex non-directed relations such as ‘Ana Bel ́en (a fa-
-mous Spanish singer) composed a song whose lyrics are about
-
-La Puerta de Alcal ́a (a well-known POI in Madrid, Spain)’.
-
-We will search for these relations in different Linked Data
-
-repositories, and will use available tools such as RelFinder
-
-[7]. It is also important to better explore and evaluate strate-
+erences into these weights.
+It is also important to better explore and evaluate strate-
 gies to initialize the importance weights of the relations and
@@
 \centering
-\includegraphics[width=0.5\textwidth]{frog.jpg}
+\includegraphics[width=0.5\textwidth]{images/frog.jpg}
 \caption{\label{fig:frog}This is a figure caption.}

### 2017-06-18 server/util.py
correct server distance_log key error

@@ -14,7 +14,7 @@ def get_near_pois(source, original_pois):
         def add_distance(point):
             point['distance'] = vincenty(src, (float(point['latitude']), float(point['longitude']))).meters
             point['distance'] += 10
-            point['distance_sqrt'] = log2(point['distance'])
+            point['distance_log'] = log2(point['distance'])
             return point
         return add_distance
 

### 2017-06-18 server/util.py
max distance in playlist_name creation is 2 km

@@ -20,7 +20,7 @@ def get_near_pois(source, original_pois):
 
 
 
-    MAX_RADIUS = 1000
+    MAX_RADIUS = 2000
 
     MAX_RADIUS_LOG = log2(MAX_RADIUS)
 

### 2017-06-20 server/server.py
update report

@@ -13,6 +13,7 @@ poi_artists = database_helper.load_poi_artists()
 # load pois
 pois = database_helper.load_pois(poi_artists)
 print(len(pois))
+print(pois)
 
 # load playlists
 playlist_collection = database_helper.PlaylistCollection(pois, poi_artists)

### 2017-06-20 report/report.tex
update gitignore

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% University Assignment Title Page 
% LaTeX Template
% Version 1.0 (27/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% WikiBooks (http://en.wikibooks.org/wiki/LaTeX/Title_Creation)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title{Title page with logo}
%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\linespread{1.1}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{cite}
\usepackage[nottoc]{tocbibind}
\usepackage{listings}
\setcounter{secnumdepth}{4}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
            base/.style = {rectangle, rounded corners, draw=black,
                           minimum width=4cm, minimum height=1cm,
                           text centered, font=\sffamily}
}
\begin{document}

\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\center % Center everything on the page

%----------------------------------------------------------------------------------------
% HEADING SECTIONS
%----------------------------------------------------------------------------------------

\textsc{\LARGE EURECOM}\\[1.5cm] % Name of your university/college
%\textsc{\Large Major Heading}\\[0.5cm] % Major heading such as course name
%\textsc{\large Minor Heading}\\[0.5cm] % Minor heading such as course title

%----------------------------------------------------------------------------------------
% TITLE SECTION
%----------------------------------------------------------------------------------------

\HRule \\[0.4cm]
{ \huge \bfseries Music Recommendation when Exploring a City}\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

%----------------------------------------------------------------------------------------
% AUTHOR SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Authors:}\\
Lorenzo \textsc{Canale} % Your name
\newline
Fabio \textsc{Ellena} % Your name
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
Pasquale \textsc{Lisena} \\ % Supervisor's Name
Raphaël  \textsc{Troncy} % Supervisor's Name
\end{flushright}
\end{minipage}\\[2cm]

% If you don't want a supervisor, uncomment the two lines below and remove the section above
%\Large \emph{Author:}\\
%John \textsc{Smith}\\[3cm] % Your name

%----------------------------------------------------------------------------------------
% DATE SECTION
%----------------------------------------------------------------------------------------

%{\large \today}\\[2cm] % Date, change the \today to a set date if you want to be precise

%----------------------------------------------------------------------------------------
% LOGO SECTION
%----------------------------------------------------------------------------------------

\includegraphics[scale=0.8]{images/logo.jpg}\\ % Include a department/university logo - this will require the graphicx package

%----------------------------------------------------------------------------------------

\vfill % Fill the rest of the page with whitespace

\end{titlepage}
\begin{abstract}
Abstract: 
Our project aims at making the user discover the existing connections that link music to a Place, by stimulating his curiosity proposing noncommon relations. In this project, we show a new approach for finding artists linked to a place of interest (POI). We propose an entity linking framework built on top of DBpedia, 3cixty, and DOREMUS that is able to reach editorial accuracy in the interlinking process. Furthermore, we present a graph exploration algorithm that is able to find deep connections in a short time and discriminate between them by looking at those that can be the most interesting. 
\end{abstract}
\newpage

\tableofcontents
\newpage

\section{Introduction}
Most of the available music recommender systems suggest music without taking into consideration the user’s context \cite{Knees:2013:SMS:2559928.2542206}. This means that a generic recommender system will propose the same set of songs regardless of the user mood, location, activity.
Finding music that suits a POI can be viewed as a context-aware recommendation problem, the place is the context for consuming the recommendation.                    
The main challenge that one must face when addressing the above-mentioned goal is related to the fact that POIs and music are two rather different domains, and there is no obvious way to match such heterogeneous items. However, with the advent of the Semantic Web, new opportunities arise to face the above difficulties. We will show that using generic semantic datasets we can recommend artists that are linked to the user location.

\subsection{Motivation and context}
In the past, many tried to link POIs and music in many different ways. managed to link music and POIs by using a common set of tags that describe emotional properties both for music and POIs \cite{Kaminskas:2013:LMR:2507157.2507180}.
This method was completely supervised, in fact it required the definition of a set of emotions for songs and POIs. This operation has been done by hand and is hardly scalable.
In another project \cite{Kaminskas:2012:KMR:2390848.2390854}, a semantic approach has been used by restricting the subspace of DBpedia \footnote{DBpedia: http://wiki.dbpedia.org/} by identifying classes related to the domains of interest, and the relations existing between instances of such classes. In this way, they managed to find relations in a set of paths constrained to pass belong to those classes. Looking at the future works proposition, they proposed the idea to exploit arbitrary semantic relations between POIs and musicians.
In order to do this, they proposed to use Relfinder \cite{Heim:2009:RRR:1695324.1695351} and set the connections' weights using an heuristic.  In fact, one of the bad things was that connections weights were assigned by experts and were not provided in the paper.
Our intention is to build our approach on top of this paper and find relations in a completely unsupervised way: this means that we intend to define a pathfinder that finds paths and a path discriminator that selects the interesting relations. We aim at reducing the need for human intervention in defining classes and weights with the hope that this approach will be completely data driven and easily scalable to different cities. Moreover, we will use different datasets with the intention to exploit their implicit advantages and obtain overall a better recommender system.

\subsection{Research problems}
Finding relations inside DBpedia is a known problem which has been solved in the past. So we could simply look for POIs and Artists in DBpedia and then link them using known algorithms.
Unfortunately, DBpedia is not perfect: it is true that it contains POIs and Artists, but these entities are not cleanly defined, they usually contain dirty data that can tremendously affect our performances.
On the other side, POIs and Artists can be found in highly specialized datasets, but unfortunately, they do not contain links to each other, and even worse they are not linked to DBpedia. This means that by using these databases alone we cannot find relations.
What is done in this cases is to link highly specialized datasets to DBpedia, in this way we can exploit the advantages of both worlds: highly specialized datasets give us confidence and trust in our main entities (POIs and Artists), while DBpedia allows us to find relations between them thanks to its generality.
Once we have our two sets, we need to find paths that link them. This problem has been solved in the past with Relfinder, a tool that is able to find relations between entities.
What we have seen is that POIs and Artists are generally far from each other, in fact usually we need 5 hops to link them, this is more that the average DBpedia degree and it is also more than what Relfinder can do, in fact, Relfinder query times are too high once we set more that 4 hops. This lead us to create a pathfinder that can work in acceptable times with 100.000 pairs that are far from each other.

\subsection{Contributions}
In this project, we show a new approach for finding artists linked to a place of interest (POI). We propose an entity linking framework built upon DBpedia, 3cixty \footnote{3cixty: https://www.3cixty.com/}, and Doremus \footnote{DOREMUS: http://www.doremus.org/} that is able to reach editorial accuracy in the interlinking process. Furthermore, we present a graph exploration algorithm that is able to find deep connections in a short time and discriminate between them by looking at those that can be the most interesting.

\subsection{Report structure}
The report is divided into five sections, one for each part of the project. The first two parts are about linking external datasets to DBpedia, this is also known as entity linking and we perform it in the optic of enriching our data with the inter-concept links present in DBpedia.
The third treats the Pathfinder, a module of our system that is able to find deep connections between two entities in DBpedia.
The fourth describes the whole implementation of the REST API that allows the application to work smoothly.
The fifth part covers the mobile web application and the technologies involved in its functioning.

\section{Interlinking and enriching POIs}
\subsection{Problem description}
Interlinking different datasets is not trivial, many approaches that aimed at a semi-supervised interlinking have been proposed, but this is still an active research topic.
One of the main problems that must be faced in an interlinking process is the ontology definition, in fact, specialized datasets tend to have a very strict ontology, while DBpedia does not enforce it. This means that in the case of POIs, not all places in nice are linked to nice, thus it is difficult to even correctly define a POI in Nice.
Since we are dealing with a medium sized city such as Nice, we can't allow loosing some matchings and we need to carefully analyze the DBpedia ontology in order to leave out a minimum part of Nice POIs.

\subsection{Datasets: 3cixty, DBpedia, Wikidata}
\subsubsection{3cixty}
3cixty is a semantic dataset that contains aggregated informations of POIs and events. The dataset is the result of an aggregation process that join the POI informations from different datasets e.g. Facebook, Foursquare, Yelp \dots
In this project 3cixty is used as a trusted source of POIs for Nice.
POIs have many informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint selecting the Nice city.
\subsubsection{DBpedia}
DBpedia is a project that aims at connecting the semantic world. We used it to get the POIs in Nice.
In order to get the POIs from DBpedia, it is necessary to perform SPARQL queries against the SPARQL endpoint. POIs are retrieved using two different sparql queries that target different kind of resources:
\begin{enumerate}
\item We perform a query that looks for all Geoentities that are in the area of nice. An entity is in the area of Nice if its coordinates are in a custom box that contains all the area of Nice.
Unfortunately there are many POIs that are without coordinates,so they are not selected by this query.
\begin{lstlisting}
SELECT ?place ?placeLabel ?lat ?long
WHERE {
    ?place geo:lat ?lat.
    ?place geo:long ?long.
    ?place rdfs:label ?placeLabel.
    FILTER(
      xsd:double(?lat)  <= 43.80 &&
      xsd:double(?lat) >= 43.63 &&
      xsd:double(?long) <= 7.36 &&
      xsd:double(?long) >= 7.14
    )
}
\end{lstlisting}
\begin{figure}[!htb]
  \centering 
    \includegraphics[width=0.5\textwidth]{images/Nice.png}
    \caption{Area for POIs selection}
\end{figure}

\item We take all resources that have as a parent either the Nice resource or the Category:Nice resource. Then we repeat this operation for each subcategory of Category:Nice in a recursive way. Among these resources, we keep those which type is in a set of classes defined by hand.
\end{enumerate}
\subsubsection{Wikidata}
Wikidata \footnote{Wikidata: https://www.wikidata.org/} is a project that aims at connecting the semantic world. We used it to get the POIs in Nice. Respect to DBpedia, Wikidata has a well defined ontology that is strictly enforced. This means that it is easier to select what we want. Moreover, most of POIs in wikidata have coordinates, so we can get them with a single query. Since wikidata supports complex geo-based queries, we can make a query that looks for all POIs in a range of 25 Kilometers from the center of Nice.
\subsection{Entity Linking process}
In order to link our two set, we copy them locally and then we perform the linking process. Having the entities locally is crucial, in fact it allows us to make way more complex operations respect to those that can be done with SPARQL queries.
\subsubsection{Properties}
The first phase is to actually get the interesting properties of the entities. Regarding those that come from DBpedia, we use only the labels. Regarding the labels, we take them in all the available languages. In this way we can do a multilingual match that improves our accuracy. Since this is not intuitive, here is an example.
DBpedia labels:
'Conservatory of Nice'
'Conservatoire de Nice'
3cixty label: 'Conservatoire de nice'
In this case if we use the english label, we do not obtain a perfect match, while with the french label we obtain a perfect match.
We do not use coordinates because not all entities have them. Moreover, we have seen experimentally that using the DBpedia coordinates we obtain worse results because they are inaccurate.
Regarding 3cixty entities, they have very accurate coordinates, and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.

\subsubsection{Transformations}
At this point of the pipeline, we have labels that are encoded into unicode utf-8. Common similarity metrics accepts only plain ASCII strings as input, so we need to convert them into ASCII. Since utf-8 can represent way more characters than ASCII, we need to strip non ASCII characters from our labels. This is done in an intelligent way using the python library \textit{'unidecode'}\footnote{Unidecode: https://pypi.python.org/pypi/Unidecode}, that is able to convert from unicode to ASCII by changing or deleting a minimum set of characters. For example, an accented letter like 'è' can't be represented in ASCII, and most of the libraries simply delete it, while \textit{'unidecode'} converts it to the nearest ASCII character: in this case 'è' is converted to 'e'. In this way we can retain most of the original information after this conversion process.

The second step is probably the most important, and is the normalization of names. Some similarity metrics are extremely sensitive to noise. For example, when we use simple levenstein distance between ('airport','airport nice') is 5, while the distance ('airport','port') is 4. This is enough to raise some concerns: the simple addition of the city name can turn a perfect match into a mediocre one. In order to fix this problem we add the city name to all the labels where it is not present.

The third step is to strip all non alphabetical characters and to convert to lowercase all strings, this off course gives us cleaner strings to compare.
The whole transformation pipeline aims at maximizing the similarity measure between correct matches. This is extremely important, because later we can set a threshold to separate matches that have a good confidence from matches with a low confidence. If we do not perform the transformation phase, we would obtain correct matches that have the same confidence of the incorrect ones because we have basically some noise in all the strings.

\subsubsection{Similarity measures and matching algorithm}
Now that strings are clean, we can proceed to the actual matching. A first problem rises: we want to match a 3cixty poi to a dbpedia poi, or we want to match a dbpedia poi to a 3cixty poi? In the first case we are sure that each 3cixty poi will be matched to a single dbpedia poi, but there is the risk that multiple 3cixty poi are matched to the same DBpedia poi. Alternatively, we are sure that each DBpedia poi is matched to at most a 3cixty poi, but there is the risk that many DBpedia poi are matched to the same 3cixty poi.
Regarding DBpedia, we are sure that POIs are univoque, while we know that for the same POI, in 3cixty there are multiple ones.
Since at the end we will be using 3cixty coordinates, we opt for the first choice: if a DBpedia poi will be matched to multiple 3cixty pois, than we will follow an heuristic to choose the best match.

Regarding the similarity metric among strings, we use multiple similarity measures based on levenstein distance. We chose to use different metrics because we have seen experimentally that in this specific case, strings that represents POIs, a single similarity metric is not enough. From a technical point of view, we used a set of the similarity metrics provided by the 'fuzzywuzzy'\footnote{FuzzyWuzzy: https://pypi.python.org/pypi/fuzzywuzzy} python module.

\subsubsection{Aggregations}
Until now, we took one by one the 3cixty labels and we calculated the different similarity metrics against all DBpedia labels. 
The aggregation algorithm is run for each 3cixty POI and can be described as follow:
\begin{enumerate}
\item For each similarity metric, take the three best matching labels and for each of them, calculate the average of all the similarity metrics.
\item The final match is the POI corresponding with the label with the highest score.
\end{enumerate}
Why we don't simply take the average, or the minimum, or the maximum?
The reasoning behind this is that by taking the average we are flattening all the scores, and there is the risk that the string with the highest similarity is a string that is mediocre in all the different metrics. If a string is mediocre in all comparisons, then we do not trust it. Instead, with our methodology we are keeping only those matches that excel in some similarity metric, and then we take the one that performs better on average. We think that in this way we can filter out all those matches with average strings that matches almost anything.

\subsubsection{Filtering}
Now that the matching is done, we need to filter our results.

The first operation to do is to eliminate all those POIs that match with Nice, but that have a label different from Nice. This happens because we added Nice to all the strings. That addition was helpful, and it also created a safe default that we can easily filter.
Most of these POIs filtered in this way are acronyms that match with Nice e.g. 'ATP Nice' matches with Nice because half of the string is Nice and is artificial, because we added it.

The second operation to perform is the filtering based on the average score.
The average score can be interpreted as a confidence. Intuitively, high scores corresponds to correct matches, while low scores corresponds to bad matches.
The importance of the selection, transformation, similarity metric and aggregation pipeline is extremely high, in fact we want a confidence which we can trust. An untrusted confidence gives us no additional informations about good matches and bad matches.
At this point we filter all matches with a score below a given threshold.

Now we are at the half of our work, for each 3cixty POI we have a link to a DBpedia POI, but we might have multiple 3cixty POIs linked to the same DBpedia POI. We aim to a 1 to 1 relation, so we need to choose among a group of 3cixty POIs linked to the same DBpedia POI, the most representative.
We have few possibilities:
\begin{enumerate}
\item Pick the POI that minimize the distance to all the other POIs, this is like applying the K-medoids clustering with K equal 1.
\item Pick the POI which is nearest to the center
\item Pick the POI which is nearest to the DBpedia POI, if coordinates are available
\item Pick the POI which is nearest to the position found on Google Maps \footnote{Google Maps: https://www.google.fr/maps}
\item Link our data to GeoNames \footnote{GeoNames: http://www.geonames.org/}, a dataset of POIs
\end{enumerate}
The first method might be the best one, but it works if most of the POIs are actually clustered. If they are very sparse it does not work.
The second method is biased towards POIs near the center.
The third method can work only with DBpedia POIs with coordinates, and gives good results if DBpedia coordinates are good, but we already know that this is not true.
The fourth method might be the best one, but we need to look outside the semantic world and trust the Google Maps API. Here the problem is that we have no control over the API, but we  know that Google Maps is very good at matching a name with a place.
The fourth method could be the best one, in fact we can exploit GeoNames coordinates that are trusted. The main problem is the fact that not all DBpedia POIs have a corresponding POI.
For simplicity and reliability, we used the Google Maps API because we trust it.
We use the API by sending the DBpedia label to the service, the response contains the coordinates of the POI associated to the DBpedia label. At this point we select the nearest 3cixty POI and we keep it if the distance is less than 2 kilometers.
\subsection{Evaluation (Google Maps)}
The evaluation part is done using the Google Maps API. As done before, we use the distance between the 3cixty POI coordinates and the POI coordinates provided by the API. Since we used the Google Maps API during our process, we expect that distances are low, in fact we know that each POI distance is less than 2 kilometers. What we want to check here is the distance distribution.

\begin{figure}[!htb]
  \centering 
    \includegraphics[width=0.5\textwidth]{images/distance.png}
    \caption{distance distribution of POIs}
\end{figure}

Looking at the distance distribution we note that most of the POIs are actually near to the Google Maps coordinates, while for few POIs this is not true. The main reason for this is the inherent error that arise when we define a POI which occupies a big surface with coordinates that refer to a specific point. For example the surface of the airport of Nice is quite big and different services can locate it in different points of his surface. In the case of the airport, the distance is actually 500 meters. This means that if it is true that most of the POIs are under 500 meters, we can't use this as a threshold because we would leave out a large part of the correct POIs.
At the end of our POI linking process we have 58 POIs that will be matched with the artists.

\section{Interlinking and enriching Artists}
\subsection{Problem description}
DBpedia contains Artists and their works in a disorganized way.
This consist a huge limit because we do not trust the data that we have in DBpedia. Even the simpler operations, such as finding all artists and all songs are extremely difficult due to the non-strict ontology of DBpedia. In order to have some order, we use DOREMUS, which contains trusted informations about artists and songs in a strict ontology.

\subsection{Datasets: DOREMUS, DBpedia, Wikidata}
\subsubsection{DOREMUS}
DOREMUS is a semantic dataset that aims to a fine description of musical works in the fields of traditional and classical music: related musical or creation events, relations to authors, cultural background, interpretations, social functions, etc.
With DOREMUS we can have absolute trust in the data regarding artists, and we can then found corresponding artists in DBpedia with a custom linking process.
Retrieving all artists from DOREMUS is extremely easy, in fact we just need to ask for the Persons in the datasets that are linked to a work at least. The performed query is written below; we retrieved not only the artist uri but also the artist name, the id,  the born year, the death year and the DBpedia "sameAs" already present. These informations are useful as input data for our similarity metric and for the final evaluation.

\begin{lstlisting}
select $uri_doremus 
(group_concat( distinct $id_doremus;separator="|||") as $id_doremus)
(group_concat(distinct $name_doremus;separator="|||") as $name_doremus) 
(group_concat(distinct $born_year;separator="|||") as $born_year) 
(group_concat( distinct $death_year;separator="|||") as $death_year) 
(group_concat(distinct $dbpedia;separator="|||") as $dbpedia) 
where {
$uri_doremus foaf:name $name_doremus.
$uri_doremus ecrm:P131_is_identified_by $id_doremus.
$uri_doremus a ecrm:E21_Person.
$activity ecrm:P14_carried_out_by $uri_doremus.
OPTIONAL{$uri_doremus owl:sameAs $dbpedia.
FILTER (strStarts(str($dbpedia), 'http://dbpedia.org/resource/'))}
OPTIONAL{$uri_doremus ecrm:P98i_was_born $born_year}
OPTIONAL{$uri_doremus ecrm:P100i_died_in $death_year}
} 
group by $uri_doremus
order by $name_doremus
\end{lstlisting}

\subsubsection{DBpedia}
In this case we don't use directly today's DBpedia version but a DBpedia 2015 dump. This because we used an Elastic Search in which this dump was already uploaded.

\subsubsection{Wikidata}
If Wikidata was extremely reliable for the POIs, it is not that strict about musical artists, in fact we need to get all persons and then filter them in some way, looking at classes that are related to music. In particular we considered all people that are composers of some works.

\subsection{Entity Linking process (DBpedia)}
Here we do the same thing that we did with POIs, we need to extract interesting properties from our entities and then use them to find the correct matches. 
With POIs we had one hundred entities from DBpedia, and we could do all operations locally. Here we would like to do the same, but we are dealing with millions of persons, and retrieving them and doing all operations locally is feasible but takes more time. For each artist in DOREMUS, we would compare his label with the label of millions of persons, and in Doremus we have thousands of artists.

In order to speedup operations, we use a dump of DBpedia indexed on ElasticSearch. This allow us to perform all the comparison in a fraction of time thanks to the use of indexes.

Instead for Wikidata the process was different because we didn't use the Elastic Search; in fact this was already set up for DBpedia but not for Wikidata. In addition there are less artists in Wikidata so the problem to handle million of entities is reduced.

This difference of implementation for DBpedia and Wikidata was also the occasion to experiment two different streets, with and without the Elastic Search. We'll resume advantages and issues of both methods at the end of this session.

\subsubsection{Retrieving Elastic Search Resources}
We are not interested in retrieving all DBpedia people but only the ones that are linked with the Doremus entities. So we query ElasticSearch two times for every Doremus artist considering the name sting and the id string(the id is composed by the name and the birth and death date).

\begin{enumerate}

\item \begin{verbatim}GET dbpedia201510/_search?q=*NAME_DOREMUS*\end{verbatim}
\item \begin{verbatim}GET dbpedia201510/_search?q=*ID_DOREMUS*\end{verbatim}

\end{enumerate}

Performing this operation,for every Doremus instance, two results can occur:

\begin{enumerate}

\item we find a list of possible DBpedia matching candidates;

\item we don't find linked DBpedia entities; this is pretty rare and it means that probably this entity is not present on DBpedia;

\end{enumerate}

Considering the first case, ES returns also a score, associated with every entity; the first time we performed the matching, we have considered this; however we have noted that it drives to bad results. So we have preferred to not consider it and to score every returned entity using the method that we'll describe below.

\subsubsection{Enrich Elastic Search data}

At the end of the Elastic Search queries we had basically a table formed by these columns:

\begin{enumerate}

\item doremus artist uri;

\item doremus artist name;

\item doremus artist birth year;

\item doremus artist death year;

\item doremus candidate uri;

\end{enumerate}

Every row is formed by a possible match Doremus artist - DBpedia artist candidate. 
Our goal is to understand which is, between the possible candidates, the exact one. 
On the Doremus side we had all the information associated to every artists as label,birth, death. On the other side instead we have only a possible matching URI. So we queried DBpedia SPARQL endpoint to get these informations:

\begin{enumerate}

\item the list of associated labels/names;

\item the birth year;

\item the death year;

\item the related categories;

\end{enumerate}

To get the labels we checked both \verb|rdfs:labels| and \verb|foaf:name|. In addition we took the labels associated to each language to have better chances of matching them with the Doremus one. Actually this is the real sense of querying Dbpedia endpoint; in fact also the ES retrieves the linked labels, but not for each language.

To get the years informations we have considered different properties because the most of the time the birth year is written as object of the property \verb|dct:subject|. Actually it's part of the object, e.g.\verb|dct:1998_births|. However there are cases in which the year is saved as object of other properties as \verb|dbo:birthDate|, \verb|dbo:birthYear|,
\verb|dbo:birthDate|, \verb|dbp:dateOfBirth|.
The same considerations could be done for the death year. 
In addition performing a query for every year asking about all people born in that year is faster than the inverse: performing a query for every resource asking about the death and the birth year. In fact we have a lot of entities retrieved by the ES queries; instead we have only about 2000 years from 0 to 2017. We used the first approach joining the result with ElasticSearch entities at the end. 
To be faster, we'll perform a query for every 10 years, using the UNION operator.

We had also to check that the entities retrieved by the Elastic Search are composers,musicians, artists or at least people. So it was necessary to get the types of each resource, in particular the ones linked with the idea of composer. When we performed the final scoring we assigned higher scores more specific the category is. 
The considered categories are:

\begin{enumerate}

\item for people \begin{enumerate} \item \verb|http://schema.org/Person| \item \verb|http://xmlns.com/foaf/0.1/Person|\item \verb|http://dbpedia.org/ontology/Person|\item \verb|http://dbpedia.org/class/yago/Person100007846| \end{enumerate}

\item for creators  \verb|http://dbpedia.org/class/yago/Person100007846|

\item for artists \verb|http://dbpedia.org/class/yago/Artist109812338|

\item for musicians \verb|http://dbpedia.org/class/yago/Musician110339966|

\item for composers \verb|http://dbpedia.org/class/yago/Composer109947232|

\end{enumerate}

\subsubsection{Transformations}
At this step we had all data to compute the link DBpedia and Doremus; however we had to perform a cleaning step on the Doremus years. We have noted two kinds of dirty data:
\begin{enumerate}

\item imprecise years: there are some years not very precise as "18..". We deduce that this probably means that we know the century in which the artist is born but not the specific year; we preserved this information because it could be useful also if it is more generic than a specific ;

\item years containing strings: 'ca1500', 'compositeur', 'ca 1720', 'ca 1400', 'ca 1750', 'ca 1430', 'ca1750', 'ca1761', 'ca 1580', 'ca 1736', 'ca1551.', 'ca 1555', 'fl 1658', 'ca 1500', 'ca 1700', 'ca 1516', 'ca 1550', 'ca 1760', 'ca 1706', 'vers 1550', 'ca 1570'; we deduced that "ca" and "vers" mean around so we preserved; however we deleted the "compositeur" case that it's probably a mistake.

\end{enumerate}
\subsubsection{Similarity measures}

We defined a method to score the Doremus-DBpedia artist links. This criteria is composed by these similarity measures:
\begin{enumerate}

\item \textbf{The names/labels similarity}: to compute it we used the Python module "fuzzywuzzy". We deleted from the DBpedia artists candidates the ones that present a very low label similarity with the Doremus one.

\item \textbf{The years similarity}: for every pair Doremus artist-DBpedia artist we checked if the born year and the death year was the same. However the year information were not always present in both Doremus and DBpedia. So we can have different possibilities:
\begin{enumerate}
\item if the complete information is present on both sides and fitted we assigned an high score to the possible DBpedia artist candidate;
\item if the year information is present only on one side we assigned score 0 but we continued to consider the DBpedia entity as a possible candidate,because we haven't enough information to say that the 2 entities are not the same;
\item if the information is present on both sides but it's different:we deleted the DBpedia artist from the candidates. Actually we didn't eliminate the candidate if the years differed for 1 or 2 years, because we have noted that, especially for the old artists, the dates are not always precise;
\item if we had only the information about the century: if it matched we preserved the candidate assigning it a low score; alternatively we deleted it;
\item if the birth year was present on both sides and fitted but the death year is not present on both sides, it could mean that the artist is not already death. To check that we basically looked at the birth date and, if it was not too far from the current date, we considered the artist as still alive, and we increased the score also for the death year matching basing the rise on the probably to be alive computed through a Gaussian distribution. This score rise was less significant than when we had explicitly the same death year;

\end{enumerate}
\item \textbf{The category similarity}: finally we checked the categories of the DBpedia entity: if it was a composer we assigned an high score, alternately we assigned a score as lower as the category is more general. The score assignment decreases following a Gaussian distribution. If the entity is not a person we assigned a negative score.
\end{enumerate}

\subsubsection{Aggregations}

After having the four different similarity scores we computed a weighted sum of them  to get the final matching score. Actually it was not a precise weighted sum; in fact we wanted to keep into account some particular combinations; for example if the category is too generic and the label score is too low, we delete the candidate also if the years matches. We have taken this decision after some trials, noting that considering also these candidates, the number of errors increases because it's more difficult to identify a good threshold to separate bad and good matchings.

TODO insert aggregation functions formula

\subsubsection{Filtering}

TODO insert graph

The graph above shows the scores distribution; the majority of matchings seems to have score near 1 that is good; however some noise it is still present; to remove it we cut all matchings with score lower that 0.5. 0.5 generally means that we don't have informations about the death and birth years but label matched perfectly and the DBpedia entity had an \verb|rdf:type| that clearly indicates that it is a composer.

It is worth noting that a pre-filtering step was performed during the aggregation phase because, as we explained, we deleted for which the category is too generic and the label score is too low.

\subsection{Entity Linking process (Wikidata)}

Now we'll briefly describe the principal differences in the Wikidata artist Linking respect to DBpedia one. It's important to note that we used only the DBpedia artists to search paths between them and POIs, so we spent more time to improve the DBpedia linking respect to the Wikidata one. However we obtained also with less effort good results; in fact the Wikidata retrieved entities are less that the DBpedia on but the data are organized very well, so is easier to apply similarity metrics.

\subsubsection{Retrieving Wikidata Entity}
As anticipated at the beginning of this section, we'll not use the Elastic Search but we considered all Wikidata entities that are composers of some works, looking at a specific property that denotes the composition act. For each of these entities we performed a second query to get the birth and death year. In this case we didn't get the category information because we have already considered only the composers.

\subsubsection{Transformations}
The only data that we transformed were the Doremus one because they presented the same problems than before for some years strings.
\subsection{Evaluation}
The evaluation of the found links is done by comparing them with those provided by ISNI. ISNI is the ISO certified global standard number for identifying the millions of contributors to creative works. By achieving these goals the ISNI will act as a bridge identifier across multiple domains and become a critical component in Linked Data and Semantic Web applications.

\subsubsection{DBpedia performances}
ISNI matches are made by persons in the editorial world, so we can consider them as a ground truth that can be trusted. By comparing our matches we want to see if our performances are acceptable and if we can discover new links between ISNI numbers and DBpedia.

\begin{figure}[!htb]
  \centering
  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{images/counts_artists.png}
    \caption{Counts of artist sets.}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{images/metrics_artists.png}
    \caption{Metrics.}
  \end{minipage}
\end{figure}

Since the matching confidence vary with the threshold, we can plot all the important counts and metrics respect to the threshold used.
In the figure 3 and 4 there are all the counts of the important sets that describe our matching.
Trues indicates the number of DOREMUS entities matched by ISNI, they are ~3500 and of course they are independent from the threshold.
Predicted indicates the number of DOREMUS entities matched by us, the number vary with the confidence, there are different drops that corresponds to crucial thresholds defined by our matching algorithm.

The most important thing is that their count goes from ~3000 to ~6000, this indicates that we are matching way more entities than ISNI.
Doremus intersection represents the number of entities that are matched from both ISNI and us. This shows us that there is a part of the DOREMUS entities that ISNI matches and that we are not able to match.

Now, the following sets are all calculated from the intersection set, in fact we cannot compare the matching performances using entities that are not present in both sets.
Equal show the number of correct matches, we see that this basically overlap with the intersection set, meaning that ISNI and our algorithm match a DOREMUS entity with the same DBpedia entity. Since ISNI matches have a professional validity, this means that we can have a great confidence in the matches produced by our algorithm.

Since equal and DOREMUS intersection are not exactly the same, it means that either our algorithm or ISNI are doing a wrong match. Looking more closely we saw that in some cases ISNI matches were wrong, especially in corner cases, where there were two persons with the same name. This corner cases can fool also an expert, and this is the reason why in our algorithm we embedded the comparison of birth-date and death-date in DBpedia with those present in Doremus. This allowed us to disambiguate between different persons with the same name. In other cases this was not enough, there are persons with the same name and birth/death dates, or whose dates are not available, that can be correctly classified looking at other fields, such as their profession.

Looking at the usual metrics, we see that they are extremely high for this kind of match. This means that we are doing an almost perfect match.
We can state that the proposed method based on combinations of labels, classes and dates is able to match almost perfectly the artists of the two datasets. Moreover, we are able to find 2000 artists that at the time of writing are not present in the ISNI register.
\subsubsection{Wikidata performances}
todo: fabio

\section{Path finder}
\subsection{Problem description}
Once we have a direct mapping between entities that comes from specialized datasets and DBpedia, we actually need to link them.
The whole problem can be solved by writing a series of queries that find paths of a given depth between two resources. 
The main problems that needs to be resolved are:
\begin{enumerate}
\item To write a query or a set of queries that finds all possible paths with given depth between two resources
\item Make sure that query response time scales well when the dataset id large and the depth is high.
\end{enumerate}

\subsection{Related work (Relfinder)}
The path finding problem has already been solved in the past with Relfinder: a tool that is able to find all paths with a specified depth between two entities. 
The first problem to address is to write a set of queries that can find all paths that have the intermediate node in a fixed position:

$$a-->b-->c-->d-->e=m$$
$$a-->b-->c-->d=m<--e$$
$$a-->b-->c=m<--d<--e$$
$$\cdots$$

These path are not able to model all possible paths, in fact we considered only paths with at most one direction change.
When we consider paths with at most two direction changes, we can model more complex relations:

$$a-->b-->c-->d-->e=m$$
$$a-->b-->c-->d=m<--e$$
$$a-->b<--c=m-->d-->e$$
$$\cdots$$

Relfinder is able to generate all paths with a given depths and with at most 2 direction changes.
These paths can express most of the interesting relations between two entities, in fact when we consider more complex paths, we start loosing significance.
For each entity pair, Relfinder generate all possible queries with at most the given depth and makes them, one by one.
When the depth increases, the number of possible path shapes increases too in a non linear way, and the whole process takes too time. The problem is that the resulting queries take too much time, and when we repeat this process for thousands of pairs, we incur in a scalability problem, the whole process would takes whole weeks.

\subsection{Proposed approach}
Our approach builds on top of the Relfinder, looking at the parts that slows the whole process. 
The problem is that DBpedia is small world and its average degree is 4.3, this means that on average we can reach every entity in at most 4-5 hops. Unfortunately our case does not make part of that average, and many times we need 5-6 hops to connect two entities. The problem is that when we make a query that looks for paths with depth 6 we are basically querying the whole DBpedia, which at the time of writing is composed of 8.8 billion triples.
It is our belief that a query that tries to find a path between two entities, is converted by the SPARQL engine in what we can compare to a join for each hop. This, with the small world characteristic of DBpedia means that we are doing huge joins for each query.
Another way to visualize the query is a Breath First Search that starts from the source entity, and it expands hop after hop until the specified depth is reached. In this way is even more easy to see why we end up by querying billions of triples.

\begin{figure}[!htb]
  \centering 
    \includegraphics[width=0.9\textwidth]{images/bfs.png}
    \caption{Bidirectional BFS}
\end{figure}

A common improvement of BFS is the two-way BFS, where the same algorithm is applied both at the source and the destination. In this way we can see that we can reach the same middle node by querying a way smaller portion of the graph.
Looking at paths found by Relfinder, we have seen that usually one direction inversion cover most of the cases, by limiting this we are actually simplifying a lot our problem. Then, we have seen that for artists and POIs, the connection is most of the times the result of a common node. This means that the direction must change at least one time. We reduced all the different cases to one. In fact what we do is to make two separate queries with depth from the source and from the destination. These queries return the list of all half-paths. We make a set of the involved nodes and then we intersect the two sets, in order to find the common nodes. At this point we operate joins that create full paths. The whole matching of POIs and Artists  requires only some hours against the weeks that would take Relfinder.
\subsection{Selection Algorithm}
Now that we have all our path, we need to find the best ones, those that shows interesting links between POIs and Artists.
todo: lorenzo
Moreover, we find a good use of an equation proposed in another paper. todo. cite

At the end, we select 5 Artists for each POI looking at those artists with the highest score, where the score is given by their most interesting path.

\subsection{Paths Evaluation}
Evaluating the goodness of the found paths is not trivial, and an ideal approach would be to ask to real users for a feedback.
What we can do is to analyze the found paths and see if they show interesting connections.
The following path is generated in Place Masséna:
\begin{lstlisting}
"http://dbpedia.org/resource/Chick_Corea", 
"http://dbpedia.org/property/associatedActs", 
"http://dbpedia.org/resource/Herbie_Hancock", 
"http://dbpedia.org/ontology/instrument", 
"http://dbpedia.org/resource/Fairlight_CMI", 
"http://purl.org/dc/terms/subject", 
"http://dbpedia.org/resource/Category:Music_technology", 
"http://www.w3.org/2004/02/skos/core#broader", 
"http://dbpedia.org/resource/Category:Musical_instruments", 
"http://www.w3.org/2004/02/skos/core#broader",       
"http://dbpedia.org/resource/Category:Musical_instrument_museums", 
"http://purl.org/dc/terms/subject", 
"http://dbpedia.org/resource/Palais_Lascaris"
\end{lstlisting}
This path can be considered quite interesting, in fact it is able to link the Palais Lascaris with an Artist because it played with Herbie Hancock, which used in his exhibitions the Fairlight CMI.
\begin{lstlisting}
"http://dbpedia.org/resource/Aristide_Bruant", 
"http://purl.org/dc/terms/subject", 
"http://dbpedia.org/resource/Category:Nightclub_owners", 
"http://www.w3.org/2004/02/skos/core#broader", 
"http://dbpedia.org/resource/Category:Nightclubs", 
"http://www.w3.org/2004/02/skos/core#broader", 
"http://dbpedia.org/resource/Category:Music_venues", 
"http://www.w3.org/2004/02/skos/core#broader", 
"http://dbpedia.org/resource/Category:Music_venues_by_country", 
"http://www.w3.org/2004/02/skos/core#broader", 
"http://dbpedia.org/resource/Category:Music_venues_in_France", 
"http://purl.org/dc/terms/subject", 
"http://dbpedia.org/resource/Palais_Nikaia"
\end{lstlisting}
This path shows one of the defects of our path selection, in fact here we see that most of the relations are given by intermediate categories. This is not a bad thing by itself, but a long chain of categories usually means that the two entities on the edges will meet thanks to a very generic category. On the other hand, this connection is ranked as interesting, and it is partially true: how many artists are Nightclub owners?

Another example that shows that categories can be really explanatory is the following one:
\begin{lstlisting}
"http://dbpedia.org/resource/Yannick_Noah", 
"http://purl.org/dc/terms/subject",   
"http://dbpedia.org/resource/Category:French_tennis_coaches", 
"http://www.w3.org/2004/02/skos/core#broader", 
"http://dbpedia.org/resource/Category:Tennis_in_France", 
"http://www.w3.org/2004/02/skos/core#broader", 
"http://dbpedia.org/resource/Category:Tennis_venues_in_France", 
"http://purl.org/dc/terms/subject", 
"http://dbpedia.org/resource/Nice_Lawn_Tennis_Club"
\end{lstlisting}

Here the connection is almost direct: Yannick Noah was a tennis coach and as expected he is linked to the Nice Lawn Tennis Club.
What is clear from this examples is that paths are really heterogeneous and it is difficult to find a rule that discriminates good paths with good results.

\section{Server Architecture}
The server communicates with the client application using a REST API that consists of two endpoints:
\begin{enumerate}
\item POIs endpoint: allows to get all POIs
\item Playlist endpoint: allows to get the playlist ID associated to the current position
\end{enumerate}
The whole server is implemented using the python Flask framework \footnote{Flask: http://flask.pocoo.org/}. This extensible framework allows to develop REST APIs requiring a minimum amount of boilerplate code.

\subsection{Database}
The result of the ETL process can be interpreted as tables or collections in a database.
Until now, we managed to link 3cixty POIs to DBpedia POIs and DOREMUS artists to DBpedia artists. Then, the result of the pathfinder was a list of paths that connects artists to POIs.
Since we will use the Spotify API \footnote{Spotify: https://www.spotify.com/}, the next step is the linking phase between each artist to the Spotify artist, and then from this to a set of Spotify tracks.
At the end we want to have a direct connection between a DBpedia artist and his tracks on Spotify.

\subsection{Spotify API usage}
Spotify provides a public API that allows to perform all the operations that can usually be done using the Spotify application. These include artist and tracks search, CRUD operations on user playlists and the listening of the tracks' preview.
All the above mentioned operation are essential for the usage of the application.
\subsubsection{Authentication}
Since the end user listen to a Spotify loaded dynamically by the application, there is no need for a client authentication. This is perfect because it allows to any user to use our application. Regarding the server, at startup it performs a token based authentication, where the server get possess of a private token used to perform all CRUD operations on the playlist catalog.
It is important to note that for the correct functioning of the application, a Spotify developer account is needed, then the associated keys are needed in order to obtain the privileges to manage the accounts playlists.
\subsubsection{Playlist}
A playlist can be seen as an ordered list of tracks. With the correct privileges, it can be dynamically created. At creation time, it is required to give a name to the playlist, and the whole playlist object is returned. The returned objects contains a unique playlist ID and many other information that we don't need. Actually, the only information we need is the playlist ID that we can use to access it in the future. It is important to note that we can access to the playlist in two ways: from the server we can access it using the playlist name, in fact we will make sure during the playlist name generation to have unique names. This will be useful to check the presence of a playlist with a given name. From the client point of view, the only access possible is through the playlist ID, in fact it is unique over all the Spotify playlists.

\subsubsection{Artist}
Artists on Spotify can be searched by name and usually, a simple search by name gives as a result different artists with the name that matches part of the search string.
What we need is to link a Doremus artist to a Spotify artist, but in this case we cannot build a proper linking pipeline because the Spotify API is like a black box. What we did is to test it against different kind of inputs with different kind of noises, such as non alphabetic characters, name repetition, the specification of the genre or the word 'composer'. What we have found is that the Spotify search API is quite robust regarding noise determined by name repetition and non alphabetic characters, while it is sensitive to additional words. This means that in order to get the correct artist we need to provide name and surname of the artist. These information are the key component of the label of DOREMUS artists. Since there is a one to one correspondence between DBpedia artists and DOREMUS artists, we can find name and surname instantly. At this point we can perform the API search request, and it returns a list of artist objects. Each object contains different informations regarding each artist, such as his popularity and his genres. Here we use only the popularity by taking the most popular one, but in the future we could use the genre information to perform a better disambiguation.

\subsubsection{Tracks}
Tracks are the main object of Spotify and the API gives us different ways to search for them. A possibility is to search them by artist. We can either get the tracks of a specific album of an artist, or the most popular tracks of an artist. In this project we use the second way because it gives us a number of advantages:
\begin{enumerate}
\item It allows us to get the most popular tracks, this is useful because the user can directly connect to a popular tracks, while this could be more difficult with non popular tracks
\item It allows us to filter outliers, in fact the artist search is not perfect and we can get an artist different from the one we looked for. These are usually outliers or non popular artists for which there are no popular songs. We can use this peculiarity to filter these unwanted artists. An artist with less than 10 popular tracks will be filtered.
\end{enumerate}
But what is popularity? Unfortunately we do not know how Spotify computes it, but we know that it is based on the playcount and recentness of a track.
Among all properties that characterize a track, we only need the name and the ID.
The name is required for simple visualization purposes, while the track ID is essential for what we want to do: add tracks to a playlist. This operation can be done with an API call, and it requires the playlist ID and the track IDs.
\subsection{POIs Endpoint}
The first endpoint that is called by the client is the POIs endpoint.
This endpoint allows to return all POIs in the database that then are drawn on the application map view.
\subsection{Playlist Endpoint}
The main endpoint is the one that exposes the tracks and the paths related to a specific geoposition.
The whole process can be summarized in:
\begin{enumerate}
\item Take user position and validate it.
\item Calculate nearest POIs and assign weights, from these create a unique playlist name.
\item Select the tracks for each artist linked with the poi.
\item Select the paths associated to each track.
\item Create a playlist if it does not exist and add previously selected tracks.
\item Save the playlist ID and attach to each track the path between the poi and the track's artist.
\item Return the playlist ID and the track-path mappings as a JSON.
\end{enumerate}

\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
    \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\begin{tikzpicture}[node distance=1.5cm,
    every node/.style={fill=white, font=\sffamily}, align=center]
  % Specification of nodes (position, etc.)

  \node (server)       [base,]                         {Server};
  %\node (database)     [base,above of=server, yshift=4cm]        {Database};
  \node (spotify)      [base,left of=server, xshift=-8cm]        {Spotify};
  \node (client)       [base,below of=server, yshift=-4cm]                   {Client};

\draw[-latex] (client) to[bend right=10] node[left,xshift=5cm] {\circled{1} $getPlaylist(position)$} (server);
\draw[-latex] (server) edge [looseness=5] node[above] {\circled{2} $playlistName(position)$ \\ \circled{3} $getTracks(name)$ \\ \circled{4} $getPaths(trackids)$} (server);

\draw[-latex] (server) to[bend right=10] node[above] {\circled{5} $createPlaylist(name,track\! ids)$} (spotify);
\draw[-latex] (spotify) to[bend right=10] node[below] {\circled{6} $playlistid$} (server);
\draw[-latex] (server) to[bend right=10] node[right,xshift=-4cm] {\circled{7} $playlist \!id,paths$} (client);

\end{tikzpicture}

\subsubsection{Nearest POIs selection algorithm}
Once the client position is validated, it is necessary to select the POIs that will be used for the recommendation. In fact, it is not possible to directly recommend tracks based on positions because otherwise we would have a playlist for each possible coordinates pair. The following operations needs to be done:
\begin{enumerate}
\item Calculate distance from the each POI to the user position. Since we are using coordinates, the distance is calculated using the haversine distance, which is very accurate and fast.
\item Add to the list the nearest POI, regardless of the distance.
\item Add the remaining two nearest POIs if their distance is inferior of 1 km.
\item For each element in the list, add 10 meters to the distance and then take the log2. By adding 10 meters we are adding a bias to all our distances, in this way positions too near to us are not over-weighted respect far distances. Then, the log2 squashes distances until 1 km to a restricted range of values.
\item Calculate repartition weights using the following equation:
$$w_i = \Bigg \lfloor 10 \dfrac{\dfrac{1}{\log_2 (d_i + 10)}}{\sum \dfrac{1}{\log_2 (d_i + 10)} } \Bigg \rceil$$
In this way we obtain normalized weights from 0 to 10 that are inversely proportional to the log base 2 of the distance. 
\end{enumerate}
At this point we have a direct mapping between POIs weights and a position

\subsubsection{Artist' tracks selection algorithm}
In order to understand the link between the recommended tracks and the POIs, we need to go deeper in the process that links a POI with his tracks.
For each artist there is a direct mapping with its tracks.
The problem is: given a playlist name, find the correct tracks.
The playlist name encodes the weights of each poi, and each weight express exactly the number of tracks that must be chosen for the POI associated.
Since each POI is linked to different artists, we need a way to select songs from them in a balanced way.
What we do is to cycle between all the artists to take each time the most important song that is not already present in the playlist. In this way we obtain different songs from different artists, and since the artist and songs are static, the tracks in the playlist will be always the same. In the future we think to add randomization to the whole selection process.

\subsubsection{Response generation}
\begin{enumerate}
\item Create a playlist with the generated playlist name if it does not exist and add previously selected tracks.
\item Attach to each track the path between the poi and the track's artist.
\item Return the playlist ID and the track-path mappings as a JSON.
\end{enumerate}

\section{Mobile Web Application}
The Web application is implemented using AngularJS and its common MVVM model. Using the Angular framework we are able to create complex single page applications that reduces to the minimum the client server interactions. Another advantage of AngularJS is his widespread adoption and the presence of numerous libraries that communicates naturally with it. One of those is the Google Map module that we use to handle all the POI navigation.
\subsubsection{Music Player}
The music player is implemented using the Spotify Play Button. This is a special <iframe> that loads a simplified Spotify player for a specified playlist. This solution is extremely convenient because it simply needs a playlist ID to run. Since the playlists are created server side and are recovered using the REST API, the whole process is very simple.
Unfortunately it is not possible to manipulate programmatically the <iframe> and this limit the whole user experience. As an improvement, we could build a custom player that still uses the Spotify API.
\subsection{Google Map API}
\subsubsection{POIs placement}
todo: Lorenzo
\subsubsection{Navigation}

\subsection{Relation visualization (and Path format)}
todo: Lorenzo
\section{Conclusion and Future Work}
todo: fabio-lorenzo, improve
In this work, we presented CityMusic: a context-aware content-based recommender system for artists. 
Regarding the first part: the interlinking, we showed that is possible to link POIs and artists to DBpedia achieving good metrics.

We worked on the Relfinder algorithm, by making it scalable. We think that having a scalable solution for the relation finding is crucial for any project that aims to use heavily the huge knowledge graph that DBpedia is.

Our future plans are:
\begin{enumerate}
\item Improve the relation finding algorithm allowing it to find more complex relations without affecting performances.
\item Improve the relation selection algorithm: this part needs a big rework because in the selected paths, there are some that are not meaningful for the user.
\item Evaluate the overall approach with real users 
\item Use additional context informations available in 3cixty and DOREMUS. In this optic, 3cixty provides information about events and this could be added in the recommendation engine, maybe suggesting songs or artists that will be played in a place in the near future.
\item Integrate the music context in the recommendation: now we recommend popular songs because we are not able to choose among them based on the current context. By linking DOREMUS songs with DBpedia we hope to extend the semantic recommendation taking into account song-specific relations with a POI. Linking songs to DBpedia is hard, but we showed that is possible, the main problem is to find good relations between POIs and Songs. This operation is even harder than linking artists to POIs because songs on DBpedia are very poor regarding of links with other resources.
\end{enumerate}
\bibliographystyle{unsrt}
\bibliography{report}
\end{document}

### 2017-06-21 report/report.tex
update report

@@
 \usepackage{tikz}
+\usepackage{xfrac}
 \usetikzlibrary{arrows.meta}
@@
 The only data that we transformed were the Doremus one because they presented the same problems than before for some years strings.
+
+\subsubsection{Similarity measures}
+To match the artist we used the same similarity criteria described before for DBpedia; however it was not feasible applying this similarity measures for all the possible links Wikidata-Doremus artists.
+In fact we got M Doremus artists (around 16000)  and N Wikidata artists (around 14000).
+The complexity of scoring all possible combinations would be $O(m*n)$, where m are the artists of Doremus and n those of Wikidata.
+To avoid this, we indexed the Wikidata artist by label, by birth year and by death year, reducing the complexity to $O(m*\tilde{n})$ where $\tilde{n}$ is the average number of artists by year.
+For this reason every founded match had at least one of these conditions: 
+\begin{enumerate}
+\item the same label
+\item the same birth year
+\item the same death year
+\end{enumerate}
+Actually this is not a big limit because we presumed that at least one similarity metric gave the best score.
+For the fields for which the match was not perfect we used the same similarity metrics used for DBpedia.
+As instance, supposing to have a pair Doremus-DBpedia artist for which the label perfectly matches, we computed the same year similarity measure than the one used for DBpedia artists.
+Alternatively, in the case in which the label doesn't match but birth or the death year match, we consider only the artist born or died in that year, computing the label similarity metric, keeping only the artist associated with the highest score and filtering it out if the label similarity score was too low.
+We remember that for DBpedia we didn't have this complexity issue because the Elastic Search already retrieved a small set of DBpedia candidates for each Doremus artist.
+This similarity approximation is not a big problem because in Wikidata there are a real high number of labels associated to each artist, in many languages but also in many different words ordering.
+So founding a perfect label match is not so rare.
+
+\subsubsection{Aggregations}
+The aggregation was performed considering a simple weighted sum.
+
+\begin{table}[!htb]
+\centering
+\caption{DBpedia/Wikidata comparison}
+\label{my-label}
+\begin{tabular}{@{}|l|l|l|@{}}
+\toprule
+                                                                                                  & \multicolumn{1}{c|}{\textbf{Pros}}                                                                               & \multicolumn{1}{c|}{\textbf{Cons}}                                     \\ \midrule
+\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Dbpedia\\ Elastic\\ Search\end{tabular}}} & \begin{tabular}[c]{@{}l@{}}- Fast\\ - Pre selection using ES\\ - Didn't present complexity problems\end{tabular} & - We used an old DBpedia dump                                           \\ \midrule
+\textbf{Wikidata}                                                                                 & \begin{tabular}[c]{@{}l@{}}- Updated Dbpdia dump\\ - Not necessary type entity checking\end{tabular}             & \begin{tabular}[c]{@{}l@{}}- Slow\\ - Complexity problems\end{tabular} \\ \bottomrule
+\end{tabular}
+\end{table}
+
 \subsection{Evaluation}
@@
     \includegraphics[width=0.9\textwidth]{images/bfs.png}
-    \caption{Bidirectional BFS}
+    \caption{Bidirectional BFS \cite{artificial_intelligence}}
 \end{figure}
@@
 In this way we can see that we can reach the same middle node by querying a way smaller portion of the graph.
+In this way the time and space complexity goes from $O(b^d)$ of the naive approach to $O(b^{\sfrac{d}{2}})$.
 Looking at paths found by Relfinder, we have seen that usually one direction inversion cover most of the cases, by limiting this we are actually simplifying a lot our problem.

### 2017-06-21 report/report.tex
update report

@@
 Abstract: 
-Our project aims at making the user discover the existing connections that link music to a Place, by stimulating his curiosity proposing noncommon relations.
+Our project aims at making the user discover the existing connections that link music to a Place, by stimulating his curiosity proposing non-common relations.
 In this project, we show a new approach for finding artists linked to a place of interest (POI).
@@
 \section{Introduction}
-Most of the available music recommender systems suggest music without taking into consideration the user’s context \cite{Knees:2013:SMS:2559928.2542206}.
+Most of the available music recommender systems suggest music without taking into consideration the user context \cite{Knees:2013:SMS:2559928.2542206}.
 This means that a generic recommender system will propose the same set of songs regardless of the user mood, location, activity.
@@
 The main challenge that one must face when addressing the above-mentioned goal is related to the fact that POIs and music are two rather different domains, and there is no obvious way to match such heterogeneous items.
-However, with the advent of the Semantic Web, new opportunities arise to face the above difficulties.
-We will show that using generic semantic datasets we can recommend artists that are linked to the user location.
+However, with the advent of the Semantic Web, new opportunities arise to face these type difficulties.
+We will show that using a general purpose semantic dataset such as DBpedia we can recommend artists that are linked to the user location.
 
@@
 In the past, many tried to link POIs and music in many different ways.
-managed to link music and POIs by using a common set of tags that describe emotional properties both for music and POIs \cite{Kaminskas:2013:LMR:2507157.2507180}.
-This method was completely supervised, in fact it required the definition of a set of emotions for songs and POIs. This operation has been done by hand and is hardly scalable.
-In another project \cite{Kaminskas:2012:KMR:2390848.2390854}, a semantic approach has been used by restricting the subspace of DBpedia \footnote{DBpedia: http://wiki.dbpedia.org/} by identifying classes related to the domains of interest, and the relations existing between instances of such classes.
-In this way, they managed to find relations in a set of paths constrained to pass belong to those classes.
-Looking at the future works proposition, they proposed the idea to exploit arbitrary semantic relations between POIs and musicians.
-In order to do this, they proposed to use Relfinder \cite{Heim:2009:RRR:1695324.1695351} and set the connections' weights using an heuristic.
-In fact, one of the bad things was that connections weights were assigned by experts and were not provided in the paper.
+Someone managed to link music and POIs by using a common set of tags that describe emotional properties both for music and POIs \cite{Kaminskas:2013:LMR:2507157.2507180}.
+This method is completely supervised, in fact it requires the definition of a set of emotions for songs and POIs.
+This operation must be done manually and is hardly scalable.
+\begin{figure}[!htb]
+  \centering 
+    \includegraphics[width=1\textwidth]{images/semantic_net.png}
+    \caption{Semantic Network with predefined classes}
+\end{figure}
+
+In a second project \cite{Kaminskas:2012:KMR:2390848.2390854}, the goal is achieved by by restricting the subspace of DBpedia \footnote{DBpedia: http://wiki.dbpedia.org/} to a set classes related to the domains of interest.
+These classes includes concepts that are easily linkable to artists and POIs, such as historic periods, architectural styles and geographic informations.
+In this way, they managed to find relations in a set of paths constrained to pass through those classes.
+
+Looking at the future propositions, both projects proposed the idea to exploit arbitrary semantic relations between POIs and musicians.
+In order to do this, they proposed to use Relfinder \cite{Heim:2009:RRR:1695324.1695351} and set the connection weights using an heuristic.
+In fact, one of the disadvantages of those approaches is that connections weights are assigned by experts and were not provided in the paper.
 Our intention is to build our approach on top of this paper and find relations in a completely unsupervised way: this means that we intend to define a pathfinder that finds paths and a path discriminator that selects the interesting relations.

### 2017-06-24 report/report.tex
update report, corrections
correct report, introduction

@@
 \section{Introduction}
-Most of the available music recommender systems suggest music without taking into consideration the user context \cite{Knees:2013:SMS:2559928.2542206}.
-This means that a generic recommender system will propose the same set of songs regardless of the user mood, location, activity.
-Finding music that suits a POI can be viewed as a context-aware recommendation problem, the place is the context for consuming the recommendation.                    
+"In order to generate relevant recommendations, a context-aware recommender system (CARS) not only makes use of user preferences, but also exploits information about the specific contextual situation in which the recommended item will be consumed." \cite{Baltrunas:2012:CRA:2339097.2339111}
+
+This is in contrast with the fact that most of the available music recommender systems suggest music without taking into consideration the user context \cite{Knees:2013:SMS:2559928.2542206}.
+This is because defining and especially exploiting contexts is not a trivial operation.
+Context can be defined as any information that can be used to characterize the situation of an entity.
+\cite{Dey:2001:UUC:593570.593572}.
+These informations informations includes mood, location, activity, friends, daily and current activities of the target user.
+
+If we think of a recommender task in a mobile scenario (e.g., choosing a song while sightseeing), we see that most recommendations are requested by users while they are on their way.
+This causes a continuous change in the context that needs to be carefully addressed.
+Recommendations are much more useful and enjoyable for end users as they change with their current context .
+\cite{Ostuni:2012:CCM:2887638.2887642}
+
+Finding music that suits a Point of Interest(POIS) can be viewed as a context-aware recommendation problem, the place is the context for consuming the recommendation.
 The main challenge that one must face when addressing the above-mentioned goal is related to the fact that POIs and music are two rather different domains, and there is no obvious way to match such heterogeneous items.
-However, with the advent of the Semantic Web, new opportunities arise to face these type difficulties.
-We will show that using a general purpose semantic dataset such as DBpedia we can recommend artists that are linked to the user location.
+However, with the advent of the Semantic Web, new opportunities arise to face these type of difficulties.
+We will show that, using a general purpose semantic dataset such as DBpedia, we can recommend artists that are linked to the user location.
 
@@
 
-TODO insert graph
+\begin{figure}[!htb]
+  \centering 
+    \includegraphics[width=1\textwidth]{images/score_distribution.jpg}
+    \caption{Score distribution}
+\end{figure}
 
@@
   \centering 
+    \includegraphics[width=0.7\textwidth]{images/Path_Discovering.jpg}
+    \caption{Bidirectional BFS 1}
+\end{figure}
+
+\begin{figure}[!htb]
+  \centering 
     \includegraphics[width=0.9\textwidth]{images/bfs.png}
-    \caption{Bidirectional BFS \cite{artificial_intelligence}}
+    \caption{Bidirectional BFS 2 \cite{artificial_intelligence}}
 \end{figure}
@@
 The whole matching of POIs and Artists  requires only some hours against the weeks that would take Relfinder.
+
+\subsection{Paths Filtering}
+Using our method we retrieve a really high number of paths: 41802195. Applying an algorithm to score each path would be really intensive. So we decide to filter out the less interesting paths.
+In practice we perform three filtering steps:
+\begin{enumerate}
+\item \textbf{Removing cycles} : in the  first filtering step we want to remove all paths in which a resource is presented two times.
+In fact it means that there is a shorter path between the POI and the artist, and it is already present in our table.
+As instance let's suppose to have these 2 paths (the letters represent the resources):
+$$a-->b-->c$$
+$$a-->b-->e-->b<--c$$
+$$\cdots$$
+We want to preserve only the first one. At the end of these step the number of remaining paths is: 1148286. This means that an half of our paths were cycles.
+
+\item \textbf{Preserving only shortest paths} :  we want to save only the shortest path between an artist and a POI.
+A shorter path doesn't mean certainly a better one.
+However the majority of our paths is really long (6 of depth), so this step is useful to delete all repeated data.
+Let's suppose to have these 2 paths (the letters represent the resources):
+$$a-->b-->d-->e-->f$$
+$$a-->b-->c-->d-->e-->f$$
+$$\cdots$$
+We want to preserve only the first one.
+
+\end{enumerate}
+
+At the end of these three filtering steps 27931 paths remain. We apply to these our selection algorithm.
+
 \subsection{Selection Algorithm}
-Now that we have all our path, we need to find the best ones, those that shows interesting links between POIs and Artists.
 todo: lorenzo
-Moreover, we find a good use of an equation proposed in another paper. todo. cite
+Now that we have all our filtered path, we need to find the best ones, those that shows interesting links between POIs and Artists. Our interest is to consider both path length and exclusiveness. 
+Moreover, we take inspiration from \cite{meng2013review}.
+We define the exclusiveness as the inverse of the generality, where the generality is:
+
+$$gen =\frac{1}{\mid N \mid}\sum_i^Nocc(r_{i})$$
+
+Here $$r(r_{i})$$ corresponds to the i resource of the path and $$occ(r_{i})$$ to the number of occurrences of this resource belongs to all considered paths.
+
+$$sim(artist,poi) = 1-k(\frac{\log(len(artist,poi)-1)}{\log(2*(deep_max -1))})-(1-k)gen$$
 

### 2017-06-26 report/report.tex
update

@@
 \usepackage{cite}
+\usepackage{textcomp}
+\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}}
 \usepackage[nottoc]{tocbibind}
+
 \usepackage{listings}
+\lstset{breaklines}
 \setcounter{secnumdepth}{4}
@@
 \section{Introduction}
-"In order to generate relevant recommendations, a context-aware recommender system (CARS) not only makes use of user preferences, but also exploits information about the specific contextual situation in which the recommended item will be consumed." \cite{Baltrunas:2012:CRA:2339097.2339111}
-
-This is in contrast with the fact that most of the available music recommender systems suggest music without taking into consideration the user context \cite{Knees:2013:SMS:2559928.2542206}.
+"In order to generate relevant recommendations, a context-aware recommender system (CARS) not only makes use of user preferences, but also exploits information about the specific contextual situation in which the recommended item will be consumed."~\cite{Baltrunas:2012:CRA:2339097.2339111}
+
+This is in contrast with the fact that most of the available music recommender systems suggest music without taking into consideration the user context~\cite{Knees:2013:SMS:2559928.2542206}.
 This is because defining and especially exploiting contexts is not a trivial operation.
-Context can be defined as any information that can be used to characterize the situation of an entity.
-\cite{Dey:2001:UUC:593570.593572}.
+Context can be defined as any information that can be used to characterize the situation of an entity~\cite{Dey:2001:UUC:593570.593572}.
 These informations informations includes mood, location, activity, friends, daily and current activities of the target user.
@@
 This causes a continuous change in the context that needs to be carefully addressed.
-Recommendations are much more useful and enjoyable for end users as they change with their current context .
-\cite{Ostuni:2012:CCM:2887638.2887642}
+Recommendations are much more useful and enjoyable for end users as they change with their current context~\cite{Ostuni:2012:CCM:2887638.2887642}.
 
@@
 \subsection{Motivation and context}
-In the past, many tried to link POIs and music in many different ways.
-Someone managed to link music and POIs by using a common set of tags that describe emotional properties both for music and POIs \cite{Kaminskas:2013:LMR:2507157.2507180}.
+In the past, different attempts have been performed to link POIs and music in many different ways.
+A strategy can consist in linking music and POIs by using a common set of tags that describe emotional properties both for music and POIs~\cite{Kaminskas:2013:LMR:2507157.2507180}.
 This method is completely supervised, in fact it requires the definition of a set of emotions for songs and POIs.
@@
 
-In a second project \cite{Kaminskas:2012:KMR:2390848.2390854}, the goal is achieved by by restricting the subspace of DBpedia \footnote{DBpedia: http://wiki.dbpedia.org/} to a set classes related to the domains of interest.
+In~\cite{Kaminskas:2012:KMR:2390848.2390854}, the goal is achieved by by restricting the subspace of DBpedia to a set classes related to the domains of interest.
 These classes includes concepts that are easily linkable to artists and POIs, such as historic periods, architectural styles and geographic informations.
-In this way, they managed to find relations in a set of paths constrained to pass through those classes.
-
-Looking at the future propositions, both projects proposed the idea to exploit arbitrary semantic relations between POIs and musicians.
-In order to do this, they proposed to use Relfinder \cite{Heim:2009:RRR:1695324.1695351} and set the connection weights using an heuristic.
-In fact, one of the disadvantages of those approaches is that connections weights are assigned by experts and were not provided in the paper.
-Our intention is to build our approach on top of this paper and find relations in a completely unsupervised way: this means that we intend to define a pathfinder that finds paths and a path discriminator that selects the interesting relations.
-We aim at reducing the need for human intervention in defining classes and weights with the hope that this approach will be completely data driven and easily scalable to different cities.
-Moreover, we will use different datasets with the intention to exploit their implicit advantages and obtain overall a better recommender system.
+In this way, it is possible to find relations in a set of paths constrained to pass through those classes.
+Looking at the future propositions, both strategies proposed the idea to exploit arbitrary semantic relations between POIs and musicians.
+In order to do this, tools like Relfinder have been proposed \cite{Heim:2009:RRR:1695324.1695351}, in combination an heuristic to set the connection weights.
+In fact, one of the disadvantages of those approaches is that connections weights are assigned by experts and are not published.
+Our goal is to build our approach on top of this paper and find relations in a completely unsupervised way: this means that we intend to define a path finder that finds paths and a path discriminator that selects the interesting relations.
 
@@
 In this project, we show a new approach for finding artists linked to a place of interest (POI).
-We propose an entity linking framework built upon DBpedia, 3cixty \footnote{3cixty: https://www.3cixty.com/}, and Doremus \footnote{DOREMUS: http://www.doremus.org/} that is able to reach editorial accuracy in the interlinking process.
+We propose an entity linking framework built upon DBpedia, 3cixty\footnote{3cixty: https://www.3cixty.com/}, and DOREMUS\footnote{DOREMUS: http://www.doremus.org/} that is able to reach editorial accuracy in the interlinking process.
 Furthermore, we present a graph exploration algorithm that is able to find deep connections in a short time and discriminate between them by looking at those that can be the most interesting.
+We aim at reducing the need for human intervention in defining classes and weights with the hope that this approach will be completely data driven and easily scalable to different cities. 
+Finally, we demonstrate the effectiveness of our work through an APP that  ....
+
+For this experimental work, we chose Nice because because it is a medium sized city that allows us to deal with both popular and unpopular places.
+Furthermore the number of POIs in Nice is manageable, this means that we can check immediately our results.
+Finally, POIs in Nice are enough to see if our proposed solution can scale.
 
 \subsection{Report structure}
-The report is divided into five sections, one for each part of the project.
-The first two parts are about linking external datasets to DBpedia, this is also known as entity linking and we perform it in the optic of enriching our data with the inter-concept links present in DBpedia.
-The third treats the Pathfinder, a module of our system that is able to find deep connections between two entities in DBpedia.
+This report is divided into five sections, one for each part of the project.
+The first two parts are about linking external datasets to DBpedia, this task is known as entity linking and we perform it in the optic of enriching our data with the inter-concept links present in DBpedia.
+The third covers the Pathfinder, a module of our system that is able to find deep connections between two entities in DBpedia.
 The fourth describes the whole implementation of the REST API that allows the application to work smoothly.
@@
 Interlinking different datasets is not trivial, many approaches that aimed at a semi-supervised interlinking have been proposed, but this is still an active research topic.
-One of the main problems that must be faced in an interlinking process is the ontology definition, in fact, specialized datasets tend to have a very strict ontology, while DBpedia does not enforce it.
-This means that in the case of POIs, not all places in nice are linked to nice, thus it is difficult to even correctly define a POI in Nice.
-Since we are dealing with a medium sized city such as Nice, we can't allow loosing some matchings and we need to carefully analyze the DBpedia ontology in order to leave out a minimum part of Nice POIs.
+One of the main problems that must be faced in an interlinking process is the ontology definition.
+In fact, specialized datasets tend to have a very strict ontology, while DBpedia does not enforce it.
+This means that in the case of POIs, not all places in Nice are linked to Nice, thus it is difficult to even correctly define a POI in Nice.
+Since we are dealing with a medium sized city such as Nice, we can't allow loosing some matchings and we need to carefully analyze the DBpedia ontology in order to leave out the minimum part of Nice POIs.
 
@@
 In this project 3cixty is used as a trusted source of POIs for Nice.
-POIs have many informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint selecting the Nice city.
+POIs have a lot of informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint of the 3cixty API.
+
+For example, this is the JSON object associated to the `Nice Lawn Tennis Club': \begin{lstlisting}
+{  
+   "_about":"http://data.linkedevents.org/location/579aa423-cb1b-3d35-90d5-ef482aa093ad",
+   "businessType":[  
+      "http://data.linkedevents.org/kos/foursquare/tennis-court"
+   ],
+   "geoLocation":{  
+      "_about":"http://data.linkedevents.org/location/579aa423-cb1b-3d35-90d5-ef482aa093ad/geometry",
+      "lat":43.7043,
+      "long":7.25188
+   },
+   "label":"Nice Lawn Tennis Club",
+   "location":{  
+      "_about":"http://data.linkedevents.org/location/579aa423-cb1b-3d35-90d5-ef482aa093ad/address",
+      "streetAddress":"5, ave. Suzanne Lenglen, 06000 Nice, France"
+   }
+}
+
+\end{lstlisting}
+
 \subsubsection{DBpedia}
-DBpedia is a project that aims at connecting the semantic world. We used it to get the POIs in Nice.
+DBpedia\footnote{DBpedia: http://wiki.dbpedia.org/} is a crowd-sourced community effort to extract structured information from Wikipedia\footnote{Wikidata: https://en.wikipedia.org/} and make this information available on the Web.
+The DBpedia knowledge base has several advantages over existing knowledge bases: it covers many domains; it automatically evolves as Wikipedia changes, and it is truly multilingual.
+We used it to get the POIs in Nice.
 In order to get the POIs from DBpedia, it is necessary to perform SPARQL queries against the SPARQL endpoint.
-POIs are retrieved using two different sparql queries that target different kind of resources:
-\begin{enumerate}
-\item We perform a query that looks for all Geoentities that are in the area of nice. An entity is in the area of Nice if its coordinates are in a custom box that contains all the area of Nice.
-Unfortunately there are many POIs that are without coordinates,so they are not selected by this query.
+POIs are retrieved using two different SPARQL queries that target different kind of resources:
+\begin{enumerate}
+\item We perform a query that looks for all resources in Nice. 
+Figure \ref{fig:box} shows the area with valid coordinates.
+Unfortunately there are many POIs that are without coordinates, so they are not selected by this query.
 \begin{lstlisting}
@@
     \caption{Area for POIs selection}
+    \label{fig:box}
 \end{figure}
 
-\item We take all resources that have as a parent either the Nice resource or the Category:Nice resource.
-Then we repeat this operation for each subcategory of Category:Nice in a recursive way.
+\item We take all resources that have as a parent either the dbr:Nice resource or the dbc:Nice resource.
+Then we repeat this operation for each subcategory of dbc:Nice in a recursive way.
 Among these resources, we keep those which type is in a set of classes defined by hand.
@@
 \subsubsection{Wikidata}
-Wikidata \footnote{Wikidata: https://www.wikidata.org/} is a project that aims at connecting the semantic world.
+Wikidata\footnote{Wikidata: https://www.wikidata.org/} Wikidata is a free and open knowledge base that can be read and edited by both humans and machines.
+Wikidata acts as central storage for the structured data of its Wikimedia\footnote{Wikimedia: https://www.wikimedia.org/} sister projects including Wikipedia.
+
 We used it to get the POIs in Nice.
@@
 Since wikidata supports complex geo-based queries, we can make a query that looks for all POIs in a range of 25 Kilometers from the center of Nice.
+\begin{lstlisting}
+SELECT ?item ?itemLabel ?location WHERE {
+  wd:Q33959 wdt:P625 ?niceLoc .
+  SERVICE wikibase:label {
+    bd:serviceParam wikibase:language "fr" .
+  }.
+  SERVICE wikibase:around { 
+      ?item wdt:P625 ?location . 
+      bd:serviceParam wikibase:center ?niceLoc . 
+      bd:serviceParam wikibase:radius "10" . 
+  }  
+}
+\end{lstlisting}
+
 \subsection{Entity Linking process}
-In order to link our two set, we copy them locally and then we perform the linking process.
+In order to link our three set, we copy them locally and then we perform the linking process.
 Having the entities locally is crucial, in fact it allows us to make way more complex operations respect to those that can be done with SPARQL queries.
+The whole process can be described as follow:
+\begin{enumerate}
+\item Extract labels from DBpedia entities.
+\item Apply transformations.
+\item Compute similarity metrics with 3cixty entities.
+\item Aggregate results
+\item Filter matches above threshold.
+\end{enumerate}
+
 \subsubsection{Properties}
@@
 In this way we can do a multilingual match that improves our accuracy.
-Since this is not intuitive, here is an example.
-DBpedia labels:
-'Conservatory of Nice'
-'Conservatoire de Nice'
-3cixty label: 'Conservatoire de nice'
-In this case if we use the english label, we do not obtain a perfect match, while with the french label we obtain a perfect match.
-We do not use coordinates because not all entities have them. Moreover, we have seen experimentally that using the DBpedia coordinates we obtain worse results because they are inaccurate.
-Regarding 3cixty entities, they have very accurate coordinates, and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.
+Here is an example:
+\begin{itemize}
+\item DBpedia labels: `Conservatory of Nice' @en, `Conservatoire de Nice' @fr
+\item 3cixty label: `Conservatoire de nice'
+\end{itemize}
+In this case if we use the English label, we do not obtain a perfect match, while with the French label we obtain a perfect match.
+Other times we have the opposite result, but using labels in different languages we solve this problem.
+
+Among other informations, we have the coordinates, but we do not use them because not all entities have them.
+Moreover, we have seen experimentally that using the DBpedia coordinates we obtain worse results because of their inaccuracy.
+Regarding 3cixty entities, they have very accurate coordinates and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.
 
@@
 Since utf-8 can represent way more characters than ASCII, we need to strip non ASCII characters from our labels.
-This is done in an intelligent way using the python library \textit{'unidecode'}\footnote{Unidecode: https://pypi.python.org/pypi/Unidecode}, that is able to convert from unicode to ASCII by changing or deleting a minimum set of characters.
-For example, an accented letter like 'è' can't be represented in ASCII, and most of the libraries simply delete it, while \textit{'unidecode'} converts it to the nearest ASCII character: in this case 'è' is converted to 'e'.
+This is done in an intelligent way using the python library \textit{`unidecode'}\footnote{Unidecode: https://pypi.python.org/pypi/Unidecode}, that is able to convert from unicode to ASCII by changing or deleting a minimum set of characters.
+For example, an accented letter like `è' can't be represented in ASCII, and most of the libraries simply delete it, while \textit{`unidecode'} converts it to the nearest ASCII character: in this case 'è' is converted to 'e'.
 In this way we can retain most of the original information after this conversion process.
 
-The second step is probably the most important, and is the normalization of names.
-Some similarity metrics are extremely sensitive to noise.
-For example, when we use simple levenstein distance between ('airport','airport nice') is 5, while the distance ('airport','port') is 4.
+The second step is probably the most important, and is the normalization of names. Some similarity metrics are extremely sensitive to noise. For example, when we use simple Levenshtein:
+\begin{itemize}
+\item levenshtein\_distance(`airport',`airport nice'): 5
+\item levenshtein\_distance(`airport',`port'): 4
+\end{itemize}
 This is enough to raise some concerns: the simple addition of the city name can turn a perfect match into a mediocre one.
@@
 The third step is to strip all non alphabetical characters and to convert to lowercase all strings, this off course gives us cleaner strings to compare.
+
 The whole transformation pipeline aims at maximizing the similarity measure between correct matches.
-This is extremely important, because later we can set a threshold to separate matches that have a good confidence from matches with a low confidence.
-If we do not perform the transformation phase, we would obtain correct matches that have the same confidence of the incorrect ones because we have basically some noise in all the strings.
+Later we will set a threshold to separate matches that have a good confidence from matches with a low confidence.
 
 \subsubsection{Similarity measures and matching algorithm}
-Now that strings are clean, we can proceed to the actual matching.
-A first problem rises: we want to match a 3cixty poi to a dbpedia poi, or we want to match a dbpedia poi to a 3cixty poi?
-In the first case we are sure that each 3cixty poi will be matched to a single dbpedia poi, but there is the risk that multiple 3cixty poi are matched to the same DBpedia poi.
+Now that strings are clean, we can continue to the actual matching.
+A first question rises: we want to match a 3cixty poi to a DBpedia poi, or we want to match a DBpedia poi to a 3cixty poi?
+In the first case we are sure that each 3cixty poi will be matched to a single DBpedia poi, but there is the risk that multiple 3cixty poi are matched to the same DBpedia poi.
 Alternatively, we are sure that each DBpedia poi is matched to at most a 3cixty poi, but there is the risk that many DBpedia poi are matched to the same 3cixty poi.
@@
 
-Regarding the similarity metric among strings, we use multiple similarity measures based on levenstein distance.
-We chose to use different metrics because we have seen experimentally that in this specific case, strings that represents POIs, a single similarity metric is not enough.
-From a technical point of view, we used a set of the similarity metrics provided by the 'fuzzywuzzy'\footnote{FuzzyWuzzy: https://pypi.python.org/pypi/fuzzywuzzy} python module.
+Regarding the similarity metric among strings, we use multiple similarity measures based on Levenshtein distance.
+This comes from the fact that experimentally we have seen experimentally that in this specific case, strings that represents POIs, a single similarity metric is not enough.
+From a technical point of view, we used a set of the similarity metrics provided by the `fuzzywuzzy'\footnote{FuzzyWuzzy: https://pypi.python.org/pypi/fuzzywuzzy} python module:
+\begin{itemize}
+\item partial\_ratio: Return the ratio of the most similar substring
+    as a number between 0 and 100.
+\item token\_set\_ratio: Find all alphanumeric tokens in each string:
+\begin{enumerate}
+\item treat them as a set
+\item construct two strings of the form: $<sorted\_intersection> <sorted\_remainder>$
+\item take ratios of those two strings
+\item controls for unordered partial matches
+\end{enumerate}
+
+\item token\_sort\_ratio: Return a measure of the sequences' similarity between 0 and 100
+    but sorting the token before comparing.
+\item partial\_token\_sort\_ratio: Return the ratio of the most similar substring as a number between 0 and 100 but sorting the token before comparing.
+
+\item WRatio: A weighted combination of other similarities
+\end{itemize}
 
@@
 Why we don't simply take the average, or the minimum, or the maximum?
-The reasoning behind this is that by taking the average we are flattening all the scores, and there is the risk that the string with the highest similarity is a string that is mediocre in all the different metrics.
+The reason behind this is that by taking the average we are flattening all the scores, and there is the risk that the string with the highest similarity is a string that is mediocre in all the different metrics.
 If a string is mediocre in all comparisons, then we do not trust it.
 Instead, with our methodology we are keeping only those matches that excel in some similarity metric, and then we take the one that performs better on average.
-We think that in this way we can filter out all those matches with average strings that matches almost anything.
+In this way we can filter out all those matches with average strings that matches almost anything.
 
@@
 Now that the matching is done, we need to filter our results.
-
-The first operation to do is to eliminate all those POIs that match with Nice, but that have a label different from Nice.
+The first operation to do is to ignore all those POIs that match with Nice, but that have a label different from Nice.
 This happens because we added Nice to all the strings.
 That addition was helpful, and it also created a safe default that we can easily filter.
-Most of these POIs filtered in this way are acronyms that match with Nice e.g. 'ATP Nice' matches with Nice because half of the string is Nice and is artificial, because we added it.
+Most of the POIs filtered in this way are acronyms that match with Nice, e.g. `ATP Nice' matches with Nice because half of the string is Nice and is artificial, because we added it.
 
@@
 An untrusted confidence gives us no additional informations about good matches and bad matches.
-At this point we filter all matches with a score below a given threshold.
-
-Now we are at the half of our work, for each 3cixty POI we have a link to a DBpedia POI, but we might have multiple 3cixty POIs linked to the same DBpedia POI.
-We aim to a 1 to 1 relation, so we need to choose among a group of 3cixty POIs linked to the same DBpedia POI, the most representative.
+At this point we filter all matches with a score below a given threshold(0.8).
+
+In this moment for each 3cixty POI we have a link to a DBpedia POI, but we might have multiple 3cixty POIs linked to the same DBpedia POI.
+We aim to a 1 to 1 relation, so we need to choose one among a group of 3cixty POIs linked to the same DBpedia POI, the most representative.
 We have few possibilities:
@@
 \item Pick the POI that minimize the distance to all the other POIs, this is like applying the K-medoids clustering with K equal 1.
-\item Pick the POI which is nearest to the center
-\item Pick the POI which is nearest to the DBpedia POI, if coordinates are available
-\item Pick the POI which is nearest to the position found on Google Maps \footnote{Google Maps: https://www.google.fr/maps}
-\item Link our data to GeoNames \footnote{GeoNames: http://www.geonames.org/}, a dataset of POIs
-\end{enumerate}
-The first method might be the best one, but it works if most of the POIs are actually clustered. If they are very sparse it does not work.
-The second method is biased towards POIs near the center.
-The third method can work only with DBpedia POIs with coordinates, and gives good results if DBpedia coordinates are good, but we already know that this is not true.
-The fourth method might be the best one, but we need to look outside the semantic world and trust the Google Maps API.
-Here the problem is that we have no control over the API, but we  know that Google Maps is very good at matching a name with a place.
-The fourth method could be the best one, in fact we can exploit GeoNames coordinates that are trusted. The main problem is the fact that not all DBpedia POIs have a corresponding POI.
+This works if POIs are actually clustered, while it does not work if they are sparse.
+\item Pick the POI which is nearest to the center. This is biased towards POIs near the center.
+\item Pick the POI which is nearest to the DBpedia POI, if coordinates are available. This works only with a subset of POIs, and we do not fully rely on DBpedia coordinates.
+\item Pick the POI which is nearest to the position found on Google Maps\footnote{Google Maps: https://www.google.fr/maps}. We have no control over Google Maps.
+\item Link our data to GeoNames\footnote{GeoNames: http://www.geonames.org/}. Not all DBpedia POIs have a corresponding GeoNames POI.
+\end{enumerate}
 For simplicity and reliability, we used the Google Maps API because we trust it.
@@
     \caption{distance distribution of POIs}
+    \label{fig:poidist}
 \end{figure}
 
-Looking at the distance distribution we note that most of the POIs are actually near to the Google Maps coordinates, while for few POIs this is not true.
+Figure \ref{fig:box} shows the POIs distance distribution with the corresponding Google Maps POIs.
+If we consider 250 meters as a threshold, 70\% of POIs are below it.
 The main reason for this is the inherent error that arise when we define a POI which occupies a big surface with coordinates that refer to a specific point.
@@
 In the case of the airport, the distance is actually 500 meters.
-This means that if it is true that most of the POIs are under 500 meters, we can't use this as a threshold because we would leave out a large part of the correct POIs.
-At the end of our POI linking process we have 58 POIs that will be matched with the artists.
+This means that if it is true that most of the POIs are under 250 meters, we can't use this as a threshold because we would leave out a large part of the correct POIs.
+At the end of our POI linking process we have 58 POIs.
 
@@
 \subsection{Problem description}
-DBpedia contains Artists and their works in a disorganized way.
-This consist a huge limit because we do not trust the data that we have in DBpedia.
+DBpedia Artists and Works are not represented with a strict ontology. 
+This is a huge limit because we can not rely entirely on the data that we have in DBpedia.
 Even the simpler operations, such as finding all artists and all songs are extremely difficult due to the non-strict ontology of DBpedia.
-In order to have some order, we use DOREMUS, which contains trusted informations about artists and songs in a strict ontology.
+In order to have some order, we use DOREMUS, which contains trusted and properly organized informations about artists and songs.
 
@@
 Retrieving all artists from DOREMUS is extremely easy, in fact we just need to ask for the Persons in the datasets that are linked to a work at least.
-The performed query is written below; we retrieved not only the artist uri but also the artist name, the id,  the born year, the death year and the DBpedia "sameAs" already present.
+The performed query is written below; we retrieved not only the artist uri but also the artist name, the id,  the born year, the death year and the DBpedia `sameAs' link.
 These informations are useful as input data for our similarity metric and for the final evaluation.
@@
 \begin{lstlisting}
-select $uri_doremus 
+SELECT $uri_doremus 
 (group_concat( distinct $id_doremus;separator="|||") as $id_doremus)
@@
 (group_concat(distinct $dbpedia;separator="|||") as $dbpedia) 
-where {
+WHERE {
   $uri_doremus foaf:name $name_doremus.
@@
   $activity ecrm:P14_carried_out_by $uri_doremus.
-OPTIONAL{$uri_doremus owl:sameAs $dbpedia.
-FILTER (strStarts(str($dbpedia), 'http://dbpedia.org/resource/'))}
+  OPTIONAL{
+    $uri_doremus owl:sameAs $dbpedia.
+    FILTER (strStarts(str($dbpedia), 'http://dbpedia.org/resource/'))
+  }
   OPTIONAL{$uri_doremus ecrm:P98i_was_born $born_year}
@@
 Here we do the same thing that we did with POIs, we need to extract interesting properties from our entities and then use them to find the correct matches. 
-With POIs we had one hundred entities from DBpedia, and we could do all operations locally.
+With POIs we had 100 entities from DBpedia, and we could do all operations locally.
 Here we would like to do the same, but we are dealing with millions of persons, and retrieving them and doing all operations locally is feasible but takes more time.
-For each artist in DOREMUS, we would compare his label with the label of millions of persons, and in Doremus we have thousands of artists.
+For each artist in DOREMUS, we would compare his label with the label of millions of persons, and in DOREMUS we have thousands of artists.
 
@@
 
-Instead for Wikidata the process was different because we didn't use the Elastic Search; in fact this was already set up for DBpedia but not for Wikidata.
+Instead for Wikidata the process was different because we didn't have an available Elastic Search index for it.
 In addition there are less artists in Wikidata so the problem to handle million of entities is reduced.
 
-This difference of implementation for DBpedia and Wikidata was also the occasion to experiment two different streets, with and without the Elastic Search.
+This difference of implementation for DBpedia and Wikidata was also the occasion to experiment two different strategies, with and without the Elastic Search.
 We'll resume advantages and issues of both methods at the end of this session.
@@
 We are not interested in retrieving all DBpedia people but only the ones that are linked with the Doremus entities.
-So we query ElasticSearch two times for every Doremus artist considering the name sting and the id string(the id is composed by the name and the birth and death date).
+So we query ElasticSearch two times for every DOREMUS artist considering the name sting and the id string(the id is composed by the name and the birth and death date).
 
@@
 
-Performing this operation,for every Doremus instance, two results can occur:
-
-\begin{enumerate}
-
+Performing this operation, for every Doremus instance, two results can occur:
+
+\begin{enumerate}
 \item we find a list of possible DBpedia matching candidates;
-
 \item we don't find linked DBpedia entities; this is pretty rare and it means that probably this entity is not present on DBpedia;
-
 \end{enumerate}
@@
 
-\item doremus artist uri;
-
-\item doremus artist name;
-
-\item doremus artist birth year;
-
-\item doremus artist death year;
-
-\item doremus candidate uri;
-
-\end{enumerate}
-
-Every row is formed by a possible match Doremus artist - DBpedia artist candidate. 
+\item DOREMUS artist uri;
+
+\item DOREMUS artist name;
+
+\item DOREMUS artist birth year;
+
+\item DOREMUS artist death year;
+
+\item DBpedia candidate uri;
+
+\end{enumerate}
+
+Every row is formed by a possible match DOREMUS artist - DBpedia artist candidate. 
 Our goal is to understand which is, between the possible candidates, the exact one. 
@@
 
-\item years containing strings: 'ca1500', 'compositeur', 'ca 1720', 'ca 1400', 'ca 1750', 'ca 1430', 'ca1750', 'ca1761', 'ca 1580', 'ca 1736', 'ca1551.', 'ca 1555', 'fl 1658', 'ca 1500', 'ca 1700', 'ca 1516', 'ca 1550', 'ca 1760', 'ca 1706', 'vers 1550', 'ca 1570'; we deduced that "ca" and "vers" mean around so we preserved; however we deleted the "compositeur" case that it's probably a mistake.
+\item years containing strings: 'ca1500', 'compositeur', 'ca 1720', 'ca 1400', 'ca 1750', 'ca 1430', 'ca1750', 'ca1761', 'ca 1580', 'ca 1736', 'ca1551.', 'ca 1555', 'fl 1658', 'ca 1500', 'ca 1700', 'ca 1516', 'ca 1550', 'ca 1760', 'ca 1706', 'vers 1550', 'ca 1570'; we deduced that "ca" and "vers" mean around so we preserved; however we ignored the "compositeur" case that it's probably a mistake.
 
@@
 \begin{enumerate}
-
-\item \textbf{The names/labels similarity}: to compute it we used the Python module "fuzzywuzzy".
-We deleted from the DBpedia artists candidates the ones that present a very low label similarity with the Doremus one.
-
+\item \textbf{The names/labels similarity}: to compute it we used the Python module `fuzzywuzzy'.
+We excluded from the DBpedia artists candidates the ones that present a very low label similarity with the Doremus one.
 \item \textbf{The years similarity}: for every pair Doremus artist-DBpedia artist we checked if the born year and the death year was the same.
@@
 \begin{enumerate}
-\item if the complete information is present on both sides and fitted we assigned an high score to the possible DBpedia artist candidate;
+\item if the information is present on both sides and has the same value we assigned an high score to the possible DBpedia artist candidate;
 \item if the year information is present only on one side we assigned score 0 but we continued to consider the DBpedia entity as a possible candidate,because we haven't enough information to say that the 2 entities are not the same;
-\item if the information is present on both sides but it's different:we deleted the DBpedia artist from the candidates.
-Actually we didn't eliminate the candidate if the years differed for 1 or 2 years, because we have noted that, especially for the old artists, the dates are not always precise;
+\item if the information is present on both sides but it's different: we exclude the DBpedia artist from the candidates.
+Actually we didn't eliminate the candidate if the years differed for 1 or 2 years, because we have noticed that, especially for the ancient artists, the dates are not always precise;
 \item if we had only the information about the century: if it matched we preserved the candidate assigning it a low score; alternatively we deleted it;
@@
 
-After having the four different similarity scores we computed a weighted sum of them  to get the final matching score.
+After having the 3 different similarity scores we computed a weighted sum of them  to get the final matching score.
 Actually it was not a precise weighted sum; in fact we wanted to keep into account some particular combinations; for example if the category is too generic and the label score is too low, we delete the candidate also if the years matches.
-We have taken this decision after some trials, noting that considering also these candidates, the number of errors increases because it's more difficult to identify a good threshold to separate bad and good matchings.
+We have taken this decision after some trials: considering also these candidates, the number of errors increases because it's more difficult to identify a good threshold to separate bad and good matchings.
 
@@
 \subsubsection{Transformations}
-The only data that we transformed were the Doremus one because they presented the same problems than before for some years strings.
+The only data that we transformed were the DOREMUS one because they presented the same problems than before for some years strings.
 
 \subsubsection{Similarity measures}
-To match the artist we used the same similarity criteria described before for DBpedia; however it was not feasible applying this similarity measures for all the possible links Wikidata-Doremus artists.
-In fact we got M Doremus artists (around 16000)  and N Wikidata artists (around 14000).
-The complexity of scoring all possible combinations would be $O(m*n)$, where m are the artists of Doremus and n those of Wikidata.
+To match the artist we used the same similarity criteria described before for DBpedia; however it was not feasible applying this similarity measures for all the possible links Wikidata-DOREMUS artists.
+In fact we got M DOREMUS artists (around 16000)  and N Wikidata artists (around 14000).
+The complexity of scoring all possible combinations would be $O(m*n)$, where m are the artists of DOREMUS and n those of Wikidata.
 To avoid this, we indexed the Wikidata artist by label, by birth year and by death year, reducing the complexity to $O(m*\tilde{n})$ where $\tilde{n}$ is the average number of artists by year.
@@
 As instance, supposing to have a pair Doremus-DBpedia artist for which the label perfectly matches, we computed the same year similarity measure than the one used for DBpedia artists.
-Alternatively, in the case in which the label doesn't match but birth or the death year match, we consider only the artist born or died in that year, computing the label similarity metric, keeping only the artist associated with the highest score and filtering it out if the label similarity score was too low.
+Alternatively, in the case in which the label doesn't match but birth or the death year do, we consider only the artist born or died in that year, we compute the label similarity metric, we select only the artist associated with the highest score and keep it if the label similarity score is enough high.
 We remember that for DBpedia we didn't have this complexity issue because the Elastic Search already retrieved a small set of DBpedia candidates for each Doremus artist.
 This similarity approximation is not a big problem because in Wikidata there are a real high number of labels associated to each artist, in many languages but also in many different words ordering.
-So founding a perfect label match is not so rare.
+So finding a perfect label match is not so rare.
 
@@
     \caption{Counts of artist sets.}
+    \label{fig:counts_artists}
   \end{minipage}
@@
     \caption{Metrics.}
+    \label{fig:metrics_artists}
   \end{minipage}
@@
 Since the matching confidence vary with the threshold, we can plot all the important counts and metrics respect to the threshold used.
-In the figure 3 and 4 there are all the counts of the important sets that describe our matching.
-Trues indicates the number of DOREMUS entities matched by ISNI, they are ~3500 and of course they are independent from the threshold.
-Predicted indicates the number of DOREMUS entities matched by us, the number vary with the confidence, there are different drops that corresponds to crucial thresholds defined by our matching algorithm.
-
-The most important thing is that their count goes from ~3000 to ~6000, this indicates that we are matching way more entities than ISNI.
-Doremus intersection represents the number of entities that are matched from both ISNI and us.
-This shows us that there is a part of the DOREMUS entities that ISNI matches and that we are not able to match.
-
-Now, the following sets are all calculated from the intersection set, in fact we cannot compare the matching performances using entities that are not present in both sets.
-Equal show the number of correct matches, we see that this basically overlap with the intersection set, meaning that ISNI and our algorithm match a DOREMUS entity with the same DBpedia entity.
+In Figure \ref{fig:counts_artists} and \ref{fig:metrics_artists} there are all the counts and metrics of the important sets that describe our matching.
+\textit{Trues} indicates the number of DOREMUS entities matched by ISNI, they are  \textapprox3500 and of course they are independent from the threshold.
+\textit{Predicted} indicates the number of DOREMUS entities matched by us, the number vary with the confidence, there are different drops that corresponds to crucial thresholds defined by our matching algorithm.
+
+The most important thing is that their count goes from \textapprox3000 to \textapprox6000. This indicates that we are matching way more entities than ISNI.
+\textit{Doremus intersection} represents the number of entities that are matched from both ISNI and us, so it exists a part of the DOREMUS entities that ISNI matches and that we are not able to match.
+
+Now, the following sets are all calculated from the intersection set. In fact we cannot compare the matching performances using entities that are not present in both sets.
+\textit{Equal} show the number of correct matches, we see that this basically overlap with the intersection set, meaning that ISNI and our algorithm match a DOREMUS entity with the same DBpedia entity.
 Since ISNI matches have a professional validity, this means that we can have a great confidence in the matches produced by our algorithm.
 
-Since equal and DOREMUS intersection are not exactly the same, it means that either our algorithm or ISNI are doing a wrong match.
+Since \textit{equal} and \textit{DOREMUS intersection} are not exactly the same, it means that either our algorithm or ISNI are wrong.
 Looking more closely we saw that in some cases ISNI matches were wrong, especially in corner cases, where there were two persons with the same name.
@@
 
-Looking at the usual metrics, we see that they are extremely high for this kind of match. This means that we are doing an almost perfect match.
+Looking at the usual metrics, we see that they are extremely high for this kind of match.
 We can state that the proposed method based on combinations of labels, classes and dates is able to match almost perfectly the artists of the two datasets.
 Moreover, we are able to find 2000 artists that at the time of writing are not present in the ISNI register.
+More important, we found different cases where ISNI matches were wrong and we corrected them.
 \subsubsection{Wikidata performances}
@@
 The whole problem can be solved by writing a series of queries that find paths of a given depth between two resources. 
-The main problems that needs to be resolved are:
+The main challenges are:
 \begin{enumerate}
@@
 \subsection{Related work (Relfinder)}
-The path finding problem has already been solved in the past with Relfinder: a tool that is able to find all paths with a specified depth between two entities. 
+The path finding problem has already been solved in the past with Relfinder; a tool that is able to find all paths with a specified depth between two entities. 
 The first problem to address is to write a set of queries that can find all paths that have the intermediate node in a fixed position:
@@
 For each entity pair, Relfinder generate all possible queries with at most the given depth and makes them, one by one.
-When the depth increases, the number of possible path shapes increases too in a non linear way, and the whole process takes too time.
-The problem is that the resulting queries take too much time, and when we repeat this process for thousands of pairs, we incur in a scalability problem, the whole process would takes whole weeks.
+When the depth increases, the number of possible path shapes increases too in a non linear way, and the whole process takes too much time.
+Repeating this process for thousands of pairs, we incur in a scalability problem, so that the whole process would takes weeks.
 
@@
     \includegraphics[width=0.9\textwidth]{images/bfs.png}
-    \caption{Bidirectional BFS 2 \cite{artificial_intelligence}}
+    \caption{Bidirectional BFS, adopted from `Artificial Intelligence: A Modern Approach'\cite{artificial_intelligence}}
 \end{figure}
@@
 In this way the time and space complexity goes from $O(b^d)$ of the naive approach to $O(b^{\sfrac{d}{2}})$.
-Looking at paths found by Relfinder, we have seen that usually one direction inversion cover most of the cases, by limiting this we are actually simplifying a lot our problem.
+Looking at paths found by Relfinder, we have seen that usually one direction inversion cover most of the cases, so limiting this simplifies a lot our problem.
 Then, we have seen that for artists and POIs, the connection is most of the times the result of a common node.
@@
 
-Here $$r(r_{i})$$ corresponds to the i resource of the path and $$occ(r_{i})$$ to the number of occurrences of this resource belongs to all considered paths.
+Here $r(r_{i})$ corresponds to the $i_{th}$ resource of the path and $occ(r_{i})$ to the number of occurrences of this resource belongs to all considered paths.
 
@@
 What we can do is to analyze the found paths and see if they show interesting connections.
-The following path is generated in Place Masséna:
+The following path is generated in Palais Lascaris:
 \begin{lstlisting}
@@
 Spotify provides a public API that allows to perform all the operations that can usually be done using the Spotify application.
-These include artist and tracks search, CRUD operations on user playlists and the listening of the tracks' preview.
+These include artist and tracks Search, Create, Read, Update, Delete (CRUD) operations on user playlists and the listening of the tracks' preview.
 All the above mentioned operation are essential for the usage of the application.
 \subsubsection{Authentication}
-Since the end user listen to a Spotify loaded dynamically by the application, there is no need for a client authentication.
-This is perfect because it allows to any user to use our application.
+Since the end user listen to a Spotify playlist loaded dynamically by the application, there is no need for a client authentication.
 Regarding the server, at startup it performs a token based authentication, where the server get possess of a private token used to perform all CRUD operations on the playlist catalog.
-It is important to note that for the correct functioning of the application, a Spotify developer account is needed, then the associated keys are needed in order to obtain the privileges to manage the accounts playlists.
+It is important to note that for the correct functioning of the application, a Spotify developer account linked to an ad-hoc account for the application is needed, then the associated keys are needed in order to obtain the privileges to manage the accounts playlists.
 \subsubsection{Playlist}
@@
 We can either get the tracks of a specific album of an artist, or the most popular tracks of an artist.
-In this project we use the second way because it gives us a number of advantages:
+In this project we use the last way because it gives us a number of advantages:
 \begin{enumerate}
@@
 \item Calculate nearest POIs and assign weights, from these create a unique playlist name.
-\item Select the tracks for each artist linked with the poi.
+\item Select the tracks for each artist linked with the POI.
 \item Select the paths associated to each track.
-\item Create a playlist if it does not exist and add previously selected tracks.
+\item Create a playlist(if it does not exist) and add previously selected tracks.
 \item Save the playlist ID and attach to each track the path between the poi and the track's artist.

### 2017-06-27 server/spotipy_util.py
server token refresh error

@@ -4,6 +4,7 @@ import spotipy.util
 import util
 from spotipy.oauth2 import SpotifyClientCredentials
 
+
 clientid = '2b4bba8dba4d406a8086f33b644ddcd0'
 clientsecret = 'dc13827b3900467383a12e803b10e52f'
 redirect = 'http://localhost'
@@ -37,7 +38,15 @@ def get_playlists_dict(pois,poi_artists,username=username):
 
 
 def create_playlist(playlist_name, username=username, sp=sp):
-    playlist = sp.user_playlist_create(username, playlist_name)
+    try:
+        playlist = sp.user_playlist_create(username, playlist_name)
+    except spotipy.SpotifyException:
+        token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
+                                                   redirect_uri=redirect)
+        sp = spotipy.Spotify(auth=token)
+        sp.trace = False
+        playlist = sp.user_playlist_create(username, playlist_name)
+
     return playlist
 
 

### 2017-06-27 server/spotipy_util.py
server token refresh error

@@ -38,14 +38,11 @@ def get_playlists_dict(pois,poi_artists,username=username):
 
 
 def create_playlist(playlist_name, username=username, sp=sp):
-    try:
-        playlist = sp.user_playlist_create(username, playlist_name)
-    except spotipy.SpotifyException:
-        token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
-                                                   redirect_uri=redirect)
-        sp = spotipy.Spotify(auth=token)
-        sp.trace = False
-        playlist = sp.user_playlist_create(username, playlist_name)
+    token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
+                                       redirect_uri=redirect)
+    sp = spotipy.Spotify(auth=token)
+    sp.trace = False
+    playlist = sp.user_playlist_create(username, playlist_name)
 
     return playlist
 

### 2017-06-27 server/database_helper.py
server: label of returned object contains track name

@@ -8,6 +8,7 @@ from copy import deepcopy
 
 POIS_PATH = os.path.normpath('data/dbpedia_match_nogeo_distinct.csv')
 POIS_ARTISTS_PATH = os.path.normpath('data/poi_artist_path.json')
+TRACKS_ARTISTS_PATH = os.path.normpath('data/tracks.json')
 
 
 def load_pois(poi_artists):
@@ -34,6 +35,13 @@ def load_poi_artists():
     with open(POIS_ARTISTS_PATH, 'r') as input_fp:
         poi_artists = json.load(input_fp)
         return poi_artists
+
+def load_tracks():
+    with open(TRACKS_ARTISTS_PATH, 'r') as input_fp:
+        tracks = json.load(input_fp)
+        return tracks
+
+
 
 
 class PlaylistCollection:

### 2017-06-27 server/server.py

@@ -19,6 +19,8 @@ print(pois)
 playlist_collection = database_helper.PlaylistCollection(pois, poi_artists)
 print(playlist_collection.playlist_dict)
 
+# load tracks
+tracks_collection = database_helper.load_tracks()
 
 # create application
 app = Flask(__name__)
@@ -117,14 +119,15 @@ def create_playlist_from_position():
         # get the correct playlist from the playlist collection
         res = playlist_collection.get_playlist(playlist_name)
         # reshape playlist
-        res['tracks_paths'] = {x[0]:{"path":x[1],"label":str(x[0])} for x in res['tracks_paths']}
-
+        res['tracks_paths'] = {x[0]:{"path":x[1],"label": tracks_collection[x[0]]} for x in res['tracks_paths']}
+        print(res)
         return jsonify(res)
     else:
         # get the correct playlist from the playlist collection
         res = playlist_collection.get_playlist(playlist_name)
         # reshape playlist
-        res['tracks_paths'] = {x[0]:{"path":x[1],"label":str(x[0])} for x in res['tracks_paths']}
+        res['tracks_paths'] = {x[0]:{"path":x[1],"label": tracks_collection[x[0]]} for x in res['tracks_paths']}
+        print(res)
         return jsonify(res)
 
 @app.route('/pois')

### 2017-06-27 server/spotipy_util.py
correct token bug

@@ -19,7 +19,8 @@ sp = spotipy.Spotify(auth=token)
 sp.trace = False
 
 
-def get_playlists_dict(pois,poi_artists,username=username):
+def get_playlists_dict(pois,poi_artists):
+    global sp
     client_credentials_manager = SpotifyClientCredentials(client_id=clientid,client_secret=clientsecret)
     sp = spotipy.Spotify(client_credentials_manager=client_credentials_manager)
 
@@ -37,18 +38,33 @@ def get_playlists_dict(pois,poi_artists,username=username):
     return playlist_dict
 
 
-def create_playlist(playlist_name, username=username, sp=sp):
-    token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
-                                       redirect_uri=redirect)
-    sp = spotipy.Spotify(auth=token)
-    sp.trace = False
-    playlist = sp.user_playlist_create(username, playlist_name)
+def create_playlist(playlist_name):
+    global token
+    global sp
 
+    try:
+        playlist = sp.user_playlist_create(username, playlist_name)
+    except spotipy.SpotifyException:
+        token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
+                                                   redirect_uri=redirect)
+        sp = spotipy.Spotify(auth=token)
+        sp.trace = False
+        playlist = sp.user_playlist_create(username, playlist_name)
     return playlist
 
 
-def add_tracks(playlist_id,track_ids, username=username):
-    sp.user_playlist_add_tracks(username, playlist_id, track_ids)
+def add_tracks(playlist_id,track_ids):
+    global token
+    global sp
+
+    try:
+        sp.user_playlist_add_tracks(username, playlist_id, track_ids)
+    except spotipy.SpotifyException:
+        token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
+                                                   redirect_uri=redirect)
+        sp = spotipy.Spotify(auth=token)
+        sp.trace = False
+        sp.user_playlist_add_tracks(username, playlist_id, track_ids)
 
 
 def get_artist_tracks(artist_name):

### 2017-06-27 report/report.tex
final report

@@
 \documentclass[paper=a4, fontsize=11pt]{scrartcl}
-\linespread{1.1}
+\linespread{1.25}
 \usepackage[english]{babel}
@@
 \subsection{Research problems}
-Finding relations inside DBpedia is a known problem which has been solved in the past. So we could simply look for POIs and Artists in DBpedia and then link them using known algorithms.
-Unfortunately, DBpedia is not perfect: it is true that it contains POIs and Artists, but these entities are not cleanly defined, they usually contain dirty data that can tremendously affect our performances.
-On the other side, POIs and Artists can be found in highly specialized datasets, but unfortunately, they do not contain links to each other, and even worse they are not linked to DBpedia.
-This means that by using these databases alone we cannot find relations.
-What is done in this cases is to link highly specialized datasets to DBpedia, in this way we can exploit the advantages of both worlds: highly specialized datasets give us confidence and trust in our main entities (POIs and Artists), while DBpedia allows us to find relations between them thanks to its generality.
-Once we have our two sets, we need to find paths that link them. This problem has been solved in the past with Relfinder, a tool that is able to find relations between entities.
-What we have seen is that POIs and Artists are generally far from each other, in fact usually we need 5 hops to link them, this is more that the average DBpedia degree and it is also more than what Relfinder can do, in fact, Relfinder query times are too high once we set more that 4 hops.
-This lead us to create a pathfinder that can work in acceptable times with 100.000 pairs that are far from each other.
+The main challenge is the goal itself: is it possible to suggest interesting artists based on the user context?
+Since we intend to find DBpedia relations between POIs and artists, how deep are this kind of relations?
+Are there tools that have already solved completely this problem?
+In which context they work and are they scalable on a big number of entities?
+What is the shape of these connections?
+Do they have a common pattern?
+How many are they?
+Can we filter only the interesting ones?
+How can we define an interesting connection?
+
+It is our intention to use specialized datasets that are not directly linked to DBpedia. Therefore, What are the important properties to consider when doing such a job?
 
@@
 We aim at reducing the need for human intervention in defining classes and weights with the hope that this approach will be completely data driven and easily scalable to different cities. 
-Finally, we demonstrate the effectiveness of our work through an APP that  ....
-
+Finally, we demonstrate the effectiveness of our work through an APP that drives the user experience in the exploration of a city, recommending songs linked to the user position.
+In addition it presents the reason of the recommendation through a graphical visualization of the path between the artist that composed the song and the POI chosen for the recommendation.
 For this experimental work, we chose Nice because because it is a medium sized city that allows us to deal with both popular and unpopular places.
@@
 \end{lstlisting}
-
 \subsubsection{DBpedia}
@@
 \subsection{Entity Linking process}
+
+\begin{figure}[!htb]
+  \centering 
+    \includegraphics[width=1\textwidth]{images/pipeline.png}
+    \caption{Entity linking pipeline}
+    \label{fig:pipeline}
+\end{figure}
+
+Figure \ref{fig:pipeline} summarizes the main steps, datasets, and outputs of the entity linking process.
 In order to link our three set, we copy them locally and then we perform the linking process.
@@
 \item Filter matches above threshold.
+\item Evaluate results.
 \end{enumerate}
@@
 \item DBpedia labels: `Conservatory of Nice' @en, `Conservatoire de Nice' @fr
-\item 3cixty label: `Conservatoire de nice'
+\item 3cixty label: `Conservatoire de Nice'
 \end{itemize}
@@
 
+\begin{figure}[!htb]
+  \centering 
+    \includegraphics[width=0.5\textwidth]{images/parc.png}
+    \caption{Parc Phœnix coordinates: blue marker from DBpedia, red marker from Google Maps}
+    \label{fig:parc}
+\end{figure}
+
 Among other informations, we have the coordinates, but we do not use them because not all entities have them.
 Moreover, we have seen experimentally that using the DBpedia coordinates we obtain worse results because of their inaccuracy.
+This is clearly visible in Figure\ref{fig:parc}
 Regarding 3cixty entities, they have very accurate coordinates and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.
@@
 So it was necessary to get the types of each resource, in particular the ones linked with the idea of composer.
-When we performed the final scoring we assigned higher scores more specific the category is.
+When we performed the final scoring we assigned higher scores to the most specific categories.
 The considered categories are:
@@
 \item for composers \verb|http://dbpedia.org/class/yago/Composer109947232| 
-
 \end{enumerate}
@@
 To check that we basically looked at the birth date and, if it was not too far from the current date, we considered the artist as still alive, and we increased the score also for the death year matching basing the rise on the probably to be alive computed through a Gaussian distribution.
-This score rise was less significant than when we had explicitly the same death year;
+This score rise was less significant than when we had explicitly the same death year.
 
@@
 If the entity is not a person we assigned a negative score.
+The final scores are:
+\begin{itemize}
+\item People: 0.01
+\item Creators: 0.07
+\item Artists: 0.31
+\item Musicians: 0.74
+\item Composers: 1
+\end{itemize}
+
 \end{enumerate}
@@
 We have taken this decision after some trials: considering also these candidates, the number of errors increases because it's more difficult to identify a good threshold to separate bad and good matchings.
-
-TODO insert aggregation functions formula
 
@@
 More important, we found different cases where ISNI matches were wrong and we corrected them.
+
 \subsubsection{Wikidata performances}
-todo: fabio
+\begin{figure}[!htb]
+  \centering
+  \begin{minipage}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{images/count_artists_wiki.png}
+    \caption{Counts of artist sets.}
+    \label{fig:counts_artists_wiki}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{images/metrics_artists_wiki.png}
+    \caption{Metrics.}
+    \label{fig:metrics_artists_wiki}
+  \end{minipage}
+\end{figure}
+In Figure \ref{fig:counts_artists_wiki} is possible to note that the DOREMUS artists matched by ISNI with Wikidata are more numerous, in fact there are 4000 artists linked.
+This is because Wikidata ontology is more clear and it is easier to match entities.
+On the other side, our algorithm matches less artists respect to DBpedia. This is due to the fact that it is not immediate to select Wikidata artists, so we only have a subset of them.
+Looking at the artists matched by our algorithm and ISNI, we note that they are almost equal, this means that our algorithm is capable to perform a good linking operation.
+Moreover, our algorithm find \textapprox400 artists that are not present in the ISNI dataset.
 
@@
     \includegraphics[width=0.9\textwidth]{images/bfs.png}
-    \caption{Bidirectional BFS, adopted from `Artificial Intelligence: A Modern Approach'\cite{artificial_intelligence}}
+    \caption{Bidirectional BFS, adopted from `Artificial Intelligence: A Modern Approach'~\cite{artificial_intelligence}}
 \end{figure}
@@
 \subsection{Selection Algorithm}
-todo: lorenzo
 Now that we have all our filtered path, we need to find the best ones, those that shows interesting links between POIs and Artists. Our interest is to consider both path length and exclusiveness. 
@@
 Here $r(r_{i})$ corresponds to the $i_{th}$ resource of the path and $occ(r_{i})$ to the number of occurrences of this resource belongs to all considered paths.
-
-$$sim(artist,poi) = 1-k(\frac{\log(len(artist,poi)-1)}{\log(2*(deep_max -1))})-(1-k)gen$$
-
-At the end, we select 5 Artists for each POI looking at those artists with the highest score, where the score is given by their most interesting path.
+Then we define the similarity measure between artist and POI:
+$$sim(artist,poi) = 1-k(\frac{\log(len(artist,poi)-1)}{\log(2*(deep_{max} -1))})-(1-k)gen$$
+
+In this formulation $deep_{max}$ identifies the biggest deep that we have in our paths (7); $len(artist,poi)$ identifies the considered path length.
+
+At the end, we select 5 Artists for each POI looking at those artists with the highest score, where the score is given by their most interesting paths.
 
@@
 \begin{lstlisting}
-"http://dbpedia.org/resource/Chick_Corea", 
-"http://dbpedia.org/property/associatedActs", 
-"http://dbpedia.org/resource/Herbie_Hancock", 
-"http://dbpedia.org/ontology/instrument", 
-"http://dbpedia.org/resource/Fairlight_CMI", 
-"http://purl.org/dc/terms/subject", 
-"http://dbpedia.org/resource/Category:Music_technology", 
-"http://www.w3.org/2004/02/skos/core#broader", 
-"http://dbpedia.org/resource/Category:Musical_instruments", 
-"http://www.w3.org/2004/02/skos/core#broader",       
-"http://dbpedia.org/resource/Category:Musical_instrument_museums", 
-"http://purl.org/dc/terms/subject", 
-"http://dbpedia.org/resource/Palais_Lascaris"
+{
+"entity":"dbr:Chick_Corea",
+"p1":"dbp:associatedActs", 
+"o1":"dbr:Herbie_Hancock", 
+"p2":"dbo:instrument", 
+"o2":"dbr:Fairlight_CMI", 
+"p3":"http://purl.org/dc/terms/subject", 
+"o":"dbc:Music_technology", 
+"p3_":"http://www.w3.org/2004/02/skos/core#broader", 
+"o2_":"dbc:Musical_instruments", 
+"p2_":"http://www.w3.org/2004/02/skos/core#broader",       
+"o1_":"dbc:Musical_instrument_museums", 
+"p1_":"http://purl.org/dc/terms/subject", 
+"poi":"dbr:Palais_Lascaris"
+}
 \end{lstlisting}
@@
 \begin{lstlisting}
-"http://dbpedia.org/resource/Aristide_Bruant", 
-"http://purl.org/dc/terms/subject", 
-"http://dbpedia.org/resource/Category:Nightclub_owners", 
-"http://www.w3.org/2004/02/skos/core#broader", 
-"http://dbpedia.org/resource/Category:Nightclubs", 
-"http://www.w3.org/2004/02/skos/core#broader", 
-"http://dbpedia.org/resource/Category:Music_venues", 
-"http://www.w3.org/2004/02/skos/core#broader", 
-"http://dbpedia.org/resource/Category:Music_venues_by_country", 
-"http://www.w3.org/2004/02/skos/core#broader", 
-"http://dbpedia.org/resource/Category:Music_venues_in_France", 
-"http://purl.org/dc/terms/subject", 
-"http://dbpedia.org/resource/Palais_Nikaia"
+{
+"entity":"dbr:Aristide_Bruant", 
+"p1":"http://purl.org/dc/terms/subject", 
+"o1":"dbr:Nightclub_owners", 
+"p2":"http://www.w3.org/2004/02/skos/core#broader", 
+"o2":"dbc:Nightclubs", 
+"p3":"http://www.w3.org/2004/02/skos/core#broader", 
+"o":"dbc:Music_venues", 
+"p3":"http://www.w3.org/2004/02/skos/core#broader", 
+"o2_":"dbc:Music_venues_by_country", 
+"p2_":"http://www.w3.org/2004/02/skos/core#broader", 
+"o1_":"dbc:Music_venues_in_France", 
+"p1_":"http://purl.org/dc/terms/subject", 
+"poi":"dbr:Palais_Nikaia"
+}
 \end{lstlisting}
@@
 \begin{lstlisting}
-"http://dbpedia.org/resource/Yannick_Noah", 
-"http://purl.org/dc/terms/subject",   
-"http://dbpedia.org/resource/Category:French_tennis_coaches", 
-"http://www.w3.org/2004/02/skos/core#broader", 
-"http://dbpedia.org/resource/Category:Tennis_in_France", 
-"http://www.w3.org/2004/02/skos/core#broader", 
-"http://dbpedia.org/resource/Category:Tennis_venues_in_France", 
-"http://purl.org/dc/terms/subject", 
-"http://dbpedia.org/resource/Nice_Lawn_Tennis_Club"
+"entity":"dbr:Yannick_Noah", 
+"p1":"http://purl.org/dc/terms/subject",   
+"o1":"dbc:French_tennis_coaches", 
+"p2":"http://www.w3.org/2004/02/skos/core#broader", 
+"o":"dbc:Tennis_in_France", 
+"p2":"http://www.w3.org/2004/02/skos/core#broader", 
+"o1_":"dbc:Tennis_venues_in_France", 
+"p1_":"http://purl.org/dc/terms/subject", 
+"poi":"dbr:Nice_Lawn_Tennis_Club"
 \end{lstlisting}
@@
 Once the client position is validated, it is necessary to select the POIs that will be used for the recommendation. 
-In fact, it is not possible to directly recommend tracks based on positions because otherwise we would have a playlist for each possible coordinates pair.
-The following operations needs to be done:
-\begin{enumerate}
-\item Calculate distance from the each POI to the user position. Since we are using coordinates, the distance is calculated using the haversine distance, which is very accurate and fast.
-\item Add to the list the nearest POI, regardless of the distance.
-\item Add the remaining two nearest POIs if their distance is inferior of 1 km.
-\item For each element in the list, add 10 meters to the distance and then take the log2.
-By adding 10 meters we are adding a bias to all our distances, in this way positions too near to us are not over-weighted respect far distances.
-Then, the log2 squashes distances until 1 km to a restricted range of values.
-\item Calculate repartition weights using the following equation:
+The recommendation is performed in the following way: select the nearest POI and two other POIs in a range of 2 km, then calculate repartition weights using the following equation:
 $$w_i = \Bigg \lfloor 10 \dfrac{\dfrac{1}{\log_2 (d_i + 10)}}{\sum \dfrac{1}{\log_2 (d_i + 10)} } \Bigg \rceil$$
+
 In this way we obtain normalized weights from 0 to 10 that are inversely proportional to the log base 2 of the distance.
-\end{enumerate}
-At this point we have a direct mapping between POIs weights and a position
 
@@
 For each artist there is a direct mapping with its tracks.
-The problem is: given a playlist name, find the correct tracks.
+The problem is: given a group of POIs, find the correct tracks.
 The playlist name encodes the weights of each poi, and each weight express exactly the number of tracks that must be chosen for the POI associated.
@@
 \section{Mobile Web Application}
-The Web application is implemented using AngularJS and its common MVVM model.
+\begin{figure}[!htb]  
+\begin{minipage}[t]{0.45\textwidth}
+\includegraphics[width=\linewidth]{images/Player.png}
+\caption{Music Player}
+\label{fig:music_player}
+\end{minipage}
+\hspace{\fill}
+\begin{minipage}[t]{0.45\textwidth}
+\includegraphics[width=\linewidth]{images/Map.png}
+\caption{Map}
+\label{fig:map}
+\end{minipage}
+
+\vspace*{0.5cm} % (or whatever vertical separation you prefer)
+\begin{minipage}[t]{0.45\textwidth}
+\includegraphics[width=\linewidth]{images/Visualization_1.png}
+\caption{Visualization Options}
+\label{fig:visualization_option}
+\end{minipage}
+\hspace{\fill}
+\begin{minipage}[t]{0.45\textwidth}
+\includegraphics[width=\linewidth]{images/Visualization_2.png}
+\caption{Visualization}
+\label{fig:visualization}
+\end{minipage}
+
+\end{figure}
+The Web application is implemented using AngularJS and its common MVC model.
 Using the Angular framework we are able to create complex single page applications that reduces to the minimum the client server interactions.
@@
 One of those is the Google Map module that we use to handle all the POI navigation.
-\subsubsection{Music Player}
+In fact all the applications is based on the user position.
+The app is composed of three views: Music Player, Map, Relation Visualization.
+
+\subsection{Music Player}
 The music player is implemented using the Spotify Play Button.
-This is a special <iframe> that loads a simplified Spotify player for a specified playlist.
+This is a special \textless{}iframe\textgreater that loads a simplified Spotify player for a specified playlist.
 This solution is extremely convenient because it simply needs a playlist ID to run.
 Since the playlists are created server side and are recovered using the REST API, the whole process is very simple.
-Unfortunately it is not possible to manipulate programmatically the <iframe> and this limit the whole user experience.
+Unfortunately it is not possible to manipulate programmatically the \textless{}iframe\textgreater and this limit the whole user experience.
 As an improvement, we could build a custom player that still uses the Spotify API.
-\subsection{Google Map API}
-\subsubsection{POIs placement}
-todo: Lorenzo
-\subsubsection{Navigation}
-
-\subsection{Relation visualization (and Path format)}
-todo: Lorenzo
+The list of songs proposed in the player are the ones associated to the artist linked with the POIs nearer to the user.
+The player page is visible in Figure \ref{fig:music_player}.
+
+\subsection{Angular Google Maps API}
+The Angular Google Maps directive supports the majority of the style attributes that the native API supports.
+Google’s native web API is used for visualizing maps and accessing rich mapping features.
+The ones used in the application are:
+
+\begin{enumerate}
+\item Markers: they are used to identify the POIs and the user position on the map
+\item Directions: they are used to give directions that allow the user to reach easily a specific POI on the map.
+\end{enumerate}
+
+The map view is composed of two elements: the big navigation map and on the bottom a small Spotify player. Figure \ref{fig:map})
+
+\subsection{Relation visualization}
+This view allows the user to visualize the link between POIs and artists.
+This is essential to deeply understand why a specific artist is recommended for a specific POI.
+Moreover, one of the goals of the project is to stimulate the user curiosity, proposing interesting connections between music and places.
+In order to draw the connection graph we use 'Sigma.js`'\footnote{Sigma.js: http://sigmajs.org/}, a JavaScript library dedicated to graph drawing.
+For our application the library is useful for the following purposes:
+\begin{enumerate}
+\item It offers a pretty good path visualization.
+\item It can define labels and styles to attach to nodes and edges.
+\item It allows to open a window associated with nodes and edges by clicking on them. The window shows the page related to the resource in the graph.
+\end{enumerate}
+In order to start visualizing connections it is necessary to select a composer between the ones linked with the songs in the playlist and a POI between the ones kept into consideration for the recommendation (Figure \ref{fig:visualization_option}).
+
+After selecting these options is possible to see the path between selected POI and the selected artist.
+This is showed in the Figure \ref{fig:visualization}.
+The green node represents the song related to the artist, the artist node is red, the POI node is blue.
+The middle resource that links POI and artist is represented in yellow.
+
 \section{Conclusion and Future Work}
-todo: fabio-lorenzo, improve
 In this work, we presented CityMusic: a context-aware content-based recommender system for artists. 
-Regarding the first part: the interlinking, we showed that is possible to link POIs and artists to DBpedia achieving good metrics.
+Regarding the first part: the interlinking, we showed that is possible to link POIs and artists to DBpedia achieving good metrics by using only the POI labels.
+In addition we linked also the Doremus artists with both Dbpedia and Wikidata artists, with an high level of precision.
+The quality allowed to correct some ISNI mistakes and to propose matchings that are not present in ISNI in order to add them to Doremus.
 
 We worked on the Relfinder algorithm, by making it scalable.
-We think that having a scalable solution for the relation finding is crucial for any project that aims to use heavily the huge knowledge graph that DBpedia is.
+Having a scalable solution for the relation finding is crucial for any project that aims to use heavily the huge knowledge graph that DBpedia contains.
+So we developed a solution that is computationally efficient and that can be executed in short times.
+This allowed us to explore the semantic graph with high depths, retrieving a big number of paths.
+
+We proposed a metric to select the best paths between the ones retrieved. This metric drove to discover some particular paths, as the one linked to Yannick Noah.
 
@@
 \item Improve the relation finding algorithm allowing it to find more complex relations without affecting performances.
+In the case of the artist for example, we should try to increase the number of matchings considering the linked works.
 \item Improve the relation selection algorithm: this part needs a big rework because in the selected paths, there are some that are not meaningful for the user.
-\item Evaluate the overall approach with real users 
+In addition we should try to explore the semantic graph not considering only one middle path but all possible.
+Actually we develop an algorithm that perform this job, but it's difficult to control the number of entities retrieved by the queries.
+\item Evaluate the overall approach with real users.
 \item Use additional context informations available in 3cixty and DOREMUS.
@@
 By linking DOREMUS songs with DBpedia we hope to extend the semantic recommendation taking into account song-specific relations with a POI.
-Linking songs to DBpedia is hard, but we showed that is possible, the main problem is to find good relations between POIs and Songs.
-This operation is even harder than linking artists to POIs because songs on DBpedia are very poor regarding of links with other resources.
+Linking songs to DBpedia is hard, but we showed that is possible.
+The main challenge continue to be the search for good relations between POIs and Songs.
+This operation is even harder than linking artists to POIs because songs on DBpedia are very poorly described, and have big lacks in links with other resources.
 \end{enumerate}

### 2017-06-28 myApp/app.js
final app

@@ -5,16 +5,28 @@
 // Declare app level module which depends on views, and components
 angular.module('myApp', [
     'ngRoute',
+    'ngMaterial',
     'uiGmapgoogle-maps',
     'myApp.login',
     'myApp.home',
     'myApp.map',
-    'myApp.geolocation'
+    'myApp.geolocation',
+    'myApp.recommendation',
+    'myApp.visualization'
 ])
 
     .config(['$routeProvider', function ($routeProvider) {
         $routeProvider.otherwise({redirectTo: '/home'});
     }])
+
+    .config(function($sceDelegateProvider) {
+        $sceDelegateProvider.resourceUrlWhitelist([
+            // Allow same origin resource loads.
+            'self',
+            // Allow loading from outer templates domain.
+            'https://open.spotify.com/**'
+        ]);
+    })
 
     .config(function(uiGmapGoogleMapApiProvider) {
         uiGmapGoogleMapApiProvider.configure({
@@ -41,25 +53,73 @@ angular.module('myApp', [
     })
 
 
-    .controller("NavCtrl",['$scope','$location','$rootScope','watchOptions',function($scope,$location,$rootScope,watchOptions){
-        $scope.home_path = "/home";
-        $scope.map_path = "/map";
-        $scope.login_path = "/login";
+    .controller("NavCtrl",['$scope','$location','$rootScope','Geolocation','watchOptions','Recommendation','shareRecommendation','$window',
+        function($scope,$location,$rootScope,Geolocation,watchOptions,Recommendation,shareRecommendation,$window){
+            $scope.home_path = "/home";
+            $scope.map_path = "/map";
+            $scope.visualization_path = "/visualization";
+            $scope.showPlaylist = false;
+            $scope.isHome = false;
+            $scope.isMap = false;
 
-        $scope.IsActive = function(str){
-            if ($location.path()==str) return true;
-            else return false;
-        }
 
 
-        $rootScope.$on('$locationChangeSuccess', function(event){
-            if ($location.path()==$scope.login_path) {
-                $scope.showNavbar = false;
+
+            var default_playlist = '5tDTLlIwA0EzoYEbEky9Ro';
+            $scope.playlist_id = default_playlist;
+            var position_data = Geolocation.watchPosition(watchOptions);
+            position_data.then(
+                null,
+                function(err) {
+                    $scope.showPlaylist = true;
+                    $window.alert("You should share your position to use all functionalities!!!");
+                },
+                function(position) {
[…]

### 2017-06-28 myApp/geolocation/geolocation-service.js

@@ -3,42 +3,52 @@
 
 angular.module('myApp.geolocation.service', [])
 
-    .factory('Geolocation', ['$q',function($q) {
+    .factory('Geolocation', ['$q','watchOptions',function($q,watchOptions) {
+
+        var lat='';
+        var long='';
+        var error='';
+        var modification = 0;
 
         return {
-            getCurrentPosition: function (options) {
-                var q = $q.defer();
-
-                navigator.geolocation.getCurrentPosition(function (result) {
-                    q.resolve(result);
-                }, function (err) {
-                    q.reject(err);
-                }, options);
-
-                return q.promise;
-            },
 
             watchPosition: function (options) {
+                console.log(444);
                 var q = $q.defer();
 
                 var watchID = navigator.geolocation.watchPosition(function (result) {
+                    console.log(8888);
+                    lat = result.coords.latitude;
+                    long = result.coords.longitude;
                     q.notify(result);
-                    console.log(result)
+                    modification += 1;
+                    if (modification > 1000){
+                        modification = 1;
+                    }
                 }, function (err) {
+                    console.log(8234);
+                    error = err;
                     q.reject(err);
-                }, options);
-
-                q.promise.cancel = function () {
-                    navigator.geolocation.clearWatch(watchID);
-                };
-
-                q.promise.clearWatch = function (id) {
-                    navigator.geolocation.clearWatch(id || watchID);
-                };
+                    modification += 1;
+                    if (modification > 1000){
+                        modification = 1;
+                    }
+                }, watchOptions);
 
                 q.promise.watchID = watchID;
 
                 return q.promise;
+            },
+
+
+            getCoordinates:function () {
+                return [lat,long,error];
+            },
+            setCoordinates:function (lat_,long_,err_) {
+            },
+
+            getModification:function () {
+                return modification;
             },
 
             clearWatch: function (watchID) {

### 2017-06-28 myApp/geolocation/geolocation-share.js

@@ -1,0 +1,41 @@
+'use strict';
+
+
+angular.module('myApp.geolocation.service', [])
+
+    .factory('GeolocationShare', ['Geolocation',function(Geolocation) {
+
+        var q = $q.defer();
+
+        var watchID = navigator.geolocation.watchPosition(function (result) {
+            q.notify(result);
+            console.log(result);
+        }, function (err) {
+            q.reject(err);
+        }, options);
+
+
+        return {
+
+            watchPosition: function (options) {
+
+
+                q.promise.cancel = function () {
+                    navigator.geolocation.clearWatch(watchID);
+                };
+
+                q.promise.clearWatch = function (id) {
+                    navigator.geolocation.clearWatch(id || watchID);
+                };
+
+                q.promise.watchID = watchID;
+
+                return q.promise;
+            },
+
+            clearWatch: function (watchID) {
+                return navigator.geolocation.clearWatch(watchID);
+            }
+        };
+
+    }]);

### 2017-06-28 myApp/home/home.js

@@ -10,23 +10,51 @@ angular.module('myApp.home', ['ngRoute'])
         });
     }])
 
+
     // Controller
-    .controller('HomeCtrl', ['$scope', '$location', '$log','Geolocation','watchOptions',
-        function($scope,  $location, $log,Geolocation,watchOptions) {
+    .controller('HomeCtrl', ['$scope', '$location', '$log','Geolocation','watchOptions','Recommendation','shareRecommendation','$window',
+        function($scope,  $location, $log,Geolocation,watchOptions,Recommendation,shareRecommendation,$window) {
+            //console.log(watchOptions)
+            $scope.selectedTrack = false;
+            $scope.flag_select = false;
+            $scope.$watch(Recommendation.getTracks, function() {
+                $scope.songList = Recommendation.getTracks();
+                if ($scope.songList.length != 0) $scope.flag_select = true;
+            });
 
-            console.log(watchOptions)
-            var position_data = Geolocation.watchPosition(watchOptions);
-            position_data.then(
-                null,
-                function(err) {
-                    // error
-                },
-                function(position) {
-                    var lat  = position.coords.latitude;
-                    var long = position.coords.longitude;
 
-                });
-            //TODO
+            $scope.visualizePath = function(){
+                $location.path('/visualization');
+            }
+
+
+
+
+            $scope.$watch('selectedSong', function(newValue, oldValue) {
+
+                if (newValue != oldValue){
+                    if (newValue == null) {
+                        $scope.selectedTrack = false;
+                    }
+                    else {
+                        $scope.selectedTrack = true;
+                        for (var key in $scope.songList){
+                            //console.log(key);
+                            if ($scope.songList[key].label == newValue.label){
+                                shareRecommendation.setPath(newValue.label,$scope.songList[key].path);
+                                break;
+                            }
+                        }
+                    }
+
+                }
+
+            });
+
+
+
+
+
 
 
     }]);

### 2017-06-28 myApp/lib/sigma/src/renderers/canvas/sigma.canvas.labels.def.js

@@ -1,0 +1,87 @@
+;(function(undefined) {
+  'use strict';
+
+  if (typeof sigma === 'undefined')
+    throw 'sigma is not declared';
+
+  // Initialize packages:
+  sigma.utils.pkg('sigma.canvas.labels');
+
+  /**
+   * This label renderer will just display the label on the right of the node.
+   *
+   * @param  {object}                   node     The node object.
+   * @param  {CanvasRenderingContext2D} context  The canvas context.
+   * @param  {configurable}             settings The settings function.
+   */
+  sigma.canvas.labels.def = function(node, context, settings) {
+    var fontSize,
+        prefix = settings('prefix') || '',
+        size = node[prefix + 'size'],
+        labelWidth = 0,
+        labelPlacementX,
+        labelPlacementY,
+        alignment;
+
+    if (size < settings('labelThreshold'))
+      return;
+
+    if (typeof node.label !== 'string')
+      return;
+
+    if (settings('labelAlignment') === undefined){
+      alignment = settings('defaultLabelAlignment');
+    } else {
+      alignment = settings('labelAlignment');
+    }
+
+    fontSize = (settings('labelSize') === 'fixed') ?
+        settings('defaultLabelSize') :
+    settings('labelSizeRatio') * size;
+
+    context.font = (settings('fontStyle') ? settings('fontStyle') + ' ' : '') +
+        fontSize + 'px ' + settings('font');
+    context.fillStyle = (settings('labelColor') === 'node') ?
+        (node.color || settings('defaultNodeColor')) :
+        settings('defaultLabelColor');
+
+    labelWidth = context.measureText(node.label).width;
+    labelPlacementX = Math.round(node[prefix + 'x'] + size + 3);
+    labelPlacementY = Math.round(node[prefix + 'y'] + fontSize / 3);
+
+    switch (alignment) {
+      case 'inside':
+        if (labelWidth <= size * 2){
+          labelPlacementX = Math.round(node[prefix + 'x'] - labelWidth / 2 );
+        }
+        break;
+      case 'center':
+        labelPlacementX = Math.round(node[prefix + 'x'] - labelWidth / 2 );
+        break;
+      case 'left':
+        labelPlacementX = Math.round(node[prefix + 'x'] - size - labelWidth - 3 );
+        break;
+      case 'right':
+        labelPlacementX = Math.round(node[prefix + 'x'] + size + 3);
+        break;
+      case 'top':
[…]

### 2017-06-28 myApp/recommendation/recommendation-service.js

@@ -3,127 +3,178 @@
 
 angular.module('myApp.recommendation.service', [])
 
-    .factory('Recommendation', ['$q','Geolocation',function($q,Geolocation) {
+    .factory('Recommendation', ['$q','$http','Geolocation',function($q,$http) {
 
-        var pois = [ {
-            id:1,
-            latitude: 43.719740,
-            longitude: 7.257380,
-            title: '2 tiltle'
-
-        }, {
-            id: 2,
-            latitude: 43.699740,
-            longitude: 7.257398,
-            title: '3 title'
-        }];
-
-        function compare(a,b) {
-            if (a.distance > b.distance)
-                return -1;
-            else return 1;
-        };
+        var server_address = 'http://127.0.0.1:5000';
 
 
-        var computeDistance = function(lat1,lon1,lat2,lon2){
-            function toRad(x) {
-                return x * Math.PI / 180;
-            }
-
-            var R = 6371; // km
-            var x1 = lat2-lat1;
-            var dLat = x1.toRad();
-            var x2 = lon2-lon1;
-            var dLon = x2.toRad();
-            var a = Math.sin(dLat/2) * Math.sin(dLat/2) +
-                Math.cos(lat1.toRad()) * Math.cos(lat2.toRad()) *
-                Math.sin(dLon/2) * Math.sin(dLon/2);
-            var c = 2 * Math.atan2(Math.sqrt(a), Math.sqrt(1-a));
-            var d = R * c;
-            return d
-        }
-
-        var getListenPoi = function (myLat,myLong){
-            var poi_distances = []
-            for (var p in pois) {
-                var poi_lat = p.latitude;
-                var poi_long = p.longitude;
-                var distance = computeDistance(poi_lat,poi_long);
-                var obj = {
-                    id : p.id,
-                    distance: distance
-                }
-                poi_distances.push(obj);
-            }
-            poi_distances.sort(compare);
-            var tot = poi_distances[0].distance + poi_distances[1].distance + poi_distances[2].distance;
-            var rand = Math.random();
-            var threshold_1 =  poi_distances[0].distance / tot;
-            var threshold_2 = poi_distances[1].distance / tot;
-            var threshold_3 = poi_distances[2].distance / tot;
-            if (rand <= threshold_1){
-                return
-            }
-            else if ()
-                switch case return
-
-
-        }
-
-
-        var position_data = Geolocation.watchPosition(watchOptions);
-        position_data.then(
-            null,
-            function(err) {
[…]

### 2017-06-28 server2/database_helper.py
clean

@@ -1,0 +1,63 @@
+import csv
+import json
+import os
+from threading import Lock
+import spotipy_util
+from copy import deepcopy
+
+
+POIS_PATH = os.path.normpath('data/dbpedia_match_nogeo_distinct.csv')
+POIS_ARTISTS_PATH = os.path.normpath('data/poi_artist_path.json')
+TRACKS_ARTISTS_PATH = os.path.normpath('data/tracks.json')
+
+
+def load_pois(poi_artists):
+    with open(POIS_PATH, 'r') as input_fp:
+        count = 1
+        reader = csv.reader(input_fp, )
+        # skip header
+        reader.next()
+        pois = []
+        for row in reader:
+            poi = dict()
+            poi['id'] = count
+            poi['label'] = row[2]
+            poi['uri'] = row[3]
+            poi['latitude'] = float(row[5])
+            poi['longitude'] = float(row[6])
+            if poi['uri'] in poi_artists:
+                pois.append(poi)
+                count += 1
+        return pois
+
+
+def load_poi_artists():
+    with open(POIS_ARTISTS_PATH, 'r') as input_fp:
+        poi_artists = json.load(input_fp)
+        return poi_artists
+
+def load_tracks():
+    with open(TRACKS_ARTISTS_PATH, 'r') as input_fp:
+        tracks = json.load(input_fp)
+        return tracks
+
+
+
+
+class PlaylistCollection:
+    def __init__(self, pois, poi_artists):
+        self.lock = Lock()
+        self.playlist_dict = spotipy_util.get_playlists_dict(pois, poi_artists)
+
+    def get_playlist(self, playlist_name):
+        with self.lock:
+            if playlist_name not in self.playlist_dict:
+                return None
+            else:
+                return deepcopy(self.playlist_dict[playlist_name])
+
+    def put_playlist(self, playlist_name, playlist):
+        with self.lock:
+            new_playlist = deepcopy(playlist)
+            self.playlist_dict[playlist_name] = new_playlist
+

### 2017-06-28 server2/etl/dump_tracks.py

@@ -1,0 +1,106 @@
+import csv
+import os
+import json
+import spotipy
+import spotipy.util
+from SPARQLWrapper import SPARQLWrapper, JSON
+
+clientid = '2b4bba8dba4d406a8086f33b644ddcd0'
+clientsecret = 'dc13827b3900467383a12e803b10e52f'
+redirect = 'http://localhost'
+username = 'fabio_ellena'
+
+# necessary to create/add track to public spotify
+scope = 'playlist-modify-public'
+
+def get_artist_tracks(artist_name):
+    token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
+                                               redirect_uri=redirect)
+    sp = spotipy.Spotify(auth=token)
+    sp.trace = False
+
+    # get matching artist
+
+    results = sp.search(q='artist:' + artist_name, type='artist')
+    artists = results['artists']['items']
+    artist = None
+    if len(artists) == 0:
+        return None
+    artist = max(artists, key=lambda x: x['popularity'])
+
+    top_tracks = sp.artist_top_tracks(artist['id'], country='FR')['tracks']
+    return_tracks = []
+    for track in top_tracks:
+        return_tracks.append((track['id'], track['name']))
+    return return_tracks
+
+
+def get_dbpedia_label(uri):
+    sparql = SPARQLWrapper("http://dbpedia.org/sparql")
+    sparql.setQuery("""
+                        SELECT ?label ?preferredLabel 
+            WHERE { 
+               <%s> rdfs:label ?label .
+            FILTER (lang(?label) = "" || lang(?label) = "en") 
+               OPTIONAL { 
+                 <%s> rdfs:label ?preferredLabel . 
+                 FILTER (lang(?preferredLabel) = "" || lang(?preferredLabel) = "tk") 
+               } 
+            } limit 1
+                        """ % (uri, uri))
+    sparql.setReturnFormat(JSON)
+    results = sparql.query().convert()
+
+    for artist in results['results']['bindings']:
+        try:
+            label = artist['preferredLabel']['value']
+        except KeyError:
+            label = artist['label']['value']
+        return label
+
+
+def get_doremus_label(uri):
+    sparql = SPARQLWrapper("http://data.doremus.org/sparql")
+    sparql.setQuery("""
+                        SELECT ?label 
+            WHERE { 
+               <%s> foaf:name ?label .
+            } limit 1
[…]

### 2017-06-28 server2/etl/poi_artist_linker.py

@@ -1,0 +1,30 @@
+import csv
+from pprint import pprint
+import json
+import os
+
+
+POIS_PATH = os.path.normpath('../data/dbpedia_match_nogeo_distinct.csv')
+
+
+def get_linked_artists():
+    with open('../data/artists_tracks.json', 'r') as input_fp:
+        artists = json.load(input_fp)
+
+        artists = artists.keys()
+
+
+with open(POIS_PATH, 'r') as input_fp:
+    count = 0
+    reader = csv.reader(input_fp, )
+    # skip header
+    reader.next()
+
+    links = dict()
+    for row in reader:
+        poi_uri = row[3]
+        link_artist = get_linked_artists()
+        links[poi_uri] = link_artist
+
+with open('../data/poi_artists.json', 'wb') as output_fp:
+    json.dump(links, output_fp)

### 2017-06-28 server2/etl/poi_enrich.py

@@ -1,0 +1,163 @@
+#read all
+#remove bus stations and add position to each 3cixty poi, remove dbpedia poi that are not in nice
+#group by dbpedia uri
+
+#foreach group:
+#    keep entries with the highest score
+#    remove entries with score < 90
+#	 keep the nearest to the center
+
+import csv
+import urllib2
+import json
+from geopy.distance import vincenty
+from SPARQLWrapper import SPARQLWrapper,JSON
+
+NICE_COORDINATES = (43.7034, 7.2663)
+THRESHOLD = 85
+
+def add_info(row):
+    url = row[0].rsplit('/',1)[1]
+    req = urllib2.Request('http://aplicaciones.localidata.com/eldaSuit/place/id/%s?_view=list' % url)
+    resp = urllib2.urlopen(req)
+    # 200
+    body = resp.read()
+    result = json.loads(body)
+    if len(result['result']['items']) > 0:
+        if type(result['result']['items'][0]["geoLocation"]['lat']) == list:
+            lat = float(result['result']['items'][0]["geoLocation"]['lat'][0])
+        else:
+            lat = float(result['result']['items'][0]["geoLocation"]['lat'])
+        if type(result['result']['items'][0]["geoLocation"]['long']) == list:
+            long_ = float(result['result']['items'][0]["geoLocation"]['long'][0])
+        else:
+            long_ = float(result['result']['items'][0]["geoLocation"]['long'])
+        row.append((lat,long_))
+    
+        uri = row[3]
+        sparql = SPARQLWrapper("http://dbpedia.org/sparql")
+        sparql.setQuery("""
+            SELECT ?place ?placeLabel ?lat ?long
+             WHERE {
+            <%s> geo:lat ?lat.
+            <%s> geo:long ?long.
+            }
+            """ % (uri,uri))        
+        sparql.setReturnFormat(JSON)
+        results = sparql.query().convert()
+
+        for place in results['results']['bindings']:
+            lat = float(place['lat']['value'])
+            long_ = float(place['long']['value'])
+            if vincenty(NICE_COORDINATES, (lat,long_)).km > 15:
+                return False
+        return True
+    else:
+        return False
+
+with open('../data/dbpedia_match_nogeo.csv','r') as input_fp:
+    reader=csv.reader(input_fp,)
+    # skip header
+    reader.next()
+    rows = [ [unicode(col,'utf-8') for col in row] for row in reader]
+
+new_rows = []
+for row in rows:
[…]

### 2017-06-28 server2/etl/poi_to_artist.py

@@ -1,0 +1,36 @@
+
+# coding: utf-8
+
+# In[2]:
+
+import csv
+import json
+with open('../data/final_paths.csv','r') as input_fp:
+    reader=csv.reader(input_fp,)
+    # skip header
+    reader.next()
+    rows = [ [unicode(col,'utf-8') for col in row] for row in reader]
+
+
+# In[26]:
+
+poi_artist_path = dict()
+for row in rows:
+    poi_artist_path[row[12]] = dict()
+
+
+# In[27]:
+
+for row in rows:
+    if len(poi_artist_path[row[12]]) < 5:
+        try:
+            poi_artist_path[row[12]][row[0]]
+        except KeyError:
+            poi_artist_path[row[12]][row[0]] = row
+
+
+# In[30]:
+
+with open('../data/poi_artist_path.json','wb') as output_fp:
+    json.dump(poi_artist_path,output_fp)
+

### 2017-06-28 server2/server.py

@@ -1,0 +1,144 @@
+from flask import Flask, request, jsonify, abort
+import database_helper
+import spotipy_util
+import util
+import threading
+from copy import deepcopy
+
+# initialization phase: load everything in memory
+
+# load poi_artists_path
+poi_artists = database_helper.load_poi_artists()
+
+# load pois
+pois = database_helper.load_pois(poi_artists)
+print(len(pois))
+print(pois)
+
+# load playlists
+playlist_collection = database_helper.PlaylistCollection(pois, poi_artists)
+print(playlist_collection.playlist_dict)
+
+# load tracks
+tracks_collection = database_helper.load_tracks()
+
+# create application
+app = Flask(__name__)
+
+# define endpoints
+
+
+@app.route('/')
+def home_page():
+    return 'hello world'
+
+
+@app.route('/position')
+def position():
+    # /position?lat=43.697093&lon=7.270747
+    # show the coordinates
+    lat = request.args.get('lat', default=None, type=float)
+    lon = request.args.get('lon', default=None, type=float)
+    if lat is None or lon is None:
+        abort(404)
+        # abort(404)
+    if lat < -90 or lat > +90:
+        abort(404)
+    if lon < -180 or lon > +180:
+        abort(404)
+
+    # latitude and longitude are correct
+    # find nearest poi
+    point = (lat, lon)
+    near_pois = util.get_near_pois(point, pois)
+
+    return jsonify(near_pois)
+
+
+@app.route('/playlist_name')
+def get_playlist_name():
+    # show the coordinates
+    lat = request.args.get('lat', default=None, type=float)
+    lon = request.args.get('lon', default=None, type=float)
+    if lat is None or lon is None:
+        abort(404)
+        # abort(404)
+    if lat < -90 or lat > +90:
+        abort(404)
+    if lon < -180 or lon > +180:
+        abort(404)
+
+    # latitude and longitude are correct
+    # find nearest poi
+    point = (lat, lon)
+    near_pois = util.get_near_pois(point, pois)
+    name = util.create_playlist_name(near_pois)
+    return jsonify(name)
+
+
+@app.route('/create_playlist')
+def create_playlist_from_position():
+    # show the coordinates
+    lat = request.args.get('lat', default=None, type=float)
+    lon = request.args.get('lon', default=None, type=float)
+    if lat is None or lon is None:
+        abort(404)
+        # abort(404)
+    if lat < -90 or lat > +90:
+        abort(404)
+    if lon < -180 or lon > +180:
[…]

### 2017-06-28 server2/spotipy_util.py

@@ -1,0 +1,87 @@
+from pprint import pprint
+import spotipy
+import spotipy.util
+import util
+from spotipy.oauth2 import SpotifyClientCredentials
+
+
+clientid = '2b4bba8dba4d406a8086f33b644ddcd0'
+clientsecret = 'dc13827b3900467383a12e803b10e52f'
+redirect = 'http://localhost'
+username = 'fabio_ellena'
+
+# necessary to create/add track to public spotify
+scope = 'playlist-modify-public'
+
+# get token if cached, otherwise refresh, or generate new prompting to user
+token = spotipy.util.prompt_for_user_token(username,scope,client_id=clientid,client_secret=clientsecret,redirect_uri=redirect)
+sp = spotipy.Spotify(auth=token)
+sp.trace = False
+
+
+def get_playlists_dict(pois,poi_artists):
+    global sp
+    client_credentials_manager = SpotifyClientCredentials(client_id=clientid,client_secret=clientsecret)
+    sp = spotipy.Spotify(client_credentials_manager=client_credentials_manager)
+
+    playlists = sp.user_playlists(username)
+    playlist_dict = dict()
+    
+    for playlist in playlists['items']:
+        name = playlist['name']
+        tracks_paths = util.select_tracks(name,pois,poi_artists)
+        playlist_object = dict()
+        playlist_object['name'] = name
+        playlist_object['id'] = playlist['id']
+        playlist_object['tracks_paths'] = tracks_paths
+        playlist_dict[playlist['name']] = playlist_object
+    return playlist_dict
+
+
+def create_playlist(playlist_name):
+    global token
+    global sp
+
+    try:
+        playlist = sp.user_playlist_create(username, playlist_name)
+    except spotipy.SpotifyException:
+        token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
+                                                   redirect_uri=redirect)
+        sp = spotipy.Spotify(auth=token)
+        sp.trace = False
+        playlist = sp.user_playlist_create(username, playlist_name)
+    return playlist
+
+
+def add_tracks(playlist_id,track_ids):
+    global token
+    global sp
+
+    try:
+        sp.user_playlist_add_tracks(username, playlist_id, track_ids)
+    except spotipy.SpotifyException:
+        token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
[…]

### 2017-06-28 server2/util.py

@@ -1,0 +1,100 @@
+from geopy.distance import vincenty
+import numpy as np
+import copy
+from pprint import pprint
+import spotipy_util
+
+def get_near_pois(source, original_pois):
+    """given a position and the poi, get three nearest ones"""
+
+    def log2(x):
+        return np.log(x)/np.log(2)
+
+    def add_distance_wrapper(src):
+        def add_distance(point):
+            point['distance'] = vincenty(src, (float(point['latitude']), float(point['longitude']))).meters
+            point['distance'] += 10
+            point['distance_log'] = log2(point['distance'])
+            return point
+        return add_distance
+
+
+
+    MAX_RADIUS = 2000
+
+    MAX_RADIUS_LOG = log2(MAX_RADIUS)
+
+    new_pois = copy.deepcopy(original_pois)
+
+    add_distance_function = add_distance_wrapper(source)
+
+    near_pois = map(add_distance_function, new_pois)
+
+    near_pois = sorted(near_pois, key=lambda x: x['distance'])[:3]
+
+    filtered_pois = [near_pois.pop(0)]
+    filtered_pois += filter(lambda x: x['distance_log'] < MAX_RADIUS_LOG, near_pois)[:2]
+
+    # weight part
+    total_score = sum(1. / x['distance_log'] for x in filtered_pois)
+    total_weight = 0
+    for poi in filtered_pois:
+        poi['weight'] = 1. / (total_score * poi['distance_log'])
+        total_weight += poi['weight']
+    for poi in filtered_pois:
+        poi['weight'] = int(round(poi['weight'] * 10. / total_weight))
+    return filtered_pois
+
+
+def create_playlist_name(pois):
+    """given a list of (id,weight), return an identifier"""
+
+    ids = [str(x['id']) for x in pois]
+    weights = [str(x['weight']) for x in pois]
+    lists = zip(ids, weights)
+    lists = sorted(lists, key=lambda _: (_[1], _[0]), reverse=True)
+
+    groups = [':'.join(x) for x in lists]
+    name = '_'.join(groups)
+    return name
+
+
+
+def select_tracks(playlist_name, pois, poi_artists):
+    """given a playlist name, return list of tracks and related paths"""
+
+    groups = playlist_name.split('_')
+    poi_weight_list = [group.split(':') for group in groups]
+    track_path_list = set()
+
+    for p_w in poi_weight_list:
+        poi_index = int(p_w[0])
+        weight = int(p_w[1])
+        dbpedia_uri = pois[poi_index-1]['uri']
[…]

### 2017-06-29 myApp/app.js
final app

@@ -48,7 +48,7 @@ angular.module('myApp', [
     }])
 
     .constant('watchOptions', {
-        timeout : 3000,
+        timeout : 15000,
         enableHighAccuracy: false // may cause errors if true
     })
 
@@ -75,9 +75,9 @@ angular.module('myApp', [
                     $window.alert("You should share your position to use all functionalities!!!");
                 },
                 function(position) {
+                    console.log(27);
                     var lat  = position.coords.latitude;
                     var lon = position.coords.longitude;
-
                     Recommendation.getRecommendation(lat,lon)
                         .then(
                             function(d) {

### 2017-07-10 myApp/app.js
clean + fix

@@ -74,9 +74,9 @@
             $window.alert("You should share your position to use all functionalities!!!");
           },
           function(position) {
-            console.log(27);
             var lat = position.coords.latitude;
             var lon = position.coords.longitude;
+            console.log('getting recommendation');
             Recommendation.getRecommendation(lat, lon)
               .then(function(d) {
                   $scope.playlist_id = d.id;

### 2017-07-10 myApp/geolocation/geolocation-service.js

@@ -1,59 +1,58 @@
-'use strict';
+(function(angular) {
 
+  'use strict';
 
-angular.module('myApp.geolocation.service', [])
+  angular.module('myApp.geolocation.service', [])
+    .factory('Geolocation', ['$q', 'watchOptions', function($q, watchOptions) {
 
-    .factory('Geolocation', ['$q','watchOptions',function($q,watchOptions) {
+      var lat, long;
+      var error;
+      var modification = 0;
 
-        var lat='';
-        var long='';
-        var error='';
-        var modification = 0;
+      return {
 
-        return {
+        watchPosition: function(options) {
+          console.log('watching position');
+          var q = $q.defer();
 
-            watchPosition: function (options) {
-                console.log(444);
-                var q = $q.defer();
-
-                var watchID = navigator.geolocation.watchPosition(function (result) {
-                    console.log(8888);
-                    lat = result.coords.latitude;
-                    long = result.coords.longitude;
-                    q.notify(result);
-                    modification += 1;
-                    if (modification > 1000){
-                        modification = 1;
-                    }
-                }, function (err) {
-                    console.log(8234);
-                    error = err;
-                    q.reject(err);
-                    modification += 1;
-                    if (modification > 1000){
-                        modification = 1;
-                    }
-                }, watchOptions);
-
-                q.promise.watchID = watchID;
-
-                return q.promise;
-            },
-
-
-            getCoordinates:function () {
-                return [lat,long,error];
-            },
-            setCoordinates:function (lat_,long_,err_) {
-            },
-
-            getModification:function () {
-                return modification;
-            },
-
-            clearWatch: function (watchID) {
-                return navigator.geolocation.clearWatch(watchID);
+          var watchID = navigator.geolocation.watchPosition(function(result) {
+            lat = result.coords.latitude;
+            long = result.coords.longitude;
+            console.log('position found: ', lat, long);
+            q.notify(result);
+            modification += 1;
+            if (modification > 1000) {
+              modification = 1;
             }
-        };
+          }, function(err) {
+            console.error(err);
+            error = err;
+            q.reject(err);
+            modification += 1;
+            if (modification > 1000) {
+              modification = 1;
+            }
+          }, watchOptions);
+
+          q.promise.watchID = watchID;
+
+          return q.promise;
+        },
+
+
+        getCoordinates: function() {
+          return [lat, long, error];
+        },
[…]

### 2017-07-10 myApp/map/map.js

@@ -1,6 +1,11 @@
 (function(angular) {
   'use strict';
 
+  const NICE_CENTER = {
+    latitude: 43.709742,
+    longitude: 7.257396
+  };
+
   angular.module('myApp.map', [])
 
     // Controller
@@ -17,27 +22,11 @@
           url: 'files/user_mark.png'
         };
 
-
-
-
-
-
-
         $scope.noSharedPosition = false;
 
-
-
         //$scope.markers = pois;
-
-
-
-        /*
-
-
-*/
         $scope.onClickMarker = function(marker, eventName, model) {
           $scope.show_hide_info(model);
-
         };
 
 
@@ -63,7 +52,7 @@
               clickOutsideToClose: true
             });
           }
-        }
+        };
 
         $scope.userModification = function() {
           if (!$scope.enableModification) {
@@ -72,21 +61,21 @@
         };
 
 
+
         $scope.disableModification = function() {
-          if (!lat) {
+          // reset user position to the one coming from GPS
+          if (lat) {
             $scope.map.center = {
               latitude: lat,
               longitude: long
             };
           } else {
-            $scope.map.center = {
-              latitude: 43.709742,
-              longitude: 7.257396
-            };
+            $scope.map.center = NICE_CENTER;
           }
           $scope.map.zoom = 14;
           $scope.enableModification = false;
         };
+
         $scope.showPath = function(song) {
           shareRecommendation.setPath(song.label, song.path);
           $location.path('/visualization');
@@ -98,8 +87,7 @@
           directionsDisplay.setMap(null);
           directionsDisplay.setPanel(null); // clear directionpanel from the map
           directionsDisplay = new google.maps.DirectionsRenderer(); // this is to render again, otherwise your route wont show for the second time searching
-
-        }
+        };
 
 
         var directionsDisplay = new google.maps.DirectionsRenderer();
@@ -132,73 +120,21 @@
             }
           });
           $scope.enableDirections = true;
-        }
+        };
         $scope.already_set = false;
         $scope.$watch(Geolocation.getModification, function() {
           var coordinates = Geolocation.getCoordinates();
-          lat = coordinates[0];
           var err = coordinates[2];
 
-
-
-          if (lat != '') {
-            long = coordinates[1];
-            // marker object
-            var position_marker = {
-              id: "user_marker",
-              latitude: lat,
-              longitude: long,
-              label: 'your position',
-              icon: image_user
-            };
-
-            if (!$scope.already_set) {
[…]

### 2017-07-10 app/map/map.js
fix

@@ -150,6 +150,7 @@
 
           lat = coordinates[0];
           long = coordinates[1];
+          if(!lat) return;
 
           // marker object
           var position_marker = {
@@ -168,6 +169,7 @@
               }, (errResponse) => {
                 console.error('Error while fetching Currencies');
               });
+
             $scope.markers.push(position_marker);
             $scope.map = {
               control: {},
@@ -175,7 +177,7 @@
                 latitude: lat,
                 longitude: long
               },
-              zoom: 14,
+              zoom: 14
             };
             $scope.already_set = true;
           } else {

### 2017-07-10 app/app.js
fix

@@ -6,14 +6,12 @@
       'ui.router',
       'ngMaterial',
       'uiGmapgoogle-maps',
-      'myApp.login',
       'myApp.home',
       'myApp.map',
       'myApp.geolocation',
       'myApp.recommendation',
       'myApp.visualization'
     ])
-
     .config(['$stateProvider', '$urlRouterProvider', function($stateProvider, $urlRouterProvider) {
 
       $urlRouterProvider.otherwise('/home');

### 2017-07-10 app/login/login.js

@@ -1,18 +1,0 @@
-'use strict';
-
-angular.module('myApp.login', ['ngRoute'])
-
-// Route Config
-    .config(['$routeProvider', function($routeProvider) {
-        $routeProvider.when('/login', {
-            templateUrl: 'login/login.html',
-            controller: 'LoginCtrl'
-        });
-    }])
-
-    // Controller
-    .controller('LoginCtrl', ['$scope', '$location', '$log',
-        function($scope,  $location, $log) {
-            //TODO
-
-        }]);

### 2017-07-10 app/recommendation/recommendation-service.js

@@ -1,174 +1,168 @@
-'use strict';
+(function(angular) {
+  'use strict';
+
+  const server_address = 'http://localhost:5000';
+  angular.module('myApp.recommendation.service', [])
+    .factory('Recommendation', ['$q', '$http', 'Geolocation', function($q, $http) {
+      var tracks = [];
 
 
-angular.module('myApp.recommendation.service', [])
+      return {
+        getPois: function() {
+          return $http.get(server_address + '/pois')
+            .then(
+              function(response) {
+                return response.data;
+              },
+              function(errResponse) {
+                console.error('Error while fetching users');
+                return $q.reject(errResponse);
+              }
+            );
+        },
 
-  .factory('Recommendation', ['$q', '$http', 'Geolocation', function($q, $http) {
-
-    var server_address = 'http://localhost:5000';
-
-
-    var tracks = [];
-
-    return {
-      getPois: function() {
-        return $http.get(server_address + '/pois')
-          .then(
-            function(response) {
-              return response.data;
-            },
-            function(errResponse) {
-              console.error('Error while fetching users');
-              return $q.reject(errResponse);
-            }
-          );
-      },
-
-      getRecommendation: function(lat, lon) {
-        return $http.get(server_address + '/create_playlist?lat=+' + lat + '&lon=' + lon)
-          .then(
-            function(response) {
-              tracks = response.data.tracks_paths;
-              return response.data;
-            },
-            function(errResponse) {
-              console.error('Error while fetching users');
-              return $q.reject(errResponse);
-            }
-          );
-      },
-      getSonglistbyPoi: function(lat, lon) {
-        return $http.get(server_address + '/create_playlist?lat=+' + lat + '&lon=' + lon)
-          .then(
-            function(response) {
-              return response.data.tracks_paths;
-            },
-            function(errResponse) {
-              console.error('Error while fetching users');
-              return $q.reject(errResponse);
-            }
-          );
-      },
-      getTracks: function() {
-        return tracks;
-      }
-    };
-
-
-    //43.7274
-    //7.30667
-
-  }])
-  .factory('shareRecommendation', function() {
-    var start_x = 0.0;
-    var start_y = 0.0;
[…]

### 2017-07-10 app/home/home.js
modified app

@@ -6,13 +6,14 @@
     // Controller
     .controller('HomeCtrl', ['$scope', '$location', '$log', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$window', '$rootScope',
       function($scope, $location, $log, Geolocation, watchOptions, Recommendation, shareRecommendation, $window, $rootScope) {
+        $scope.spinner_visible = true;
         $rootScope.iframeClass = "big_playlist";
         //console.log(watchOptions)
         $scope.selectedTrack = false;
         $scope.flag_select = false;
         $scope.$watch(Recommendation.getTracks, function() {
           $scope.songList = Recommendation.getTracks();
-          $scope.flag_select = !$scope.songList.length;
+          if ($scope.songList.length > 0) $scope.flag_select = true;
         });
 
 
@@ -26,6 +27,7 @@
         $scope.$watch('selectedSong', function(newValue, oldValue) {
 
           if (newValue != oldValue) {
+            $scope.spinner_visible = false;
             if (newValue == null) {
               $scope.selectedTrack = false;
             } else {

### 2017-07-10 app/recommendation/recommendation-service.js

@@ -4,7 +4,7 @@
   const server_address = 'http://localhost:5000';
   angular.module('myApp.recommendation.service', [])
     .factory('Recommendation', ['$q', '$http', 'Geolocation', function($q, $http) {
-      var tracks = [];
+      var tracks = {};
 
 
       return {

### 2017-07-10 app/home/home.js
fix

@@ -12,33 +12,29 @@
         $scope.flag_select = false;
         $scope.$watch(Recommendation.getTracks, function() {
           $scope.songList = Recommendation.getTracks();
-          $scope.flag_select = !$scope.songList.length;
+          $scope.flag_select = !!Object.values($scope.songList).length;
         });
 
 
         $scope.visualizePath = function() {
           $location.path('/visualization');
-        }
-
-
-
+        };
 
         $scope.$watch('selectedSong', function(newValue, oldValue) {
 
           if (newValue != oldValue) {
-            if (newValue == null) {
+            if (!newValue) {
               $scope.selectedTrack = false;
-            } else {
-              $scope.selectedTrack = true;
-              for (var key in $scope.songList) {
-                //console.log(key);
-                if ($scope.songList[key].label == newValue.label) {
-                  shareRecommendation.setPath(newValue.label, $scope.songList[key].path);
-                  break;
-                }
+              return;
+            }
+            $scope.selectedTrack = true;
+            for (var value of $scope.songList) {
+              //console.log(key);
+              if (value.label == newValue.label) {
+                shareRecommendation.setPath(newValue.label, value.path);
+                break;
               }
             }
-
           }
 
         });

### 2017-07-10 app/recommendation/recommendation-service.js

@@ -4,7 +4,7 @@
   const server_address = 'http://localhost:5000';
   angular.module('myApp.recommendation.service', [])
     .factory('Recommendation', ['$q', '$http', 'Geolocation', function($q, $http) {
-      var tracks = [];
+      var tracks = {};
 
 
       return {
@@ -80,7 +80,7 @@
         x = unescape(x);
         var y = x.split("/");
         var res = y[y.length - 1].replace(/_/g, " ").replace("Category:", "");
-        console.log(res);
+
         if ((res.length > 14) && (j !== 0) && (j !== 12) && (j !== 6)) {
           res = res.substr(0, 14) + '...';
         }

### 2017-07-10 app/recommendation/recommendation.js

@@ -1,6 +1,7 @@
-'use strict';
+(function(angular) {
+  'use strict';
 
-angular.module('myApp.recommendation', [
+  angular.module('myApp.recommendation', [
     'myApp.recommendation.service'
-]);
-
+  ]);
+})(angular);

### 2017-07-10 app/recommendation/recommendation-service.js
fix

@@ -4,8 +4,7 @@
   const server_address = 'http://localhost:5000';
   angular.module('myApp.recommendation.service', [])
     .factory('Recommendation', ['$q', '$http', 'Geolocation', function($q, $http) {
-      var tracks = {};
-
+      var tracks = [];
 
       return {
         getPois: function() {
@@ -23,16 +22,18 @@
 
         getRecommendation: function(lat, lon) {
           return $http.get(server_address + '/create_playlist?lat=+' + lat + '&lon=' + lon)
-            .then(
-              function(response) {
-                tracks = response.data.tracks_paths;
-                return response.data;
-              },
-              function(errResponse) {
-                console.error('Error while fetching users');
-                return $q.reject(errResponse);
+            .then(function(response) {
+              tracks = [];
+              for (let key of Object.keys(response.data.tracks_paths)) {
+                let v = response.data.tracks_paths[key];
+                v.key = key;
+                tracks.push(v);
               }
-            );
+              return response.data;
+            }, function(errResponse) {
+              console.error('Error while fetching users');
+              return $q.reject(errResponse);
+            });
         },
         getSonglistbyPoi: function(lat, lon) {
           return $http.get(server_address + '/create_playlist?lat=+' + lat + '&lon=' + lon)
@@ -88,6 +89,7 @@
       };
 
       var setPath = function(trackname, path_dirty) {
+
         track = trackname;
         null_res_1 = 0;
         null_res_2 = 0;
@@ -95,9 +97,10 @@
         path = [];
         positions_colors = [];
         var avg_resource = '';
-        for (var i = 0; i < path_dirty.length; i++) {
-          var p = path_dirty[i];
-          if (!p) {
+
+        for (let i in path_dirty) {
+          let p = path_dirty[i];
+          if (p) {
             var res = changeStringStyle(path_dirty[i], i);
             if (i == 6) avg_resource = res[0];
             path.push(res[0]);
@@ -119,9 +122,8 @@
         var pos_x = start_x;
         var pos_y = start_y;
 
-        for (i = 0; i < path.length; i++) {
+        for (let i = 0; i < path.length; i++) {
           var col;
-
           if (i % 2 == 0) {
             if (i == path.length - 1) {
               col = '#4D84FF';
@@ -157,12 +159,10 @@
       };
 
       return {
-        setPath: setPath,
-        getPath: getPath,
-        changeStringStyle: changeStringStyle,
-        getTrack: function() {
[…]

### 2017-07-10 app/visualization/visualization.js

@@ -134,12 +134,13 @@
           $scope.songList = Recommendation.getTracks();
           var artistList = {};
           var poiList = {};
-          for (var key in $scope.songList) {
-            var artist = $scope.songList[key]["path"][0];
+          console.log($scope.songList);
+          for (var song of $scope.songList) {
+            var artist = song.path[0];
             var artist_name = shareRecommendation.changeStringStyle(artist, 0)[1];
-            var poi = $scope.songList[key]["path"][12];
+            var poi = song.path[12];
             var poi_name = shareRecommendation.changeStringStyle(poi, 12)[1];
-            if (artist in artistList) artistList[artist]['uri_ref'].push(poi);
+            if (artist in artistList) artistList[artist].uri_ref.push(poi);
             else {
               artistList[artist] = {};
               artistList[artist]['uri'] = artist;
@@ -155,7 +156,7 @@
               poiList[poi]['uri_ref'] = [artist];
               poiList[poi]['active'] = true;
             }
-            //$scope.songList[key]
+            //song
             $scope.artistList = Object.values(artistList);
             $scope.poiList = Object.values(poiList);
           }
@@ -203,17 +204,17 @@
         };
 
         $scope.showVisualization = function() {
-          for (var key in $scope.songList) {
-            if (($scope.songList[key]["path"][0] == $scope.selectedArtist.uri) && ($scope.songList[key]["path"][12] == $scope.selectedPoi.uri)) {
-              shareRecommendation.setPath($scope.songList[key].label, $scope.songList[key].path);
+          for (var song of $scope.songList) {
+            if ((song.path[0] == $scope.selectedArtist.uri) && (song.path[12] == $scope.selectedPoi.uri)) {
+              shareRecommendation.setPath(song.label, song.path);
               data_link = shareRecommendation.getPath();
-              if (data_link[0] != "") {
+              if (data_link[0] !== "") {
                 drawPath();
                 break;
               }
             }
           }
-        }
+        };
 
 
 

### 2017-07-10 server/spotipy_util.py
change user for spotify

@@ -5,10 +5,10 @@ import util
 from spotipy.oauth2 import SpotifyClientCredentials
 
 
-clientid = '2b4bba8dba4d406a8086f33b644ddcd0'
-clientsecret = 'dc13827b3900467383a12e803b10e52f'
+clientid = '4b115cf521ba4691a64a622eb3158f44'
+clientsecret = '8d8e24a769cf4f6797e6325b33b16016'
 redirect = 'http://localhost'
-username = 'fabio_ellena'
+username = 'doremus_fr'
 
 # necessary to create/add track to public spotify
 scope = 'playlist-modify-public'
@@ -26,7 +26,7 @@ def get_playlists_dict(pois,poi_artists):
 
     playlists = sp.user_playlists(username)
     playlist_dict = dict()
-    
+
     for playlist in playlists['items']:
         name = playlist['name']
         tracks_paths = util.select_tracks(name,pois,poi_artists)

### 2017-07-11 app/app.js
fix

@@ -56,13 +56,16 @@
 
 
     .controller("NavCtrl", ['$scope', '$location', '$rootScope', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$window',
-      function($scope, $location, $rootScope, Geolocation, watchOptions, Recommendation, shareRecommendation, $window) {$scope.spinner_visible = true;
+      function($scope, $location, $rootScope, Geolocation, watchOptions, Recommendation, shareRecommendation, $window) {
+          $scope.spinner_visible = true;
         $scope.showPlaylist = false;
         $scope.isHome = false;
         $scope.isMap = false;
 
 
-
+        $scope.loading = function(){
+            return $location.path() == '/home' && $scope.spinner_visible;
+        };
 
         var default_playlist = '5tDTLlIwA0EzoYEbEky9Ro';
         $scope.playlist_id = default_playlist;

### 2017-07-11 app/home/home.js

@@ -6,7 +6,6 @@
     // Controller
     .controller('HomeCtrl', ['$scope', '$location', '$log', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$window', '$rootScope',
       function($scope, $location, $log, Geolocation, watchOptions, Recommendation, shareRecommendation, $window, $rootScope) {
-        $scope.spinner_visible = true;
         $rootScope.iframeClass = "big_playlist";
         //console.log(watchOptions)
         $scope.selectedTrack = false;
@@ -14,6 +13,8 @@
         $scope.$watch(Recommendation.getTracks, function() {
           $scope.songList = Recommendation.getTracks();
           $scope.flag_select = !!Object.values($scope.songList).length;
+          if ($scope.flag_select){
+          }
         });
 
 
@@ -24,7 +25,6 @@
         $scope.$watch('selectedSong', function(newValue, oldValue) {
 
           if (newValue != oldValue) {
-            $scope.spinner_visible = false;
             if (!newValue) {
               $scope.selectedTrack = false;
               return;

### 2017-07-11 app/map/map.js

@@ -11,8 +11,21 @@
     // Controller
     .controller('MapCtrl', ['$scope', '$location', '$log', 'uiGmapGoogleMapApi', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$mdDialog', '$rootScope',
       function($scope, $location, $log, uiGmapGoogleMapApi, Geolocation, watchOptions, Recommendation, shareRecommendation, $mdDialog, $rootScope) {
+
+        function distance(lat1, lon1, lat2, lon2) {
+          var p = 0.017453292519943295;    // Math.PI / 180
+          var c = Math.cos;
+          var a = 0.5 - c((lat2 - lat1) * p)/2 +
+              c(lat1 * p) * c(lat2 * p) *
+              (1 - c((lon2 - lon1) * p))/2;
+
+          return 12742 * Math.asin(Math.sqrt(a)); // 2 * R; R = 6371 km
+        }
+
+
         $scope.spinner_visible = true;
         $rootScope.iframeClass = "small_playlist";
+
 
         $scope.enableModification = false;
         $scope.enableDirections = false;
@@ -29,6 +42,8 @@
         $scope.onClickMarker = function(marker, eventName, model) {
           $scope.show_hide_info(model);
         };
+
+
 
 
         $scope.show_hide_info = function(model) {
@@ -129,6 +144,7 @@
           $scope.enableDirections = true;
         };
         $scope.already_set = false;
+
         $scope.$watch(Geolocation.getModification, function() {
           var coordinates = Geolocation.getCoordinates();
           var err = coordinates[2];
@@ -148,14 +164,15 @@
             $scope.map = {
               control: {},
               center: {
-                latitude: 43.709742,
-                longitude: 7.257396
+                latitude: NICE_CENTER.latitude,
+                longitude: NICE_CENTER.longitude
               },
               zoom: 14,
               options: {
                 disableDefaultUI: true
               }
             };
+
             $scope.noSharedPosition = true;
             return;
           }
@@ -184,12 +201,24 @@
               });
 
             $scope.markers.push(position_marker);
-            $scope.map = {
-              control: {},
-              center: {
+            var center;
+            if (distance(NICE_CENTER.latitude,NICE_CENTER.longitude,lat,long) < 6){
+              center =  {
                 latitude: lat,
                 longitude: long
-              },
+              }
+            }
+            else {
+              center =  {
+                latitude: NICE_CENTER.latitude,
+                longitude: NICE_CENTER.longitude
+              };
[…]

### 2017-07-12 app/recommendation/recommendation-service.js
production ready

@@ -1,7 +1,9 @@
-(function(angular) {
+(function(angular, window) {
   'use strict';
 
-  const server_address = 'http://localhost:5000';
+  const PROD = 'citymus.doremus.org';
+  const server_address = (window.location.hostname == PROD) ? '/' : 'http://localhost:5000';
+
   angular.module('myApp.recommendation.service', [])
     .factory('Recommendation', ['$q', '$http', 'Geolocation', function($q, $http) {
       var tracks = [];
@@ -165,4 +167,4 @@
         getTrack: () => track
       };
     });
-})(angular);
+})(angular, window);

### 2017-07-12 app/recommendation/recommendation-service.js
fix

@@ -2,7 +2,7 @@
   'use strict';
 
   const PROD = 'citymus.doremus.org';
-  const server_address = (window.location.hostname == PROD) ? '/' : 'http://localhost:5000';
+  const server_address = (window.location.hostname == PROD) ? '.' : 'http://localhost:5000';
 
   angular.module('myApp.recommendation.service', [])
     .factory('Recommendation', ['$q', '$http', 'Geolocation', function($q, $http) {

### 2017-07-12 relfinder/artists _all/pytest.py
folder renaming

@@ -1,38 +1,0 @@
-
-import urllib2
-s = """
-PREFIX rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
-PREFIX skos: <http://www.w3.org/2004/02/skos/core#>
-SELECT * WHERE {
-?of1 ?pf1 <http://dbpedia.org/resource/Rome> . 
-?middle ?pf2 ?of1 . 
-?middle ?ps1 <http://dbpedia.org/resource/Lazio> . 
-
-FILTER ((?pf1 != rdf:type ) && 
-(?pf1 != skos:subject ) && 
-(?pf1 != <http://dbpedia.org/property/wikiPageUsesTemplate> ) && 
-(?pf1 != <http://dbpedia.org/property/wordnet_type> ) && 
-(?pf2 != rdf:type ) && 
-(?pf2 != skos:subject ) && 
-(?pf2 != <http://dbpedia.org/property/wikiPageUsesTemplate> ) && 
-(?pf2 != <http://dbpedia.org/property/wordnet_type> ) && 
-(?ps1 != rdf:type ) && 
-(?ps1 != skos:subject ) && 
-(?ps1 != <http://dbpedia.org/property/wikiPageUsesTemplate> ) && 
-(?ps1 != <http://dbpedia.org/property/wordnet_type> ) && 
-(!isLiteral(?middle)) && 
-(?middle != <http://dbpedia.org/resource/Rome> ) && 
-(?middle != <http://dbpedia.org/resource/Lazio> ) && 
-(?middle != ?of1 ) && 
-(!isLiteral(?of1)) && 
-(?of1 != <http://dbpedia.org/resource/Rome> ) && 
-(?of1 != <http://dbpedia.org/resource/Lazio> ) && 
-(?of1 != ?middle )
-). 
-} LIMIT 10
-"""
-
-print urllib2.quote(s)
-
-
-

### 2017-07-12 relfinder/artists/goodResults.py

@@ -1,26 +1,0 @@
-import csv
-import sys
-
-def evaluateQuality(row):
-    goods = []
-    if '&&&1' in row[1]:
-        work_uri = row[0]
-        paths = row[1].split('|||')
-        poi_uri = row[2]
-        for p in paths:
-            if '&&&1' in p:
-                goods.append(work_uri+'--->'+p.replace('&&&1','')+'--->'+poi_uri)
-    return goods
-all_tuples = []
-with open(sys.argv[1], 'r') as f:
-    reader = csv.reader(f)
-    count = 0
-    for row in reader:
-        if count > 0:
-            res = evaluateQuality(row)
-            if len(res)>0:
-                all_tuples += res
-        count += 1
-
-with open(sys.argv[2],'w+') as out:
-        out.write("\n".join(all_tuples))

### 2017-07-12 relfinder/works/removeDouble.py

@@ -1,3 +1,0 @@
-import sys
-print tuple(open(sys.argv[1]).readlines())
-print len(list(tuple(open(sys.argv[1]).readlines())))

### 2017-07-12 relfinder/works_all/readable.py

@@ -1,58 +1,0 @@
-
-import re
-import sys
-import urllib2
-query_wikidata_prop = """SELECT ?label WHERE {
-  ?m ?p <STRING_TO_SUB>.
-  ?m rdfs:label ?label.
-  FILTER (lang(?label) = 'en') 
-  FILTER (?m = wd:P190|| ?m= wd:P19 || ?m =wd:P86||?m =wd:P47||?m = wd:P495||?m = wd:P17||?m = wd:P136)
-}
-LIMIT 1"""
-
-
-
-query_wikidata_ent = """SELECT ?label WHERE {
-  <STRING_TO_SUB> rdfs:label ?label.
-  FILTER (lang(?label) = 'en')                               
-}
-LIMIT 1"""
-
-def getQueryResponse(query,endpointURL='http://dbpedia.org/sparql'):
-    escapedQuery = urllib2.quote(query)
-    requestURL = endpointURL + "?query=" + escapedQuery
-    try:
-        request = urllib2.Request(requestURL)
-        result = urllib2.urlopen(request)
-        res = result.read()
-        return res
-    except:
-        raise Exception
-
-all_lines_1 = open(sys.argv[1]).read().splitlines()
-
-all_lines_2 = []
-
-for l_1 in all_lines_1:
-    items_1 = l_1.split('--->')
-    items_2 = []
-    for i in items_1:
-        if 'wikidata' in i:
-            if 'prop' in i:
-                q = query_wikidata_prop.replace('STRING_TO_SUB',i)
-            else:
-                q = query_wikidata_ent.replace('STRING_TO_SUB',i)
-            res = getQueryResponse(q,endpointURL='http://query.wikidata.org/sparql')
-            print q
-            i_2 = re.findall(r'<literal.*>(.*?)</literal>', res , re.S)[0]
-            items_2.append(i_2)
-    l_2 = '--->'.join(items_2)
-    all_lines_2.append(l_2)
-
-with open(sys.argv[2],'w+') as out:
-        out.write("\n".join(all_lines_2))
-
-
-        
-
-

### 2017-07-12 server2/etl/dump_tracks.py

@@ -1,106 +1,0 @@
-import csv
-import os
-import json
-import spotipy
-import spotipy.util
-from SPARQLWrapper import SPARQLWrapper, JSON
-
-clientid = '2b4bba8dba4d406a8086f33b644ddcd0'
-clientsecret = 'dc13827b3900467383a12e803b10e52f'
-redirect = 'http://localhost'
-username = 'fabio_ellena'
-
-# necessary to create/add track to public spotify
-scope = 'playlist-modify-public'
-
-def get_artist_tracks(artist_name):
-    token = spotipy.util.prompt_for_user_token(username, scope, client_id=clientid, client_secret=clientsecret,
-                                               redirect_uri=redirect)
-    sp = spotipy.Spotify(auth=token)
-    sp.trace = False
-
-    # get matching artist
-
-    results = sp.search(q='artist:' + artist_name, type='artist')
-    artists = results['artists']['items']
-    artist = None
-    if len(artists) == 0:
-        return None
-    artist = max(artists, key=lambda x: x['popularity'])
-
-    top_tracks = sp.artist_top_tracks(artist['id'], country='FR')['tracks']
-    return_tracks = []
-    for track in top_tracks:
-        return_tracks.append((track['id'], track['name']))
-    return return_tracks
-
-
-def get_dbpedia_label(uri):
-    sparql = SPARQLWrapper("http://dbpedia.org/sparql")
-    sparql.setQuery("""
-                        SELECT ?label ?preferredLabel 
-            WHERE { 
-               <%s> rdfs:label ?label .
-            FILTER (lang(?label) = "" || lang(?label) = "en") 
-               OPTIONAL { 
-                 <%s> rdfs:label ?preferredLabel . 
-                 FILTER (lang(?preferredLabel) = "" || lang(?preferredLabel) = "tk") 
-               } 
-            } limit 1
-                        """ % (uri, uri))
-    sparql.setReturnFormat(JSON)
-    results = sparql.query().convert()
-
-    for artist in results['results']['bindings']:
-        try:
-            label = artist['preferredLabel']['value']
-        except KeyError:
-            label = artist['label']['value']
-        return label
-
-
-def get_doremus_label(uri):
-    sparql = SPARQLWrapper("http://data.doremus.org/sparql")
-    sparql.setQuery("""
-                        SELECT ?label 
-            WHERE { 
-               <%s> foaf:name ?label .
-            } limit 1
[…]

### 2017-07-12 server2/etl/poi_enrich.py

@@ -1,163 +1,0 @@
-#read all
-#remove bus stations and add position to each 3cixty poi, remove dbpedia poi that are not in nice
-#group by dbpedia uri
-
-#foreach group:
-#    keep entries with the highest score
-#    remove entries with score < 90
-#	 keep the nearest to the center
-
-import csv
-import urllib2
-import json
-from geopy.distance import vincenty
-from SPARQLWrapper import SPARQLWrapper,JSON
-
-NICE_COORDINATES = (43.7034, 7.2663)
-THRESHOLD = 85
-
-def add_info(row):
-    url = row[0].rsplit('/',1)[1]
-    req = urllib2.Request('http://aplicaciones.localidata.com/eldaSuit/place/id/%s?_view=list' % url)
-    resp = urllib2.urlopen(req)
-    # 200
-    body = resp.read()
-    result = json.loads(body)
-    if len(result['result']['items']) > 0:
-        if type(result['result']['items'][0]["geoLocation"]['lat']) == list:
-            lat = float(result['result']['items'][0]["geoLocation"]['lat'][0])
-        else:
-            lat = float(result['result']['items'][0]["geoLocation"]['lat'])
-        if type(result['result']['items'][0]["geoLocation"]['long']) == list:
-            long_ = float(result['result']['items'][0]["geoLocation"]['long'][0])
-        else:
-            long_ = float(result['result']['items'][0]["geoLocation"]['long'])
-        row.append((lat,long_))
-    
-        uri = row[3]
-        sparql = SPARQLWrapper("http://dbpedia.org/sparql")
-        sparql.setQuery("""
-            SELECT ?place ?placeLabel ?lat ?long
-             WHERE {
-            <%s> geo:lat ?lat.
-            <%s> geo:long ?long.
-            }
-            """ % (uri,uri))        
-        sparql.setReturnFormat(JSON)
-        results = sparql.query().convert()
-
-        for place in results['results']['bindings']:
-            lat = float(place['lat']['value'])
-            long_ = float(place['long']['value'])
-            if vincenty(NICE_COORDINATES, (lat,long_)).km > 15:
-                return False
-        return True
-    else:
-        return False
-
-with open('../data/dbpedia_match_nogeo.csv','r') as input_fp:
-    reader=csv.reader(input_fp,)
-    # skip header
-    reader.next()
-    rows = [ [unicode(col,'utf-8') for col in row] for row in reader]
-
-new_rows = []
-for row in rows:
[…]

### 2017-07-12 server2/server.py

@@ -1,144 +1,0 @@
-from flask import Flask, request, jsonify, abort
-import database_helper
-import spotipy_util
-import util
-import threading
-from copy import deepcopy
-
-# initialization phase: load everything in memory
-
-# load poi_artists_path
-poi_artists = database_helper.load_poi_artists()
-
-# load pois
-pois = database_helper.load_pois(poi_artists)
-print(len(pois))
-print(pois)
-
-# load playlists
-playlist_collection = database_helper.PlaylistCollection(pois, poi_artists)
-print(playlist_collection.playlist_dict)
-
-# load tracks
-tracks_collection = database_helper.load_tracks()
-
-# create application
-app = Flask(__name__)
-
-# define endpoints
-
-
-@app.route('/')
-def home_page():
-    return 'hello world'
-
-
-@app.route('/position')
-def position():
-    # /position?lat=43.697093&lon=7.270747
-    # show the coordinates
-    lat = request.args.get('lat', default=None, type=float)
-    lon = request.args.get('lon', default=None, type=float)
-    if lat is None or lon is None:
-        abort(404)
-        # abort(404)
-    if lat < -90 or lat > +90:
-        abort(404)
-    if lon < -180 or lon > +180:
-        abort(404)
-
-    # latitude and longitude are correct
-    # find nearest poi
-    point = (lat, lon)
-    near_pois = util.get_near_pois(point, pois)
-
-    return jsonify(near_pois)
-
-
-@app.route('/playlist_name')
-def get_playlist_name():
-    # show the coordinates
-    lat = request.args.get('lat', default=None, type=float)
-    lon = request.args.get('lon', default=None, type=float)
-    if lat is None or lon is None:
-        abort(404)
-        # abort(404)
-    if lat < -90 or lat > +90:
-        abort(404)
-    if lon < -180 or lon > +180:
-        abort(404)
-
-    # latitude and longitude are correct
-    # find nearest poi
-    point = (lat, lon)
-    near_pois = util.get_near_pois(point, pois)
-    name = util.create_playlist_name(near_pois)
-    return jsonify(name)
-
-
-@app.route('/create_playlist')
-def create_playlist_from_position():
-    # show the coordinates
-    lat = request.args.get('lat', default=None, type=float)
-    lon = request.args.get('lon', default=None, type=float)
-    if lat is None or lon is None:
-        abort(404)
-        # abort(404)
-    if lat < -90 or lat > +90:
-        abort(404)
-    if lon < -180 or lon > +180:
[…]

### 2017-07-13 app/app.js
app modified

@@ -67,6 +67,10 @@
             return $location.path() == '/home' && $scope.spinner_visible;
         };
 
+        $scope.isHome = function(){
+            return $location.path() == '/home';
+        }
+
         var default_playlist = '5tDTLlIwA0EzoYEbEky9Ro';
         $scope.playlist_id = default_playlist;
         var position_data = Geolocation.watchPosition(watchOptions);

### 2017-07-13 app/home/home.js

@@ -6,7 +6,7 @@
     // Controller
     .controller('HomeCtrl', ['$scope', '$location', '$log', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$window', '$rootScope',
       function($scope, $location, $log, Geolocation, watchOptions, Recommendation, shareRecommendation, $window, $rootScope) {
-        $rootScope.iframeClass = "big_playlist";
+        $rootScope.iframeClass = "iframe_container_1";
         //console.log(watchOptions)
         $scope.selectedTrack = false;
         $scope.flag_select = false;

### 2017-07-13 app/map/map.js

@@ -24,7 +24,7 @@
 
 
         $scope.spinner_visible = true;
-        $rootScope.iframeClass = "small_playlist";
+        $rootScope.iframeClass = "iframe_container_2";
 
 
         $scope.enableModification = false;

### 2017-07-13 app/recommendation/recommendation-service.js

@@ -58,17 +58,7 @@
 
     }])
     .factory('shareRecommendation', function() {
-      var start_x = 0.0;
-      var start_y = 0.0;
-      var end_x = 1.0 - start_x;
-      var end_y = start_y;
-      var avg_x = 0.5;
-      var avg_y = 1.0;
-      var delta_w = avg_x - start_x;
-      var delta_h = avg_y - start_y;
       var path = [];
-      var pathnames = [];
-      var positions_colors = [];
       var track = '';
       var null_res_1 = 0;
       var null_res_2 = 0;
@@ -79,12 +69,13 @@
           return String.fromCharCode(parseInt(grp, 16));
         });
         x = unescape(x);
-        var y = x.split("/");
+        var y = x.split(/\/|#/);
         var res = y[y.length - 1].replace(/_/g, " ").replace("Category:", "");
 
-        if ((res.length > 14) && (j !== 0) && (j !== 12) && (j !== 6)) {
+        /*if ((res.length > 14) && (j !== 0) && (j !== 12) && (j !== 6)) {
           res = res.substr(0, 14) + '...';
         }
+        */
         return [x, res];
       };
 
@@ -93,9 +84,7 @@
         track = trackname;
         null_res_1 = 0;
         null_res_2 = 0;
-        pathnames = [];
         path = [];
-        positions_colors = [];
         var avg_resource = '';
 
         for (let i in path_dirty) {
@@ -103,59 +92,36 @@
           if (p) {
             var res = changeStringStyle(path_dirty[i], i);
             if (i == 6) avg_resource = res[0];
-            path.push(res[0]);
-            pathnames.push(res[1]);
+            path.push({"link":res[0],"label":res[1]});
           } else {
             if (i < 6) null_res_1++;
             else null_res_2++;
           }
         }
-        var nodes_left = 3 - null_res_1 / 2;
-        var nodes_right = 3 - null_res_2 / 2;
 
-        var step_left_x = delta_w / nodes_left;
-        var step_left_y = delta_h / nodes_left;
-
-        var step_right_x = delta_w / nodes_right;
-        var step_right_y = delta_h / nodes_right;
-
-        var pos_x = start_x;
-        var pos_y = start_y;
 
         for (let i = 0; i < path.length; i++) {
           var col;
           if (i % 2 == 0) {
             if (i == path.length - 1) {
-              col = '#4D84FF';
-              positions_colors.push([end_x, end_y, col]);
+              col = 'transparent';
[…]

### 2017-07-13 app/visualization/visualization.js

@@ -7,126 +7,28 @@
     // Controller
     .controller('VisualizationCtrl', ['$scope', '$location', '$log', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$mdDialog', '$window', '$rootScope',
       function($scope, $location, $log, Geolocation, watchOptions, Recommendation, shareRecommendation, $mdDialog, $window, $rootScope) {
-        $rootScope.iframeClass = "small_playlist";
-
-        var data_link = shareRecommendation.getPath();
-        var s = "";
-        var isGraph = false;
-
-        function drawPath() {
-          if (isGraph) {
-            s.graph.clear();
-            s.refresh();
-          }
-          isGraph = true;
-          var track = data_link[0];
-          var path = data_link[1];
-          var pathnames = data_link[2];
-          var positions_colors = data_link[3];
-          var i,
-            N = 20,
-            E = 200,
-            g = {
-              nodes: [],
-              edges: []
-            };
-          g.nodes.push({
-            id: 'n' + pathnames.length,
-            label: track,
-            x: 0.5,
-            y: 0.1,
-            size: 30,
-            color: '#1ECC5C'
-          });
-          for (i = 0; i < pathnames.length; i += 2) {
-
-            g.nodes.push({
-              id: 'n' + i,
-              label: pathnames[i],
-              link: path[i],
-              x: positions_colors[i][0],
-              y: positions_colors[i][1],
-              size: 30,
-              color: positions_colors[i][2]
-            });
-          }
-
-          g.edges.push({
-            id: 'e' + i,
-            source: 'n' + pathnames.length,
-            target: 'n' + 0,
-            size: 0.2,
-            type: 'curve',
-            color: '#1ECC5C',
-          });
+        $rootScope.iframeClass = "iframe_container_2";
 
 
-          for (i = 1; i < pathnames.length; i += 2)
-            g.edges.push({
-              id: 'e' + i,
-              label: pathnames[i],
-              link: path[i],
-              source: 'n' + (i - 1),
-              target: 'n' + (i + 1),
-              size: 0.2,
-              type: 'line',
-              color: '#ccc'
-            });
+        $scope.data_link = shareRecommendation.getPath();
 
-          s = new sigma({
-            graph: g,
-            renderer: {
-              container: document.getElementById('graph-container'),
-              type: 'canvas'
-            },
-            settings: {
-              doubleClickEnabled: false,
-              minEdgeSize: 0.5,
[…]

### 2017-07-13 app/app.js
Nice centered

@@ -54,9 +54,14 @@
       enableHighAccuracy: false // may cause errors if true
     })
 
+      .constant('NICE_CENTER', {
+          latitude: 43.709742,
+          longitude: 7.257396
+      })
 
-    .controller("NavCtrl", ['$scope', '$location', '$rootScope', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$window',
-      function($scope, $location, $rootScope, Geolocation, watchOptions, Recommendation, shareRecommendation, $window) {
+
+    .controller("NavCtrl", ['$scope', '$location', '$rootScope', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$window','NICE_CENTER',
+      function($scope, $location, $rootScope, Geolocation, watchOptions, Recommendation, shareRecommendation, $window,NICE_CENTER) {
           $scope.spinner_visible = true;
         $scope.showPlaylist = false;
         $scope.isHome = false;
@@ -75,8 +80,24 @@
         $scope.playlist_id = default_playlist;
         var position_data = Geolocation.watchPosition(watchOptions);
         position_data.then(null, function(err) {
-            $scope.showPlaylist = true;
             $window.alert("You should share your position to use all functionalities!!!");
+                var lat = NICE_CENTER.latitude;
+                var lon = NICE_CENTER.longitude;
+                console.log('getting recommendation');
+                Recommendation.getRecommendation(lat, lon)
+                    .then(function(d) {
+                            $scope.playlist_id = d.id;
+                            $scope.songList = d.tracks_paths;
+                            $scope.showPlaylist = true;
+                            $scope.spinner_visible = false;
+                        },
+                        function(errResponse) {
+                            console.error('Error while fetching recommendation');
+                            $scope.spinner_visible = false;
+                        }
+                    );
+
+
           },
           function(position) {
             var lat = position.coords.latitude;

### 2017-07-13 app/home/home.js

@@ -4,17 +4,17 @@
   angular.module('myApp.home', [])
 
     // Controller
-    .controller('HomeCtrl', ['$scope', '$location', '$log', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$window', '$rootScope',
-      function($scope, $location, $log, Geolocation, watchOptions, Recommendation, shareRecommendation, $window, $rootScope) {
+    .controller('HomeCtrl', ['$scope', '$location', '$log', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$window', '$rootScope','NICE_CENTER',
+      function($scope, $location, $log, Geolocation, watchOptions, Recommendation, shareRecommendation, $window, $rootScope,NICE_CENTER) {
         $rootScope.iframeClass = "iframe_container_1";
-        //console.log(watchOptions)
         $scope.selectedTrack = false;
         $scope.flag_select = false;
+
+
         $scope.$watch(Recommendation.getTracks, function() {
           $scope.songList = Recommendation.getTracks();
           $scope.flag_select = !!Object.values($scope.songList).length;
-          if ($scope.flag_select){
-          }
+
         });
 
 

### 2017-07-13 app/map/map.js

@@ -1,16 +1,13 @@
 (function(angular) {
   'use strict';
 
-  const NICE_CENTER = {
-    latitude: 43.709742,
-    longitude: 7.257396
-  };
+
 
   angular.module('myApp.map', [])
 
     // Controller
-    .controller('MapCtrl', ['$scope', '$location', '$log', 'uiGmapGoogleMapApi', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$mdDialog', '$rootScope',
-      function($scope, $location, $log, uiGmapGoogleMapApi, Geolocation, watchOptions, Recommendation, shareRecommendation, $mdDialog, $rootScope) {
+    .controller('MapCtrl', ['$scope', '$location', '$log', 'uiGmapGoogleMapApi', 'Geolocation', 'watchOptions', 'Recommendation', 'shareRecommendation', '$mdDialog', '$rootScope','NICE_CENTER',
+      function($scope, $location, $log, uiGmapGoogleMapApi, Geolocation, watchOptions, Recommendation, shareRecommendation, $mdDialog, $rootScope,NICE_CENTER) {
 
         function distance(lat1, lon1, lat2, lon2) {
           var p = 0.017453292519943295;    // Math.PI / 180

### 2017-07-13 report/report.tex

@@
 Context can be defined as any information that can be used to characterize the situation of an entity~\cite{Dey:2001:UUC:593570.593572}.
-These informations informations includes mood, location, activity, friends, daily and current activities of the target user.
+These information information includes mood, location, activity, friends, daily and current activities of the target user.
 
@@
 In~\cite{Kaminskas:2012:KMR:2390848.2390854}, the goal is achieved by by restricting the subspace of DBpedia to a set classes related to the domains of interest.
-These classes includes concepts that are easily linkable to artists and POIs, such as historic periods, architectural styles and geographic informations.
+These classes includes concepts that are easily linkable to artists and POIs, such as historic periods, architectural styles and geographic information.
 In this way, it is possible to find relations in a set of paths constrained to pass through those classes.
@@
 \subsubsection{3cixty}
-3cixty is a semantic dataset that contains aggregated informations of POIs and events.
-The dataset is the result of an aggregation process that join the POI informations from different datasets e.g.
+3cixty is a semantic dataset that contains aggregated information of POIs and events.
+The dataset is the result of an aggregation process that join the POI information from different datasets e.g.
 Facebook, Foursquare, Yelp \dots
 In this project 3cixty is used as a trusted source of POIs for Nice.
-POIs have a lot of informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint of the 3cixty API.
+POIs have a lot of information, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint of the 3cixty API.
 
@@
 
-Among other informations, we have the coordinates, but we do not use them because not all entities have them.
+Among other information, we have the coordinates, but we do not use them because not all entities have them.
 Moreover, we have seen experimentally that using the DBpedia coordinates we obtain worse results because of their inaccuracy.
-This is clearly visible in Figure\ref{fig:parc}
+This is clearly visible in Figure~\ref{fig:parc}.
 Regarding 3cixty entities, they have very accurate coordinates and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.
@@
 The importance of the selection, transformation, similarity metric and aggregation pipeline is extremely high, in fact we want a confidence which we can trust.
-An untrusted confidence gives us no additional informations about good matches and bad matches.
+An untrusted confidence gives us no additional information about good matches and bad matches.
 At this point we filter all matches with a score below a given threshold(0.8).
@@
 Even the simpler operations, such as finding all artists and all songs are extremely difficult due to the non-strict ontology of DBpedia.
-In order to have some order, we use DOREMUS, which contains trusted and properly organized informations about artists and songs.
+In order to have some order, we use DOREMUS, which contains trusted and properly organized information about artists and songs.
 
@@
 The performed query is written below; we retrieved not only the artist uri but also the artist name, the id, the born year, the death year and the DBpedia `sameAs' link.
-These informations are useful as input data for our similarity metric and for the final evaluation.
+These information are useful as input data for our similarity metric and for the final evaluation.
 
@@
 On the other side instead we have only a possible matching URI.
-So we queried DBpedia SPARQL endpoint to get these informations:
+So we queried DBpedia SPARQL endpoint to get these information:
 
@@
 
-To get the years informations we have considered different properties because the most of the time the birth year is written as object of the property \verb|dct:subject|.
+To get the years information we have considered different properties because the most of the time the birth year is written as object of the property \verb|dct:subject|.
 Actually it's part of the object, e.g.\verb|dct:1998_births|.
@@
 The graph above shows the scores distribution; the majority of matchings seems to have score near 1 that is good; however some noise it is still present; to remove it we cut all matchings with score lower that 0.5.
-0.5 generally means that we don't have informations about the death and birth years but label matched perfectly and the DBpedia entity had an \verb|rdf:type| that clearly indicates that it is a composer.
+0.5 generally means that we don't have information about the death and birth years but label matched perfectly and the DBpedia entity had an \verb|rdf:type| that clearly indicates that it is a composer.
 
@@
 
-Relfinder is able to generate all paths with a given depths and with at most 2 direction changes.
+Relfinder is able to generate all paths with a given depth and with at most 2 direction changes.
 These paths can express most of the interesting relations between two entities, in fact when we consider more complex paths, we start loosing significance.
@@
 Our approach builds on top of the Relfinder, looking at the parts that slows the whole process.
-The problem is that DBpedia is small world and its average degree is 4.3, this means that on average we can reach every entity in at most 4-5 hops.
+The problem is that DBpedia is a small world and its average degree is 4.3: this means that on average we can reach every entity in at most 4-5 hops.
 Unfortunately our case does not make part of that average, and many times we need 5-6 hops to connect two entities.
@@
 
-Here $r(r_{i})$ corresponds to the $i_{th}$ resource of the path and $occ(r_{i})$ to the number of occurrences of this resource belongs to all considered paths.
+Here $r(r_{i})$ corresponds to the $i_{th}$ resource of the path and $occ(r_{i})$ to the number of occurrences of this resource in all considered paths.
 Then we define the similarity measure between artist and POI:
@@
 
-At the end, we select 5 Artists for each POI looking at those artists with the highest score, where the score is given by their most interesting paths.
+At the end, we select 5 artists for each POI looking at those artists with the highest score, where the score is given by their most interesting paths.
 
@@
 At this point we can perform the API search request, and it returns a list of artist objects.
-Each object contains different informations regarding each artist, such as his popularity and his genres.
+Each object contains different information regarding each artist, such as his popularity and his genres.
 Here we use only the popularity by taking the most popular one, but in the future we could use the genre information to perform a better disambiguation.
@@
 \item Evaluate the overall approach with real users.
-\item Use additional context informations available in 3cixty and DOREMUS.
+\item Use additional context information available in 3cixty and DOREMUS.
 In this optic, 3cixty provides information about events and this could be added in the recommendation engine, maybe suggesting songs or artists that will be played in a place in the near future.
